---
title: "Plotting global models inputs"
author: "Camilla Novaglio"
date: "02/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# TO DO 

Derek: Is it worth doing the mean SST / NPP  etc for 2000-2010 and 2090-2100 rather than 2030? Done for 1990-2000 and 2090-2100 as per years used to calcualte changes between the 2 periods - 2000-2010 is trickier as 1/2 data is on hist file and the other 1/2 is on the fut file for CMIP5 - OK

Cheryl: https://doi.org/10.5194/bg-17-3439-2020

Ryan: When doing delta temperatures, don't do % change, do celsius change. When showing npp, phy or zoo, use g C as the weight (*12), and per day, not per second as the time unit for npp. - OK

# Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

# variables - TO CHANGE 
cmip<-c("CMIP5", "CMIP6")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values_tos = c(0,30) # C and following Ryan paper  

# for CMIP6.... units checked by checking max and min in 2030 for each variable # MAX are too high for all 
# main_plot_colour_values_pp = c(1e-09,5e-07) # mol m-2 s-1 # ryan paper is in mg C m-2 d-1
# main_plot_colour_values_phyto = c(0, 0.3) # mol m-2 # ryan paper is in mg C m-2
# main_plot_colour_values_zoo = c(0,0.5) # mol m-2 # ryan paper is in mg C m-2
main_plot_colour_values_pp = c(0,1) # g C m-2 d-1 
main_plot_colour_values_phyto = c(0, 4) # g C m-2 
main_plot_colour_values_zoo = c(0, 4) # g C m-2 
delta_plot_colour_values = c(-50,50)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots (% change between cmips) # purple to yellow shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 
colour_scheme4 <- c(low = 'white', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# load ISIMIP2b inputs 

```{r}

# extract data IPSL ---- 

directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP2b/IPSL_CM5A_LR/"

variable_to_extract <-c("to", "pp", "phy", "zoo")

yearmonth1<- as.yearmon("1990-01")
yearmonth2<- as.yearmon("1999-01") # yearly values

yearmonth1_fut<- as.yearmon("2090-01")
yearmonth2_fut<- as.yearmon("2099-01")

data_ipsl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # i = 2
  # the variable is temperature,extract adn convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], ".nc4.zs.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 # can be done later on if this is going to be merged with the loop below
    hist$data_units<-"C"
    
    # ####### HERE 
    # hist_2010<-averageEnvironmentalCDF(directory, filename , variable_to_extract[i], as.yearmon("2000-01"), as.yearmon("2010-01"), average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE) # mean annual temp 2000-2010
    # hist_2010<-hist_2010$fishvar[,]
    # hist_2010<-hist_2010 - 273.15
    # hist_2010$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp261_20060101_21001231_1Y.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp851_20060101_21001231_1Y.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
    
    # ####### HERE 
    # fut585_2100<-averageEnvironmentalCDF(directory, filename , variable_to_extract[i], as.yearmon("2090-01"), as.yearmon("2100-01"), average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE) # mean annual temp 2000-2010
    # fut585_2100<-fut585_2100$fishvar[,]
    # fut585_2100<-fut585_2100 - 273.15
    # fut585_2100$data_units<-"C"
    
    ####### HERE 
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  
  }else{ # the variable is other than temperature, extract both small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
      
      filename<-paste0("l",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      # ####### HERE
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      # ####### HERE
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 
      
      # ####### HERE
      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      # ####### HERE
      if(variable_to_extract[i] == "pp"){
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }
      
      # (mean(hist$fishvar, na.rm = TRUE)/0.0000115741)*1000 # mg * day as per Ryan 
      # (mean(hist$fishvar, na.rm = TRUE)/3.1709791983765e-8) # g per year as per cmip6 input paper 
      # (mean(hist$fishvar, na.rm = TRUE)/0.0000115741) # g per days as here 
      
      diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
      diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
    
  }
  
  data_ipsl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
  
}

names(data_ipsl_CMIP5)


# extract data GFDL ---- 

directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP2b/GFDL_ESM2M/"

variable_to_extract <-c("to", "pp", "phy", "zoo")
# the variable inside the netcdf is called differently than the variable in the file name.  
variable_to_extract2 <-c("TO_ZS", "PP_ZINT", "PHY_ZINT", "ZOO_ZINT")

data_gfdl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # the variable is temperature,extract adn convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], "_gfdl-esm2m_historical_zs_annual_195001-200512.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 # can be done later on if this is going to be merged with the loop below
    hist$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp26_zs_annual_200601-210012.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp85_zs_annual_200601-210012.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
  
    # fut585_2030<-averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], as.yearmon("2030-01"), as.yearmon("2030-01"), average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE) # mean annual temp in 2030
    # fut585_2030<-fut585_2030$fishvar[,]
    # fut585_2030<-fut585_2030 - 273.15
    # fut126$data_units<-"C"
    
    ####### HERE 
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  
  }else{ # # the variable is other than temperature, extract both small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
      filename<-paste0("l",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      # ####### HERE
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      # ####### HERE
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      # fut585_2030S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), as.yearmon("2030-01"), as.yearmon("2030-01"), average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      # fut585_2030S<-fut585_2030S$fishvar[,]
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      # fut585_2030L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), as.yearmon("2030-01"), as.yearmon("2030-01"), average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      # fut585_2030L<-fut585_2030L$fishvar[,]
  
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 
  
      # fut585_2030<-fut585_2030S + fut585_2030L
      
      # ####### HERE
      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      # ####### HERE
      if(variable_to_extract[i] == "pp"){
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }
      
      # (mean(hist$fishvar, na.rm = TRUE)/0.0000115741)*1000 # mg * day as per Ryan 
      # (mean(hist$fishvar, na.rm = TRUE)/3.1709791983765e-8) # g per year as per cmip6 input paper 
      # (mean(hist$fishvar, na.rm = TRUE)/0.0000115741) # g per days as here 
      
      diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
      diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
    
  }
  
  data_gfdl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
  
}

names(data_gfdl_CMIP5)

```

# Plot ISIMIP2b inputs

```{r map CMIP6}

# flip matrix

fliplr_matrix<- function(data_to_flip){
  temp= data_to_flip
  for (ii in 1:dim(data_to_flip)[2])
    data_to_flip[,ii] = temp[,dim(data_to_flip)[2] - ii + 1]
  
  data_to_flip
}

move_hemispheres<- function(data_to_flip){
  temp= data_to_flip
  data_to_flip[1:180,] = temp[181:360,]
  data_to_flip[181:360,] = temp[1:180,]
  data_to_flip
}
  

## plot IPSL ----

names(data_ipsl_CMIP5)

data_ipsl_CMIP5$to$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$to$diff_8p5)
data_ipsl_CMIP5$to$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$to$diff_8p5)

#### HERE
data_ipsl_CMIP5$to$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$to$fut585$fishvar)
data_ipsl_CMIP5$to$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$to$fut585$fishvar)
data_ipsl_CMIP5$to$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$to$hist$fishvar)
data_ipsl_CMIP5$to$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$to$hist$fishvar)

data_ipsl_CMIP5$pp$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$pp$diff_8p5)
data_ipsl_CMIP5$pp$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$pp$diff_8p5)
data_ipsl_CMIP5$pp$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$pp$fut585$fishvar)
data_ipsl_CMIP5$pp$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$pp$fut585$fishvar)
data_ipsl_CMIP5$pp$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$pp$hist$fishvar)
data_ipsl_CMIP5$pp$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$pp$hist$fishvar)

data_ipsl_CMIP5$phy$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$phy$diff_8p5)
data_ipsl_CMIP5$phy$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$phy$diff_8p5)
data_ipsl_CMIP5$phy$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$phy$fut585$fishvar)
data_ipsl_CMIP5$phy$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$phy$fut585$fishvar)
data_ipsl_CMIP5$phy$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$phy$hist$fishvar)
data_ipsl_CMIP5$phy$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$phy$hist$fishvar)

data_ipsl_CMIP5$zoo$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$zoo$diff_8p5)
data_ipsl_CMIP5$zoo$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$zoo$diff_8p5)
data_ipsl_CMIP5$zoo$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$zoo$fut585$fishvar)
data_ipsl_CMIP5$zoo$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$zoo$fut585$fishvar)
data_ipsl_CMIP5$zoo$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$zoo$hist$fishvar)
data_ipsl_CMIP5$zoo$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$zoo$hist$fishvar)

titles<-c("Sea surface temperature", "Net primary production","Phytoplankton carbon","Zooplankton carbon")
coltitles<-c("C", "g C m-2 d-1","g C m-2","g C m-2") # check that all units are the same across CMIPs and earth models - transform to more meaningful - e.g. milligrams?
data_ipsl_CMIP5$to$hist$data_units
data_ipsl_CMIP5$pp$hist$data_units
data_ipsl_CMIP5$phy$hist$data_units
data_ipsl_CMIP5$zoo$hist$data_units

color<-list(main_plot_colour_values_tos, main_plot_colour_values_pp, main_plot_colour_values_phyto, main_plot_colour_values_zoo) 
num_dp_variables<-c(0,1,0,0)

# # we don't need maps for each earth model - otherwise update
# map_ipsl585_CMIP5<-list()
# 
# ##### HERE
# map_ipsl585_CMIP5_2000<-list()
# map_ipsl585_CMIP5_2100<-list()
# 
# for (i in 1:length(data_ipsl_CMIP5)){ 
#   
#   tit <- paste("IPSL RCP8.5", titles[[i]], "change (1990s vs 2090s)",cmip[1],sep =" ")
#   map_ipsl585_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "change \n (%)", model_type = NA)
#   names(map_ipsl585_CMIP5)[[i]]<-variable_to_extract[[i]]
#   
#   ##### HERE
#   tit <- paste("IPSL RCP8.5", titles[[i]], " mean 1990s", cmip[1], sep =" ")
#   map_ipsl585_CMIP5_2000[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$hist$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
#   names(map_ipsl585_CMIP5_2000)[[i]]<-variable_to_extract[[i]]
#   
#   ##### HERE
#   tit <- paste("IPSL RCP8.5", titles[[i]], " mean 2090s", cmip[1], sep =" ")
#   map_ipsl585_CMIP5_2100[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$fut585$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
#   names(map_ipsl585_CMIP5_2100)[[i]]<-variable_to_extract[[i]]
# 
#   rm(tit)
#   
# }
# 
# names(map_ipsl585_CMIP5)

## plot GFDL ----

names(data_gfdl_CMIP5)

data_gfdl_CMIP5$to$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$to$diff_8p5)
data_gfdl_CMIP5$to$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$to$diff_8p5)

### HERE
data_gfdl_CMIP5$to$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$to$fut585$fishvar)
data_gfdl_CMIP5$to$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$to$fut585$fishvar)
data_gfdl_CMIP5$to$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$to$hist$fishvar)
data_gfdl_CMIP5$to$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$to$hist$fishvar)

data_gfdl_CMIP5$pp$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$pp$diff_8p5)
data_gfdl_CMIP5$pp$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$pp$diff_8p5)
data_gfdl_CMIP5$pp$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$pp$fut585$fishvar)
data_gfdl_CMIP5$pp$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$pp$fut585$fishvar)
data_gfdl_CMIP5$pp$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$pp$hist$fishvar)
data_gfdl_CMIP5$pp$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$pp$hist$fishvar)

data_gfdl_CMIP5$phy$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$phy$diff_8p5)
data_gfdl_CMIP5$phy$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$phy$diff_8p5)
data_gfdl_CMIP5$phy$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$phy$fut585$fishvar)
data_gfdl_CMIP5$phy$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$phy$fut585$fishvar)
data_gfdl_CMIP5$phy$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$phy$hist$fishvar)
data_gfdl_CMIP5$phy$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$phy$hist$fishvar)

data_gfdl_CMIP5$zoo$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$zoo$diff_8p5)
data_gfdl_CMIP5$zoo$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$zoo$diff_8p5)
data_gfdl_CMIP5$zoo$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$zoo$fut585$fishvar)
data_gfdl_CMIP5$zoo$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$zoo$fut585$fishvar)
data_gfdl_CMIP5$zoo$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$zoo$hist$fishvar)
data_gfdl_CMIP5$zoo$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$zoo$hist$fishvar)

# coltitles<-c("C", "mol m-2 s-1","mol m-2","mol m-2") 
# check units 
data_gfdl_CMIP5$to$hist$data_units
data_gfdl_CMIP5$pp$hist$data_units
data_gfdl_CMIP5$phy$hist$data_units
data_gfdl_CMIP5$zoo$hist$data_units

# # we don't need maps for each earth model - otherwise update 
# map_gfdl585_CMIP5<-list()
# 
# ##### HERE
# map_gfdl585_CMIP5_2000<-list()
# map_gfdl585_CMIP5_2100<-list()
# 
# for (i in 1:length(data_ipsl_CMIP5)){ 
#   
#   tit <- paste("GFDL RCP8.5", titles[[i]], "change (1990s vs 2090s)",cmip[1],sep =" ")
#   map_gfdl585_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "change \n (%)", model_type = NA)
#   names(map_gfdl585_CMIP5)[[i]]<-variable_to_extract[[i]]
#   
#   ##### HERE
#   tit <- paste("GFDL RCP8.5", titles[[i]], " mean 1990s", cmip[1], sep =" ")
#   map_gfdl585_CMIP5_2000[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$hist$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
#   names(map_gfdl585_CMIP5_2000)[[i]]<-variable_to_extract[[i]]
#   
#   ##### HERE
#   tit <- paste("GFDL RCP8.5", titles[[i]], " mean 2090s", cmip[1], sep =" ")
#   map_gfdl585_CMIP5_2100[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$fut585$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
#   names(map_gfdl585_CMIP5_2100)[[i]]<-variable_to_extract[[i]]
# 
#   rm(tit)
#   
# }
# 
# names(map_gfdl585_CMIP5)
# map_gfdl585_CMIP5$to

```

# Model average for CMIP5

```{r}

# you can calculate SD and agreement as in batch_run_maps.R

model_stat<-function(data, variable){

  # i = 1
  # data=list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]])
  # variable = 'hist'
  
  X <- lapply(data, `[[`, variable)
  
  if (variable != "diff_8p5"){
    X <- lapply(X, `[[`, 'fishvar')
  }
  
  X <- lapply(X, function(x) replace(x, !is.finite(x), NA))
  Y <- do.call(cbind, X)
  Y <- array(Y, dim=c(dim(X[[1]]), length(X)))
  model_average_new<-apply(Y, c(1, 2), mean, na.rm = TRUE)

  return(list(model_average = model_average_new))
}

data_average_change_CMIP5<-list()

#### HERE
data_average_value_2000_CMIP5<-list()
data_average_value_2100_CMIP5<-list()

names(data_ipsl_CMIP5)

for(i in 1:length(data_ipsl_CMIP5)){
  
  # i = 1
  data_average_change_CMIP5[[i]]<-model_stat(list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]]), variable = 'diff_8p5')$model_average
  names(data_average_change_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  #### HERE 
  data_average_value_2000_CMIP5[[i]]<-model_stat(list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]]), variable = 'hist')$model_average
  names(data_average_value_2000_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  data_average_value_2100_CMIP5[[i]]<-model_stat(list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]]), variable = 'fut585')$model_average
  names(data_average_value_2100_CMIP5)[[i]]<-variable_to_extract[[i]]
  
}

# plot earth models average for all input variables

##### HERE
delta_plot_colour_values_new<-list(c(0,4), delta_plot_colour_values, delta_plot_colour_values, delta_plot_colour_values)
coltitles1<-list("Change \n(C)", "Change \n(%)", "Change \n(%)", "Change \n(%)")
colour_scheme_vary<-list(c(low = "white", mid = '#fee5d9', high = "#de2d26"),colour_scheme2,colour_scheme2,colour_scheme2) # or mid = #fcbba1 for darker 

map_average_change_CMIP5<-list()

###### HERE
map_average_value_2000_CMIP5<-list()
map_average_value_2100_CMIP5<-list()

for (i in 1:length(data_average_change_CMIP5)){ 
  
  # i = 1
  ###### HERE 
  tit <- paste("Mean change in", titles[[i]], "RCP 8.5, 1990s to 2090s",cmip[1], sep =" ")
  map_average_change_CMIP5[[i]]<-plot_FISH_MIP(data_average_change_CMIP5[[i]], tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_average_change_CMIP5)[[i]]<-variable_to_extract[[i]]

  ####### HERE
  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 1990s", cmip[1], sep =" ")
  map_average_value_2000_CMIP5[[i]]<-plot_FISH_MIP(data_average_value_2000_CMIP5[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2000_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 2090s", cmip[1], sep =" ")
  map_average_value_2100_CMIP5[[i]]<-plot_FISH_MIP(data_average_value_2100_CMIP5[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2100_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

map_average_value_2000_CMIP5$phy
map_average_value_2000_CMIP5$zoo
map_average_value_2100_CMIP5$pp

max(data_average_value_2000_CMIP5$pp, na.rm = TRUE) # 2 ### CHANGE to 1
min(data_average_value_2000_CMIP5$pp, na.rm = TRUE) # 0.05 # change to 0
mean(data_average_value_2000_CMIP5$pp, na.rm = TRUE)
max(data_average_value_2000_CMIP5$phy, na.rm = TRUE) # 6 ### CHANGE to  4
min(data_average_value_2000_CMIP5$phy, na.rm = TRUE) # 0
mean(data_average_value_2000_CMIP5$phy, na.rm = TRUE)
max(data_average_value_2000_CMIP5$zoo, na.rm = TRUE) # 6 ### CHANGE to 4
min(data_average_value_2000_CMIP5$zoo, na.rm = TRUE) # 0
mean(data_average_value_2000_CMIP5$zoo, na.rm = TRUE)

```

# save inputs ISIMIP2b temp 

```{r}

##### HERE 
data_summaries_CMIP5<-list(data_average_change_CMIP5 = data_average_change_CMIP5, data_average_value_2000_CMIP5 = data_average_value_2000_CMIP5, data_average_value_2100_CMIP5 = data_average_value_2100_CMIP5)
map_summaries_CMIP5<-list(map_average_change_CMIP5 = map_average_change_CMIP5, map_average_value_2000_CMIP5 = map_average_value_2000_CMIP5, map_average_value_2000_CMIP5 = map_average_value_2000_CMIP5)
save(data_ipsl_CMIP5, data_gfdl_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_inputs_CMIP5.RData")

```

# Load ISIMIP3b inputs 

```{r}

# CMIP6 data location
directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP3b/"

# extract data IPSL ---- 

variable_to_extract <-c("to", "pp", "phy", "zoo") # just to be consistent with names across cmips and earth models 
variable_to_extract3 <-c("tos", "intpp", "phyc-vint", "zooc-vint")

yearmonth1<- as.yearmon("1990-01")
yearmonth2<- as.yearmon("1999-12") # montly values 

yearmonth1_fut<- as.yearmon("2090-01")
yearmonth2_fut<- as.yearmon("2099-12")

data_ipsl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  # fut585_2030<-averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], as.yearmon("2030-01"), as.yearmon("2030-12"), average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6) # mean annual temp in 2030
  # fut585_2030<-fut585_2030$fishvar[,,1]
  
  ### HERE
  if (variable_to_extract3[[i]] == "tos"){
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  }else {
    
    # ####### HERE
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    # ####### HERE
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }

    diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
    diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  }
  
  data_ipsl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_ipsl_CMIP6)

# extract data GFDL ---- 

data_gfdl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("gfdl-esm4_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut126<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  # fut585_2030<-averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], as.yearmon("2030-01"), as.yearmon("2030-12"), average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6) # mean annual temp in 2030
  # fut585_2030<-fut585_2030$fishvar[,,1]
  
  ### HERE
  if (variable_to_extract3[[i]] == "tos"){
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  }else {
    
    # ####### HERE
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    # ####### HERE
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }

    diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
    diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  }
  
  data_gfdl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126,  fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_gfdl_CMIP6)

```

# Plot ISIMIP3b inputs

```{r map CMIP6}

## plot IPSL ----

# same as above - need to run if only considering CMIP6
# titles<-c("Sea surface temperature", "Net primary production","Phytoplankton carbon","Zooplankton carbon")
# coltitles<-c("C", "mol m-2 s-1","mol m-2","mol m-2")
# color<-list(main_plot_colour_values_tos, main_plot_colour_values_pp, main_plot_colour_values_phyto, main_plot_colour_values_zoo) 
# check units
data_ipsl_CMIP6$to$hist$data_units
data_ipsl_CMIP6$pp$hist$data_units
data_ipsl_CMIP6$phy$hist$data_units
data_ipsl_CMIP6$zoo$hist$data_units

# # we don't need maps for each earth model - otherwise update 
# map_ipsl585_CMIP6<-list()
# map_ipsl585_CMIP6_2030<-list()
# 
# for (i in 1:length(data_ipsl_CMIP6)){ 
#   
#   tit <- paste("IPSL RCP8.5", titles[[i]], "change (1990s vs 2090s)",cmip[2],sep =" ")
#   map_ipsl585_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "change \n (%)", model_type = NA)
#   names(map_ipsl585_CMIP6)[[i]]<-variable_to_extract[[i]]
#   
#   tit <- paste("IPSL RCP8.5", titles[[i]], "in 2030", cmip[2], sep =" ") # can change year....
#   map_ipsl585_CMIP6_2030[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$fut585_2030, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
#   names(map_ipsl585_CMIP6_2030)[[i]]<-variable_to_extract[[i]]
# 
#   rm(tit)
#   
# }
# 
# names(map_ipsl585_CMIP6)
# map_ipsl585_CMIP6$to 
# map_ipsl585_CMIP6_2030$to

## plot GFDL ----

# need to model hemisphere
# checked: different data layout do not effect the calculation of model mean, SD and agreements because these are done after you flipped the matrix and/or change hemisphere. it does not effect the calculation of trends because you are first weighting biomass by grid cell according to explicit lat values and then you are averaging by lat and long anyway.

#### HERE
data_gfdl_CMIP6$to$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$to$diff_8p5)
data_gfdl_CMIP6$to$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$to$fut585$fishvar)
data_gfdl_CMIP6$to$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$to$hist$fishvar)

data_gfdl_CMIP6$pp$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$pp$diff_8p5)
data_gfdl_CMIP6$pp$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$pp$fut585$fishvar)
data_gfdl_CMIP6$pp$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$pp$hist$fishvar)

data_gfdl_CMIP6$phy$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$phy$diff_8p5)
data_gfdl_CMIP6$phy$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$phy$fut585$fishvar)
data_gfdl_CMIP6$phy$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$phy$hist$fishvar)

data_gfdl_CMIP6$zoo$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$zoo$diff_8p5)
data_gfdl_CMIP6$zoo$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$zoo$fut585$fishvar)
data_gfdl_CMIP6$zoo$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$zoo$hist$fishvar)

# # we don't need maps for each earth model - otherwise update 
# map_gfdl585_CMIP6<-list()
# map_gfdl585_CMIP6_2030<-list()
# 
# for (i in 1:length(data_gfdl_CMIP6)){ 
#   
#   tit <- paste("GFDL RCP8.5", titles[[i]], "change (1990s vs 2090s)",cmip[2],sep =" ")
#   map_gfdl585_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "change \n (%)", model_type = NA)
#   names(map_gfdl585_CMIP6)[[i]]<-variable_to_extract[[i]]
#   
#   tit <- paste("GFDL RCP8.5", titles[[i]], "in 2030", cmip[2], sep =" ") # can change year....
#   map_gfdl585_CMIP6_2030[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$fut585_2030, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
#   names(map_gfdl585_CMIP6_2030)[[i]]<-variable_to_extract[[i]]
# 
#   rm(tit)
#   
# }

```

# Model average for CMIP6

```{r}

data_average_change_CMIP6<-list()

#### HERE
data_average_value_2000_CMIP6<-list()
data_average_value_2100_CMIP6<-list()

for(i in 1:length(data_ipsl_CMIP6)){
  
  # i = 1
  data_average_change_CMIP6[[i]]<-model_stat(list(data_ipsl_CMIP6[[i]], data_gfdl_CMIP6[[i]]), variable = 'diff_8p5')$model_average
  names(data_average_change_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  #### HERE 
  data_average_value_2000_CMIP6[[i]]<-model_stat(list(data_ipsl_CMIP6[[i]], data_gfdl_CMIP6[[i]]), variable = 'hist')$model_average
  names(data_average_value_2000_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  data_average_value_2100_CMIP6[[i]]<-model_stat(list(data_ipsl_CMIP6[[i]], data_gfdl_CMIP6[[i]]), variable = 'fut585')$model_average
  names(data_average_value_2100_CMIP6)[[i]]<-variable_to_extract[[i]]
  
}

# plot earth models average for all input variables

map_average_change_CMIP6<-list()

###### HERE
map_average_value_2000_CMIP6<-list()
map_average_value_2100_CMIP6<-list()

for (i in 1:length(data_average_change_CMIP6)){ 
  
  # i = 1
  ###### HERE 
  tit <- paste("Mean change in", titles[[i]], "RCP 8.5, 1990s to 2090s",cmip[2], sep =" ")
  map_average_change_CMIP6[[i]]<-plot_FISH_MIP(data_average_change_CMIP6[[i]], tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_average_change_CMIP6)[[i]]<-variable_to_extract[[i]]

  ####### HERE
  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 1990s", cmip[2], sep =" ")
  map_average_value_2000_CMIP6[[i]]<-plot_FISH_MIP(data_average_value_2000_CMIP6[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2000_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 2090s", cmip[2], sep =" ")
  map_average_value_2100_CMIP6[[i]]<-plot_FISH_MIP(data_average_value_2100_CMIP6[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2100_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

```


# save inputs ISIMIP3b temp 

```{r}

data_summaries_CMIP6<-list(data_average_change_CMIP6 = data_average_change_CMIP6, data_average_value_2000_CMIP6 = data_average_value_2000_CMIP6, data_average_value_2100_CMIP6 = data_average_value_2100_CMIP6)
map_summaries_CMIP6<-list(map_average_change_CMIP6 = map_average_change_CMIP6, map_average_value_2000_CMIP6 = map_average_value_2000_CMIP6, map_average_value_2000_CMIP6 = map_average_value_2000_CMIP6)
save(data_ipsl_CMIP6, data_gfdl_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_inputs_CMIP6.RData")

```

# Delta plot 

```{r}

# you could calculate delta as scatter plot - as in batch_run_maps.R
# option 1 - subtract (julia) - OK
# delta_plot_colour_values_new2<-delta_plot_colour_values_new
delta_plot_colour_values_new2<-list(c(-2, 2), c(-30, 30), c(-30, 30), c(-30, 30)) # highlight delta changes more ..... 

delta_data<-list()
delta_map<-list()

for(i in 1:length(data_summaries_CMIP6$data_average_change_CMIP6)){
 
  # NOTE it should be OK with temp too even if temp is in C change and the other are in % change
  # if positive -> t, pp, phy or zoo have increased between 1990s and 2090s more in CMIP6 than in CMIP5
  # if negative, inputs have increased more in CMIP5 than CMIP6
  # THIS IS STRANGE!!! for temp results change if I consider % change or C change !!! why??? 
  
  
  
  
  
  
  delta_data[[i]]<-data_summaries_CMIP6$data_average_change_CMIP6[[i]] - data_summaries_CMIP5$data_average_change_CMIP5[[i]]
  names(delta_data)[[i]]<-variable_to_extract[[i]]
  
  tit<-paste("Delta (CMIP6 change - CMIP5 change)", titles[[i]], sep =" ")
  delta_map[[i]]<-plot_FISH_MIP(delta_data[[i]], tit, delta_plot_colour_values_new2[[i]], colour_scheme = colour_scheme3, coltitle = "Difference \nin \nchange \n")  
  names(delta_map)[[i]]<-variable_to_extract[[i]]
  
}

names(delta_map)
delta_map$zoo

```


# Put all maps together 

```{r multipanel plot}

library(patchwork)

# FIG 1
# change between 1990 and 2090s for CMIP5 and form CMIP6 and delta between CMIPs 

layout <- "
ABC
DEF
GHK
LMN
"

pt<-map_average_change_CMIP5$to + map_average_change_CMIP6$to + delta_map$to +
  map_average_change_CMIP5$pp + map_average_change_CMIP6$pp + delta_map$pp +
  map_average_change_CMIP5$phy + map_average_change_CMIP6$phy + delta_map$phy +
  map_average_change_CMIP5$zoo + map_average_change_CMIP6$zoo + delta_map$zoo +
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig1_revised.pdf"), height=15, width=20)
pt 
dev.off()

# FIG 1B or S1?? 
layout <- "
AB
CD
EF
GH
"

pt<-map_average_value_2000_CMIP5$to + map_average_value_2000_CMIP6$to +
  map_average_value_2000_CMIP5$pp + map_average_value_2000_CMIP6$pp + 
  map_average_value_2000_CMIP5$phy + map_average_value_2000_CMIP6$phy + 
  map_average_value_2000_CMIP5$zoo + map_average_value_2000_CMIP6$zoo + 
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig1B_1990.pdf"), height=15, width=15)
pt 
dev.off()

# FIG 1B or S1?? 
layout <- "
AB
CD
EF
GH
"

pt<-map_average_value_2100_CMIP5$to + map_average_value_2100_CMIP6$to +
  map_average_value_2100_CMIP5$pp + map_average_value_2100_CMIP6$pp + 
  map_average_value_2100_CMIP5$phy + map_average_value_2100_CMIP6$phy + 
  map_average_value_2100_CMIP5$zoo + map_average_value_2100_CMIP6$zoo + 
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig1B_2090.pdf"), height=15, width=15)
pt 
dev.off()



```




