---
title: "Plotting global models' time series inputs"
author: "Camilla Novaglio & Derek Tittensor"
date: "18/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script analysis Earth System Models' outputs used as inputs for Marine Ecosystem Models. It is structured in two steps:  
Step 1 extracts environmental variables (temperature, PP, phytoplankton and zooplankton) from ESMs netcdfs and collapses them into a grid-averaged time-series (1970 to 2100)  
Step 2 averages the data across ESMs and scenarios and produces Figure 1

# STEP 1 extract data

## Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())

install_load <- function (this_package)  {   

   package <- c(this_package)
   if(package %in% rownames(installed.packages()))
        do.call('library', list(package))

    # if package is not installed locally, download, then load
    else {
        install.packages(package)
         do.call("library", list(package))
    }
}

### load/install libraries ###
install_load("grid")
install_load("zoo")
install_load("viridis")
install_load("tidyr")
install_load("dplyr")
install_load("ncdf4")

### load helper scripts with functions to extract data from netcdfs ###
source("R/HelperScripts.r")

### create folders where temporary data can be stored ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep1 = "temp_data"
ifelse(!dir.exists(file.path(mainDir, DirStep1)), dir.create(file.path(mainDir, DirStep1)), FALSE)

```

## Extract environmetnal variables and calcaulte % change in time for CMIP5 runs 

```{r}

# extract data IPSL ---- 

directory = "../CMIP5vsCMIP6_data/fishmip_inputs/marine-fishery_global_ISIMIP2b/IPSL_CM5A_LR/"

variable_to_extract <-c("to", "pp", "phy", "zoo")

yearmonth1<- as.yearmon("1971-01")
yearmonth2<- as.yearmon("2005-01") 

yearmonth1_fut<- as.yearmon("2006-01")
yearmonth2_fut<- as.yearmon("2100-01")

output = "yearly"
cmip = 5

data_ipsl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # extract temperature and convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], ".nc4.zs.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1, yearmonth2, average_whole_period = FALSE, ipsl = TRUE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 
    hist$data_units<-"C"
    
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp261_20060101_21001231_1Y.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = TRUE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp851_20060101_21001231_1Y.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = TRUE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
    
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")   
  
  }else{ # extract small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, ipsl = TRUE, hist = TRUE)
      
      filename<-paste0("l",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, ipsl = TRUE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = TRUE, hist = FALSE)
      
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = TRUE, hist = FALSE)
      
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = TRUE, hist = FALSE)
      
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = TRUE, hist = FALSE)
      
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 
      
      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      if(variable_to_extract[i] == "pp"){ 
        
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }

    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")   
      
  }

  data_ipsl_CMIP5[[i]]<-list(all = all)
  names(data_ipsl_CMIP5)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
  
}

# extract data GFDL ---- 

directory = "../CMIP5vsCMIP6_data/fishmip_inputs/marine-fishery_global_ISIMIP2b/GFDL_ESM2M/"

variable_to_extract2 <-c("TO_ZS", "PP_ZINT", "PHY_ZINT", "ZOO_ZINT")

output = "yearly"
cmip = 5

data_gfdl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], "_gfdl-esm2m_historical_zs_annual_195001-200512.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1, yearmonth2, average_whole_period = FALSE, ipsl = FALSE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 
    hist$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp26_zs_annual_200601-210012.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = FALSE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp85_zs_annual_200601-210012.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = FALSE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
    
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")   
  
  }else{ 
    
      filename<-paste0("s",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, ipsl = FALSE, hist = TRUE)
      filename<-paste0("l",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, ipsl = FALSE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = FALSE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, ipsl = FALSE, hist = FALSE)
  
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 

      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      if(variable_to_extract[i] == "pp"){
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }
      
    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")   
    
  }
  
  data_gfdl_CMIP5[[i]]<-list(all = all)
  names(data_gfdl_CMIP5)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
  
}

```

## Save temporary outputs ISIMIP2b 

```{r}

save(data_ipsl_CMIP5, data_gfdl_CMIP5, file = "../CMIP5vsCMIP6_data/temp_data/data_trends_inputs_CMIP5.RData")

```

## Extract data and calcaulte % change in time CMIP6 

```{r}

# CMIP6 data location

directory = "../CMIP5vsCMIP6_data/fishmip_inputs/marine-fishery_global_ISIMIP3b/"

# extract data IPSL ---- 

variable_to_extract <-c("to", "pp", "phy", "zoo") 
variable_to_extract3 <-c("tos", "intpp", "phyc-vint", "zooc-vint")

yearmonth1<- as.yearmon("1971-01")
yearmonth2<- as.yearmon("2014-12") 

yearmonth1_fut<- as.yearmon("2015-01")
yearmonth2_fut<- as.yearmon("2099-12") 

output = "monthly"
cmip = 6

data_ipsl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, hist = FALSE, cmip = 6)
  
  if (variable_to_extract3[[i]] == "tos"){
    
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")
  }else {
    
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }
    
    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")
  }
  
  
  data_ipsl_CMIP6[[i]]<-list(all = all)
  names(data_ipsl_CMIP6)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
 
}

# extract data GFDL ---- 

data_gfdl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("gfdl-esm4_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut126<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, hist = FALSE, cmip = 6)
  
  if (variable_to_extract3[[i]] == "tos"){
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")
  }else {
    
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }

    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")
  }
  
  data_gfdl_CMIP6[[i]]<-list(all = all)
  names(data_gfdl_CMIP6)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
 
}

```

## Save temporary outputs ISIMIP3b 

```{r}

save(data_ipsl_CMIP6, data_gfdl_CMIP6, file = "../CMIP5vsCMIP6_data/temp_data/data_trends_inputs_CMIP6.RData")

```

# STEP 2 averadge and plot data

## Load data

```{r}

rm(list=ls())

load("../CMIP5vsCMIP6_data/temp_data/data_trends_inputs_CMIP5.RData")
load("../CMIP5vsCMIP6_data/temp_data/data_trends_inputs_CMIP6.RData")

```

## Load libraries for netcdf and define variables

```{r load CMIP5}

install_load <- function (this_package)  {   

   package <- c(this_package)
   if(package %in% rownames(installed.packages()))
        do.call('library', list(package))

    # if package is not installed locally, download, then load
    else {
        install.packages(package)
         do.call("library", list(package))
    }
}

### load/install libraries ###
install_load("grid")
install_load("zoo")
install_load("viridis")
install_load("tidyr")
install_load("dplyr")
install_load("ncdf4")
install_load("patchwork")
install_load("ggplot2")

### load helper scripts with functions to extract data from netcdfs ###
source("R/HelperScripts.r")

### define variables to extract ###
variable_to_extract <-c("to", "pp", "phy", "zoo")

### create folders where figures can be saved ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep2 = "figures"
ifelse(!dir.exists(file.path(mainDir, DirStep2)), dir.create(file.path(mainDir, DirStep2)), FALSE)
save_loc<-"../CMIP5vsCMIP6_data/figures/"

```

## Mean and sd of environmental variables across models and ssp for both CMIP5 and CMIP6

```{r}

all<-list()
all_notMean<-list()

for (i in 1:length(variable_to_extract)){

  # CMIP5 
  data_ipsl_CMIP5_tcb<-as.data.frame(data_ipsl_CMIP5[[i]]$all) %>% 
    mutate(cmip = 5, 
           earth = "ipsl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  data_gfdl_CMIP5_tcb<-as.data.frame(data_gfdl_CMIP5[[i]]$all) %>% 
    mutate(cmip = 5, 
           earth = "gfdl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  # CMIP6
  data_ipsl_CMIP6_tcb<-as.data.frame(data_ipsl_CMIP6[[i]]$all) %>% 
    mutate(cmip = 6, 
           earth = "ipsl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  data_gfdl_CMIP6_tcb<-as.data.frame(data_gfdl_CMIP6[[i]]$all) %>% 
    mutate(cmip = 6, 
           earth = "gfdl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  # add all together and average
  all_notMean[[i]]<-data_ipsl_CMIP5_tcb %>% 
    full_join(data_gfdl_CMIP5_tcb) %>% 
    full_join(data_ipsl_CMIP6_tcb) %>% 
    full_join(data_gfdl_CMIP6_tcb) 
  
  all[[i]]<- all_notMean[[i]] %>% 
    group_by(protocol, year, cmip) %>% 
    summarise(mean = mean(tcbChange, na.rm = TRUE), 
              sd = sd(tcbChange, na.rm = TRUE)) %>% 
    mutate(sd_min = mean - sd, 
           sd_max = mean + sd) 
  
  names(all)[i]<-variable_to_extract[i]
  names(all_notMean)[i]<-variable_to_extract[i]
  
  }

# create dots when CMIP6 < CMIP6 
trial<-all$to %>% 
  dplyr::select(cmip, mean, protocol, year) %>%
  spread(cmip, mean) %>% 
  mutate(A = ifelse(`6`> `5`,`5`, NA)) %>% 
  gather("cmip","mean", -c(protocol, year, A)) %>% 
  mutate(cmip = as.numeric(cmip))

all$to<-all$to %>% 
  full_join(trial)

# create dots when CMIP6 < CMIP6 
trial<-all$pp %>% 
  dplyr::select(cmip, mean, protocol, year) %>%
  spread(cmip, mean) %>% 
  mutate(A = ifelse(`6` < `5`,`5`, NA)) %>% 
  gather("cmip","mean", -c(protocol, year, A)) %>% 
  mutate(cmip = as.numeric(cmip))

all$pp<-all$pp %>% 
  full_join(trial)

```

## FIG 1 - trends in environmental variables by ESM and scenario

```{r}

general_plot<-function(data){
  
  plot<-ggplot(data, aes(x=year, y = tcbChange,  color = protocol, linetype = earth))+ 
  annotate("rect", xmin = 1990, xmax = 2000, ymin = -Inf, ymax = Inf, alpha = .2)+
  geom_line(size=0.7) +
  geom_hline(yintercept = 0, color = "grey60", size = 1)+
  scale_x_continuous(limits = c(1970, 2100), breaks = pretty(data$year, n = 10), name = "Year")+
  scale_color_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "RCP2.6", "RCP8.5"))+
  scale_fill_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "RCP2.6", "RCP8.5"))+
  scale_linetype_manual(values = c("solid","dotdash"),name = "Earth System Models", labels =c("GFDL-ESM2M","IPSL-CM5A-LR"))+
  theme_bw()+
  theme(text = element_text(size=14),
        axis.title.y = element_text(vjust=0.4, size = 20),
        axis.title.x = element_text(vjust=0.3, size = 20),
        axis.text.x = element_text(angle=90, size=16),
        axis.text.y = element_text(angle=0, size=16),
        panel.border = element_rect(colour = "black"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        strip.text.x = element_text(face = "bold"),
        legend.background= element_rect(colour = 'black', fill = 'white', linetype='solid'),
        legend.text=element_text(size=16),
        legend.title = element_text(size=16),
        legend.position = c(0.18, 0.65),
        legend.key.size = unit(0.8, "cm"))
  
  return (plot = plot)
  
}

# temperature CMIP5
data = all_notMean$to %>% 
  filter(cmip == 5)

to_cmip5<-general_plot(data)
to_cmip5<-to_cmip5 +
  geom_vline(xintercept = 2005.5, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-1, 5), breaks = pretty(seq(5, -1), n = 5), name = "Change in sea surface temperature (°C)")

# temperature CMIP6
data = all_notMean$to %>% 
  filter(cmip == 6)

to_cmip6<-general_plot(data)
to_cmip6<-to_cmip6 +geom_vline(xintercept = 2015, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-1, 5), breaks = pretty(seq(5, -1), n = 5), name = "Change in sea surface temperature (°C)")+
  scale_color_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "SSP1-2.6", "SSP5-8.5"))+
  scale_fill_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "SSP1-2.6", "SSP5-8.5"))+
  scale_linetype_manual(values = c("solid","dotdash"),name = "Earth System Models", labels =c("GFDL-ESM4","IPSL-CM6A-LR"))+
  guides(colour = guide_legend(order = 1), linetype = guide_legend(order = 2))

# PP CMIP5
data = all_notMean$pp %>% 
  filter(cmip == 5)

pp_cmip5<-general_plot(data)
pp_cmip5<-pp_cmip5 +
  geom_vline(xintercept = 2005.5, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-15, 15), breaks = pretty(seq(15, -15), n = 10), name = "Change in net primary production (%)")+
  theme(legend.position = "none")

# PP CMIP6
data = all_notMean$pp %>% 
  filter(cmip == 6)

pp_cmip6<-general_plot(data)
pp_cmip6<-pp_cmip6 +
  geom_vline(xintercept = 2015, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-15, 15), breaks = pretty(seq(15, -15), n = 10), name = "Change in net primary production (%)")+
  theme(legend.position = "none")

# Phy CMIP5
data = all_notMean$phy %>% 
  filter(cmip == 5)

ph_cmip5<-general_plot(data)
ph_cmip5<-ph_cmip5 +
  geom_vline(xintercept = 2005.5, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-15, 5), breaks = pretty(seq(15, -15), n = 10), name = "Change in phytoplankton carbon (%)") +
  theme(legend.position = "none")

# Phy CMIP6
data = all_notMean$phy %>% 
  filter(cmip == 6)

ph_cmip6<-general_plot(data)
ph_cmip6<-ph_cmip6 +
  geom_vline(xintercept = 2015, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-15, 5), breaks = pretty(seq(15, -15), n = 10), name = "Change in phytoplankton carbon (%)") +
  theme(legend.position = "none")

# Zoo CMIP5
data = all_notMean$zoo %>% 
  filter(cmip == 5)

zoo_cmip5<-general_plot(data)
zoo_cmip5<-zoo_cmip5 +
  geom_vline(xintercept = 2005.5, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-20, 5), breaks = pretty(seq(5,-20), n = 5), name = "Change in zooplankton carbon (%)") +
  theme(legend.position = "none")

# Zoo CMIP6
data = all_notMean$zoo %>% 
  filter(cmip == 6)

zoo_cmip6<-general_plot(data)
zoo_cmip6<-zoo_cmip6 +
  geom_vline(xintercept = 2015, color = "grey60", size = 2)+
  scale_y_continuous(limits = c(-20, 5), breaks = pretty(seq(5,-20), n = 5), name = "Change in zooplankton carbon (%)") +
  theme(legend.position = "none")


# add all together 
layout <- "
AB
CD
EF
GH
"

to_cmip5<-to_cmip5 + ggtitle("a)") + theme(plot.title = element_text(size = 20, face = "bold", hjust = 0), axis.title.x = element_blank())
to_cmip6<-to_cmip6 + ggtitle("b)") + theme(plot.title = element_text(size = 20, face = "bold",hjust = 0), axis.title.x = element_blank(), axis.title.y = element_blank())
pp_cmip5<-pp_cmip5 + ggtitle("c)") + theme(plot.title = element_text(size = 20, face = "bold", hjust = 0))
pp_cmip6<-pp_cmip6 + ggtitle("d)") + theme(plot.title = element_text(size = 20, face = "bold",hjust = 0), axis.title.y = element_blank())

ph_cmip5<-ph_cmip5 + ggtitle("e)") + theme(plot.title = element_text(size = 20, face = "bold", hjust = 0), axis.title.x = element_blank())
ph_cmip6<-ph_cmip6 + ggtitle("f)") + theme(plot.title = element_text(size = 20, face = "bold",hjust = 0), axis.title.x = element_blank(), axis.title.y = element_blank())
zoo_cmip5<-zoo_cmip5 + ggtitle("g)") + theme(plot.title = element_text(size = 20, face = "bold", hjust = 0))
zoo_cmip6<-zoo_cmip6 + ggtitle("h)") + theme(plot.title = element_text(size = 20, face = "bold",hjust = 0), axis.title.y = element_blank())

plot<-to_cmip5 + to_cmip6 + pp_cmip5 + pp_cmip6 +
  ph_cmip5 + ph_cmip6 + zoo_cmip5 + zoo_cmip6 +
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig1.pdf"), height=22, width=15)
plot 
dev.off()

```
