---
title: "Plotting global models outputs"
author: "Camilla Novaglio"
date: "04/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# TO DO 

# TO CHECK 

Models maps CMIP6 - why do i have to invert matrices?  

# Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

# variables 
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values = c(0,10000) # these need to change for each model? 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots (between cmips change) # purple to green shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# Load global ISIMIP2b model data 

```{r}

# CMIP5 data location
directory = "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/"

# APECOSM ----
h_yearsA <- "1950_2005"
f_yearsA<- "2006_2100"
outputA<-"monthly"
oaA<-"no-oa"

# BOATS ----
h_yearsB <- "1971_2005"
f_yearsB<- "2006_2099"
outputB<-"monthly"
oaB<-"no-oa"

# DBEM ----
h_yearsD <- "1951_2005"
f_yearsD<- "2006_2099"
outputD<-"annual"
oaD<-"oa"

# DBPM ----
h_yearsDB <- "1950_2005"
f_yearsDB<- "2006_2100"
outputDB<-"monthly"
oaDB<-"no-oa"

# EcoOcean ----  
h_yearsE <- "1971_2005"
f_yearsE<- "2006_2100"
outputE<-"monthly"
oaE<-"no-oa"

# macroecological ----  
h_yearsM <- "1950_2005"
f_yearsM<- "2006_2100"
outputM<-"annual"
oaM<-"no-oa"

# extract data IPSL ---- 
h_years <-c(h_yearsA, h_yearsB, h_yearsD, h_yearsDB, h_yearsE, h_yearsM)
f_years <-c(f_yearsA, f_yearsB, f_yearsD, f_yearsDB, f_yearsE, f_yearsM)
output <-c(outputA, outputB, outputD, outputDB, outputE, outputM)
oa <-c(oaA, oaB, oaD, oaDB, oaE, oaM)

yearmonth1<- rep(as.yearmon("1990-01"), length(mod_ipsl))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- rep(as.yearmon("2090-01"), length(mod_ipsl))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_ipsl_CMIP5<-list()

for (i in 1:length(mod_ipsl)){

  # i = 1
  filename<-paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[2],"/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_hist_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], ".nc4")
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_rcp2p6_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_rcp8p5_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_ipsl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_ipsl_CMIP5)

# add Zoom IPSL ----

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/historical/"
filename<-"zoomss_ipsl-cm5a-lr_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"
yearmonth1 = as.yearmon("1990-01")
yearmonth2 = as.yearmon("1999-01")
hist<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/future/"
filename<-"zoomss_ipsl-cm5a-lr_nobc_rcp26_nosoc_co2_tcb_global_annual_2006_2100.nc4"
yearmonth1 = as.yearmon("2090-01")
yearmonth2 = as.yearmon("2099-01")
fut126<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

filename<-"zoomss_ipsl-cm5a-lr_nobc_rcp85_nosoc_co2_tcb_global_annual_2006_2100.nc4"
fut585<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP5$ZooMSS<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# extract data GFDL ---- 

h_years <-c(h_yearsB, h_yearsD, h_yearsE, h_yearsM)
f_years <-c(f_yearsB, f_yearsD, f_yearsE, f_yearsM)
f_years[3]<-"2006_2099" #  # ecoOcean changes 
output <-c(outputB, outputD, outputE, outputM)
oa <-c(oaB, oaD, oaE, oaM)

yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_gfdl_CMIP5<-list()

for (i in 1:length(mod_gfdl)){

  # i = 1
  filename<-paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[2],"/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_hist_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], ".nc4")
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[3], "/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_rcp2p6_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[3], "/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_rcp8p5_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_gfdl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_gfdl_CMIP5)

# add zoom GFDL ----

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/historical/"
filename<-"zoomss_gfdl-esm2m_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"
yearmonth1 = as.yearmon("1990-01")
yearmonth2 = as.yearmon("1999-01")
hist<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/future/"
filename<-"zoomss_gfdl-esm2m_nobc_rcp26_nosoc_co2_tcb_global_annual_2006_2100.nc4"
yearmonth1 = as.yearmon("2090-01")
yearmonth2 = as.yearmon("2099-01")
fut126<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

filename<-"zoomss_gfdl-esm2m_nobc_rcp85_nosoc_co2_tcb_global_annual_2006_2100.nc4"
fut585<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP5$ZooMSS<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

```

NOTES   
average_whole_period: if TRUE you are averaging data between 1990 and 1999, if FALSE you are extrapolating data for each one of the years between 1990 and 1999  
the  printed info on year is the file year extent   
here you are considering only ipsl, no fishing - but can apply the same code to the other scenarios   
DBEM dimension 0.5 deg - here taken care of   

# Plot global ISIMIP2b model outputs

```{r map CMIP5}

## plot IPSL ----

map_ipsl585_CMIP5<-list()

mod_ipsl<-c(mod_ipsl, "ZooMSS")
model_type_ipsl<-ifelse(mod_ipsl == "DBEM","DBEM", NA) # this is because DBEM need to be plotted in 0.5 deg

for (i in 1:length(data_ipsl_CMIP5)){ 
  
  tit <- paste(mod_ipsl[i], "IPSL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_ipsl585_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl585_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(tit)
  
}

names(map_ipsl585_CMIP5)
# map_ipsl585_CMIP5$ZooMSS

### plot GFDL ----

mod_gfdl<-c(mod_gfdl, "ZooMSS")
model_type_gfdl<-ifelse(mod_gfdl == "DBEM","DBEM", NA) 
map_gfdl585_CMIP5<-list()

for (i in 1:length(data_gfdl_CMIP5)){ 
  
  tit <- paste(mod_gfdl[i], "GFDL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_gfdl585_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl585_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(tit)
  
}

names(map_gfdl585_CMIP5)
# map_gfdl585_CMIP5$ZooMSS


```

# Model average for CMIP5

```{r}

# RCP 8.5
# MAKE SURE THAT ALL MATRICES ARE ON ONE DEGREE SCALE
### TEMPORARY - JUST TAKE THE VALUE FROM CLOSE POINT
lons_to_use = seq(1,719,2)
lats_to_use = seq(1,359,2)

data_ipsl_CMIP5$DBEM$diff_8p5 = data_ipsl_CMIP5$DBEM$diff_8p5[lons_to_use, lats_to_use] 
data_gfdl_CMIP5$DBEM$diff_8p5 = data_gfdl_CMIP5$DBEM$diff_8p5[lons_to_use, lats_to_use] 

# 3 options here: ipsl, gfdl, or combined depending on data_ipsl_CMIP5
# also other options would  be to consider spp126 ('diff_2p6')

# old version in Derek's code and here vectorised 

model_stat<-function(data){
  
  #data = c(data_ipsl_CMIP6,data_gfdl_CMIP6)

  X <- lapply(data, `[[`, 'diff_8p5')
  X <- lapply(X, function(x) replace(x, !is.finite(x), NA))
  Y <- do.call(cbind, X)
  Y <- array(Y, dim=c(dim(X[[1]]), length(X)))
  model_average_new<-apply(Y, c(1, 2), mean, na.rm = TRUE)
  # model_average_new[!is.finite(model_average_new)]<-NA # just to make sure that all NaN and Inf resulting from mean() are treated as NA 
  model_sd_new<-apply(Y, c(1, 2), sd, na.rm = TRUE)
  # model_sd_new[!is.finite(model_sd_new)]<-NA
  
  X <- lapply(data, `[[`, 'diff_8p5')
  Y <- do.call(cbind, X)
  Y <- array(Y, dim=c(dim(X[[1]]), length(X)))

  #  this takes into account agreement on both positive or negative changes. - i.e. if most models show positive change agreement will be high and vice versa. 
  temp<-apply(Y, c(1,2), function(x) length(x[which(x>=0)])) # sum the number of values that are > = 0 (increase or stable) 
  temp2<-apply(Y, c(1,2), function(x) length(x[which(!is.na(x))])) # sum the number of values that are different from na and nan - including inf
  
  temp4<-temp/temp2
  model_agreement_new<-ifelse(is.na(temp4), NA, ifelse(temp4>0.5, temp4*100, (1-temp4)*100)) 
  # if 0/7 = 0 -> 100 # [1,88]
  # if 1/7 = 0.14 it means that 1 over 7 models show increases hence model strongly agree on the decrease -> (1-temp4)*100) = 86%
  # if 2/7 = 0.28 -> 72% on decreases
  # if 3/7 = 0.42 -> 57% on decreases 
  # if 4/7 = 0.57 -> 0.57*100 = 57% on increases 
  # if 5/7 = 0.71 -> 71% in increases 
  # if 6/7 = 0.85 -> 85% on increases 
  # if 7/7 = 100% on increases 
  # model_agreement_new[!is.finite(model_agreement_new)]<-NA

  return(list(model_average = model_average_new, model_sd = model_sd_new, model_agreement = model_agreement_new))
}

# # remove DBEM first but keep option with DBEM just in case 
# data_ipsl_CMIP52<-data_ipsl_CMIP5
# data_ipsl_CMIP5$DBEM<-NULL
# data_gfdl_CMIP5$DBEM<-NULL

# if you want the plot to be exactly as per Lotze use '2' version of data 
# data_ipsl_CMIP52$ZooMSS<-NULL
# data_gfdl_CMIP52$ZooMSS<-NULL

res_ipsl<-model_stat(data_ipsl_CMIP5)
model_average_ipsl_CMIP5<-res_ipsl$model_average
model_sd_ipsl_CMIP5<-res_ipsl$model_sd
model_agreement_ipsl_CMIP5<- res_ipsl$model_agreement

res_gfdl<-model_stat(data_gfdl_CMIP5)
model_average_gfdl_CMIP5<-res_gfdl$model_average
model_sd_gfdl_CMIP5<-res_gfdl$model_sd
model_agreement_gfdl_CMIP5<- res_gfdl$model_agreement

# if you want the plot to be exactly as per Lotze (DBEM gfdl in agreemetn was not considered)
# data_gfdl_CMIP52$DBEM$diff_8p5<-NULL

res_all<-model_stat(c(data_ipsl_CMIP5, data_gfdl_CMIP5))
model_average_all_CMIP5<-res_all$model_average
model_sd_all_CMIP5<-res_all$model_sd
model_agreement_all_CMIP5<- res_all$model_agreement 

# save model_average_ipsl_CMIP5 to plot together with crop data... Might need to change folder 
# save(model_average_all_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/model_average_all_CMIP5.RData")

# Define a layout function
mean_plot_colour_values = c(-50,50)
sd_plot_colour_values = c(0,50)
model_agreement_plot_colour_values = c(50,100)

# # define title IPSL
# maptitle_average = paste("Mean % change IPSL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_sd = paste("Standard Deviation IPSL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_agreement = paste("Agreement IPSL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# 
# # Plot the model average and standard deviation
# avarage_CMIP5_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
# sd_CMIP5_ipsl<-plot_FISH_MIP(model_sd_ipsl_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
# agreement_CMIP5_ipsl<-plot_FISH_MIP(model_agreement_ipsl_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") # why is this white along all coasts?!
# 
# # define title GFDL
# maptitle_average = paste("Mean % change GFDL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_sd = paste("Standard Deviation GFDL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_agreement = paste("Agreement GFDL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# 
# # Plot the model average and standard deviation
# avarage_CMIP5_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
# sd_CMIP5_gfdl<-plot_FISH_MIP(model_sd_gfdl_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
# agreement_CMIP5_gfdl<-plot_FISH_MIP(model_agreement_gfdl_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") 

# define title All
maptitle_average = paste("Mean % change RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
maptitle_agreement = paste("Agreement RCP 8.5, 1990s to 2090s CMIP5", sep=" ")

# Plot the model average and standard deviation
avarage_CMIP5_all<-plot_FISH_MIP(model_average_all_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP5_all<-plot_FISH_MIP(model_sd_all_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP5_all<-plot_FISH_MIP(model_agreement_all_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot averadge by esm 
avarage_CMIP5_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP5, "Mean % change RCP 8.5, 1990s to 2090s CMIP5 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP5_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP5, "Mean % change RCP 8.5, 1990s to 2090s CMIP5 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

```

# save outputs ISIMIP2b temp 

```{r}

data_summaries_CMIP5<-list(res_all= res_all, res_ipsl = res_ipsl, res_gfdl = res_gfdl)
map_summaries_CMIP5<-list(avarage_CMIP5_all = avarage_CMIP5_all, sd_CMIP5_all = sd_CMIP5_all, agreement_CMIP5_all = agreement_CMIP5_all, avarage_CMIP5_ipsl = avarage_CMIP5_ipsl, avarage_CMIP5_gfdl = avarage_CMIP5_gfdl)
save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5.RData")

```

# Load global ISIMIP3b model data

```{r load CMIP6}

# run first 2 sections if you are not running the CMIP5 sections

directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/"
# 
# # # CHECK GFDL DBPM .... is it corrupted? YES - need to rerun .... re-run and it's OK now but the map shows some white parallel lines which migth be due to cell not being run ... strange! re-run but still the same.... ned to check with Ryan! 
# filename<-"dbpm_gfdl-esm4_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBPM/_tmp/gfdl-esm4/future/"
# 
# fut126<- averageFishCDF(directory, filename, variable_to_extract[1], as.yearmon("2090-01"), as.yearmon("2099-12"), average_whole_period = TRUE, CMIP = 6)
# 
# image(fut126$fishvar)

# # CHECK IPSL DBPM .... is it corrupted? NO - I don't understand why the same code now produces corrupted new outputs (GFDL + size-spectrum) - I might have deleted print(lat) and print(log) when printing output to the matrix between IPSL and GFDL + size-spectrum netdfs runs... that was the bug for GFDL and the size-spectrum outputs
# # print("-169")
# # paste("-169")
# filename<-"dbpm_ipsl-cm6a-lr_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBPM/_tmp/ipsl-cm6a-lr/future/"
# 
# fut126<- averageFishCDF(directory, filename, variable_to_extract[1], as.yearmon("2090-01"), as.yearmon("2099-12"), average_whole_period = TRUE, CMIP = 6)
# 
# dim(fut126$fishvar)
# image(fut126$fishvar)
# fut126$fishvar[90:92, 90:92]
# 
# 
# # CHECK IPSL DBPM .... all good when you overwrite the outputs by mistake? - all good 
# # print("-169")
# # paste("-169")
# filename<-"dbpm_ipsl-cm6a-lr_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/Desktop/"
# 
# fut1262<- averageFishCDF(directory, filename, variable_to_extract[1], as.yearmon("2090-01"), as.yearmon("2099-12"), average_whole_period = TRUE, CMIP = 6)
# 
# dim(fut1262$fishvar)
# image(fut1262$fishvar)
# fut1262$fishvar[90:92, 90:92]

# # # CHECK FEISTY ... dimension order changed between versions (before after last Matthias correction)? NO and warning below is OK because the order in which the dimensions are specified is different than the order of the dimension in the data array...  
# filename<-"feisty_ipsl-cm6a-lr_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/FEISTY_beforeUpdate/_tmp/ipsl-cm6a-lr/future/"
# nc <- nc_open(paste(directory, filename, sep = ""))
# print(nc)

mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL", "EcoTroph", "FEISTY", "ZooMSS") 
mod_ipsl <- c("APECOSM","BOATS","DBPM","MACROECOLOGICAL","FEISTY","ZooMSS") 

# APECOSM ----
# will be updated 
h_yearsA <- "1950_2014"
f_yearsA<- "2015_2100"
earthA<-"_ipsl-cm6a-lr_nobasd_"
outputA<-"monthly"
extensionA<-".nc"

# BOATS ----
h_yearsB <- "1950_2014"
f_yearsB<- "2015_2100"
earthB<-"_ipsl-cm6a-lr_nobc_"
outputB<-"monthly"
extensionB<-".nc"

# DBEM ----
# added below

# DBPM ----
h_yearsDB <- "1850_2014"
f_yearsDB<- "2015_2100"
earthDB<-"_ipsl-cm6a-lr_nobasd_"
outputDB<-"monthly" 
extensionDB <-".nc"

# EcoOcean ----  
# added below  

# macroecological ----  
h_yearsM <- "1950_2014"
f_yearsM<- "2015-2100"
earthM<-"_ipsl-cm6a-lr_nobc_"
outputM<-"annual"
extensionM<-".nc"

# EcoTroph ----  
h_yearsE <- "1950-2014"
f_yearsE<- "2015-2100"
earthE<-"_ipsl-cm6a_nobc_"
outputE<-"annual"
extensionE<-".nc"

# FEISTY ----  
h_yearsF <- "1950_2014"
f_yearsF<- "2015_2100"
earthF<-"_ipsl-cm6a-lr_nobasd_" 
outputF<-"monthly"
extensionF<-".nc"

# ZooMSS ----  
h_yearsZ <- "1950_2014"
f_yearsZ<- "2015_2100"
earthZ<-"_ipsl-cm6a-lr_nobasd_"
outputZ<-"annual"
extensionZ<-".nc"

# extract data IPSL ---- 
h_years <-c(h_yearsA,h_yearsB, h_yearsDB, h_yearsM,h_yearsF, h_yearsZ) 
f_years <-c(f_yearsA, f_yearsB, f_yearsDB, f_yearsM,f_yearsF, f_yearsZ) 
earth <-c(earthA, earthB, earthDB, earthM, earthF, earthZ) 
output <-c(outputA, outputB, outputDB, outputM, outputF, outputZ) 
extension <-c(extensionA, extensionB, extensionDB,extensionM,extensionF,extensionZ) 

# same as above but need to re-do as here outputs are from a different set of models 
yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_ipsl_CMIP6<-list()

# NOTE: warning for Feisty are OK - see above 

for (i in 1:length(mod_ipsl)){

  # i = 5
  # file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/APECOSM/_tmp/ipsl-cm6a-lr/historical/apecosm_ipsl-esm4_nobc_historical_nat_default_tcb_global_monthly_1950_1989.nc"
  filename<-paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[2],"/", tolower(mod_ipsl[i]), earth[i], "historical_nat_default_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], extension[i])
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE, CMIP =  6)
  
  filename <- paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), earth[i], "ssp126_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE, CMIP = 6)
  
  filename <- paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), earth[i], "ssp585_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE,CMIP = 6)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_ipsl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP6)[[i]]<-mod_ipsl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_ipsl_CMIP6)

# add EcoTrpoh IPSL ----
# naming mistakes that complicate uploading - Matthias check will fix them 
# write function for ecothroph 

time1_h = 1990 
time2_h = 1999
time1_f = 2090 # here the file is one so need to read-in the same file and  use it to calculate these averages
time2_f = 2099

averageFishCDF_EcoTroph<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE){
  
  # Open the netcdf file
  nc <- nc_open(file)
  var <-names(nc$var)
  # Extract important information
  data_attributes <- ncatt_get(nc, var) # variable is called "Band1" instead of "tcb"
  main_title <- data_attributes$long_field_name
  data_units <- data_attributes$units
    
  lon <- ncvar_get(nc, "lon")
  lat <- ncvar_get(nc, "lat")

  # time_vector <- convert_model_dates_CMIP6(nc, model_type) 
  # new convert_model_dates_CMIP6 for this model 
  time_months <- ncvar_get(nc, "time")
  print(nc$dim$time$units) # annual since 1950.....
  yearmonth = as.yearmon("1950-01")
  time_months = floor(as.numeric(as.yearmon(yearmonth + seq(0, (length(time_months) - 1)))))
  time_vector<-time_months
  print(time_months[1])
  print(time_months[length(time_months)])
  # print("but  hist and fut will extract at different time points")

  #  opposite of averaging the whole period ... line 488 in original function
  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  temp_array1 <-ncvar_get(nc, var)[, , tpte$start_point_to_extract:tpte$end_point_to_extract]
  # Extract averages
  for (ii in 1:length(lon)){
    for (jj in 1:length(lat))
      {
      # Fill in 2D matrix of whole time-period averages 
      new_var_mat[ii, jj] = mean(temp_array1[ii, jj, ])
    }
    }
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

if(can_model_units_be_standardized(data_units, convert_to_kg_km))
    {
      new_var_mat = new_var_mat * 1000
      data_units = "kg km-2" 
      }
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

# hist is the beginning of the future files and  I am assuming is the same for both futures 
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc"
hist<-averageFishCDF_EcoTroph(file, time1_h, time2_h)
fut126<-averageFishCDF_EcoTroph(file, time1_f, time2_f)
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp585_nat_default_tcb_annual_1950_2100.nc"
fut585<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$EcoTroph<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add EcoOcean IPSL ----

# this is very different as inputs are RDS files ... I hope it changes so that we don't have to guess stuff

averageFishCDF_EcoOcean<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE, type = "hist"){
  
  # data_ipsl_CMIP6$BOATS$hist
  # time1 = time1_h
  # time2 = time2_h
  # type = "fut"
  
  # Open the netcdf file
  nc <- file
  # Extract important information
  data_attributes <- "guess" # should be "tcb"
  main_title <- "guess"
  data_units <- "guess"
    
  lon <- data_ipsl_CMIP6$BOATS$hist$lon
  lat <- data_ipsl_CMIP6$BOATS$hist$lat

  # time_vector <- convert_model_dates_CMIP6(nc, model_type) 
  time_months <- seq(1, dim(nc)[3])
  
  if(type == "hist"){
    yearmonth = as.yearmon("1949-12") + time_months[1] / 12
    }else{
      yearmonth = as.yearmon("2006-01") + time_months[1] / 12 # this should be 2015 for CMIP6 but these files adopted CMIP5 convention
      }

  time_months = as.yearmon(yearmonth + seq(0, (length(time_months) - 1)) / 12)     
  tail(time_months)
  time_vector<-time_months
  print(time_months[1])
  print(time_months[length(time_months)])

  # line 488 in original function
  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  temp_array1 <-nc[, , tpte$start_point_to_extract:tpte$end_point_to_extract]
  dim(temp_array1)
  
  # Extract averages
  for (ii in 1:length(lon)){
    for (jj in 1:length(lat))
      {
      # Fill in 2D matrix of whole time-period averages 
      new_var_mat[ii, jj] = mean(temp_array1[ii, jj, ])
    }
    }
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

  # this should be done when we know the data units 
  new_var_mat = new_var_mat * 1000
  data_units = "kg km-2" 
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_historical_nosoc_default_tcb_global_monthly_1950-2005.RDS")
hist<-averageFishCDF_EcoOcean(file, time1_h, time2_h, type = "hist")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp126_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut126<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp585_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut585<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$EcoOcean<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add DBEM IPSL ----

# these are RData files similar to EcoOcean but the data layout is very different

averageFishCDF_DBEM<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE){
  
  # # data_ipsl_CMIP6$BOATS$hist
  # time1 = time1_h
  # time2 = time2_h
  # type = "hist"
  
  # Open the netcdf file
  nc <- file
  # Extract important information
  data_attributes <- "tcb"
  main_title <- "guess"
  data_units <- "guess"
    
  lon <- unique(coord$lon)
  lat <- unique(coord$lat)

  # time_vector <- convert_model_dates_CMIP6(nc, model_type) 
  time_months <- seq(1951, 2100)
  yearmonth = as.yearmon("1951-01")

  time_months = as.yearmon(yearmonth + seq(0, (length(time_months) - 1)))     
  time_vector<-time_months
  print(time_months[1])
  print(time_months[length(time_months)])

  # line 488 in original function
  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  # dimension and data format are different than for other models, so need different way of extracting data. GRID CELL X YEAR
  temp_array1 <-nc[,tpte$start_point_to_extract:tpte$end_point_to_extract]
  # Extract averages
  new_var_vec<-rowMeans(temp_array1)
  new_var_df<-cbind(coord, new_var_vec)
  new_var_df<-new_var_df[,-1]
  library(reshape2)
  new_var_mat<-acast(new_var_df, lon~lat, value.var="new_var_vec")
  
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

  # this should be done when we know the data units 
  new_var_mat = new_var_mat * 1000
  data_units = "kg km-2" 
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

coord<-read.delim("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/Lat_Lon.txt", header = FALSE, sep = ",")
colnames(coord)<-c("grid", "lon", "lat")
file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6IPSL26F0_t2_Abd.RData")
file<-sppfnlmap
hist<-averageFishCDF_DBEM(file, time1_h, time2_h)
fut126<-averageFishCDF_DBEM(file, time1_f, time2_f)
file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6IPSL85F0_t2_Abd.RData")
file<-sppfnlmap
fut585<-averageFishCDF_DBEM(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$DBEM<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# extract data GFDL ---- 

mod_gfdl <- c("BOATS","DBPM" ,"MACROECOLOGICAL","ZooMSS", "FEISTY") 

h_years <-c(h_yearsB,h_yearsDB, h_yearsM, h_yearsZ,h_yearsF) 
f_years <-c(f_yearsB,f_yearsDB, f_yearsM, f_yearsZ, f_yearsF) 
earth<-c("_gfdl-esm4_nobc_","_gfdl-esm4_nobasd_","_gfdl-esm4_nobc_","_gfdl-esm4_nobasd_","_gfdl-esm4_nobasd_")
output <-c(outputB,outputDB, outputM, outputZ, outputF) 
extension <-c(extensionB, extensionDB,extensionM, extensionZ, extensionF) 

yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_gfdl_CMIP6<-list()

for (i in 1:length(mod_gfdl)){

  # i = 4
  filename<-paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[2],"/", tolower(mod_gfdl[i]), earth[i], "historical_nat_default_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], extension[i])
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE, CMIP =  6)

  filename <- paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[3], "/", tolower(mod_gfdl[i]), earth[i], "ssp126_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE, CMIP = 6)
  
  filename <- paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[3], "/", tolower(mod_gfdl[i]), earth[i], "ssp585_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE,CMIP = 6)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_gfdl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP6)[[i]]<-mod_gfdl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_gfdl_CMIP6)

# add EcoTroph GFDL ----

# hist is the beginning of the future files and  I am assuming is the same for both futures 
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/gfdl-esm4/future/ecotroph_gfdl-esm4_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc"
hist<-averageFishCDF_EcoTroph(file, time1_h, time2_h)
fut126<-averageFishCDF_EcoTroph(file, time1_f, time2_f)
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/gfdl-esm4/future/ecotroph_gfdl-esm4_nobc_ssp585_nat_default_tcb_annual_1950_2100.nc"
fut585<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
data_gfdl_CMIP6$EcoTroph<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

names(data_gfdl_CMIP6)

# add EcoOcean GFDL ----

file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_gfdl_nobc_historical_nosoc_default_tcb_global_monthly_1950-2005.RDS")
hist<-averageFishCDF_EcoOcean(file, time1_h, time2_h, type = "hist")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp126_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut126<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp585_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut585<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP6$EcoOcean<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add DBEM GFDL ----

file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6GFDL26F0_t2_Abd.RData")
file<-sppfnlmap
hist<-averageFishCDF_DBEM(file, time1_h, time2_h)
fut126<-averageFishCDF_DBEM(file, time1_f, time2_f)
file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6GFDL85F0_t2_Abd.RData")
file<-sppfnlmap
fut585<-averageFishCDF_DBEM(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP6$DBEM<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

```

# Plot global ISIMIP3b model outputs

```{r plot CMIP6}

########## first you need to FLIP MATRICES 

fliplr_matrix<- function(data_to_flip){
  temp= data_to_flip
  for (ii in 1:dim(data_to_flip)[2])
    data_to_flip[,ii] = temp[,dim(data_to_flip)[2] - ii + 1]
  
  data_to_flip
}

# plot IPSL ----

# I re-grid everything from -180 to 180 inside the plot function
# FEISTY should be an example of the final/Mathias checked file (though still from -179.5, as used old inputs) and apecosm should be en example of model using the newest inputs (-180 to 180).... 
data_ipsl_CMIP6$DBPM$hist$lon
data_ipsl_CMIP5$DBPM$hist$lon
data_ipsl_CMIP6$ZooMSS$hist$lon
data_ipsl_CMIP5$ZooMSS$hist$lon
# tit <- paste("a")
# trial<-plot_FISH_MIP(data_ipsl_CMIP6$DBPM$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)")

data_ipsl_CMIP6$APECOSM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$hist$fishvar)
data_ipsl_CMIP6$APECOSM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$fut126$fishvar)
data_ipsl_CMIP6$APECOSM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$fut585$fishvar)
data_ipsl_CMIP6$APECOSM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$diff_2p6)
data_ipsl_CMIP6$APECOSM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$diff_8p5)

# not necessary anymore ...! why?! with the new runs
dim(data_ipsl_CMIP6$DBPM$hist$fishvar)
image(data_ipsl_CMIP6$DBPM$diff_8p5)
image(data_ipsl_CMIP6$APECOSM$diff_8p5)
image(data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5)
# data_ipsl_CMIP6$DBPM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBPM$hist$fishvar)
# data_ipsl_CMIP6$DBPM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBPM$fut126$fishvar)
# data_ipsl_CMIP6$DBPM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBPM$fut585$fishvar)
# data_ipsl_CMIP6$DBPM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$DBPM$diff_2p6)
# data_ipsl_CMIP6$DBPM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$DBPM$diff_8p5)

data_ipsl_CMIP6$MACROECOLOGICAL$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$hist$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$fut126$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$fut585$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$diff_2p6)
data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5)

data_ipsl_CMIP6$ZooMSS$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$hist$fishvar)
data_ipsl_CMIP6$ZooMSS$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$fut126$fishvar)
data_ipsl_CMIP6$ZooMSS$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$fut585$fishvar)
data_ipsl_CMIP6$ZooMSS$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$diff_2p6)
data_ipsl_CMIP6$ZooMSS$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$diff_8p5)

data_ipsl_CMIP6$FEISTY$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$hist$fishvar)
data_ipsl_CMIP6$FEISTY$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$fut126$fishvar)
data_ipsl_CMIP6$FEISTY$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$fut585$fishvar)
data_ipsl_CMIP6$FEISTY$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$diff_2p6)
data_ipsl_CMIP6$FEISTY$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$diff_8p5)

data_ipsl_CMIP6$EcoTroph$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$hist$fishvar)
data_ipsl_CMIP6$EcoTroph$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$fut126$fishvar)
data_ipsl_CMIP6$EcoTroph$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$fut585$fishvar)
data_ipsl_CMIP6$EcoTroph$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$diff_2p6)
data_ipsl_CMIP6$EcoTroph$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$diff_8p5)

data_ipsl_CMIP6$EcoOcean$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$hist$fishvar)
data_ipsl_CMIP6$EcoOcean$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$fut126$fishvar)
data_ipsl_CMIP6$EcoOcean$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$fut585$fishvar)
data_ipsl_CMIP6$EcoOcean$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$diff_2p6)
data_ipsl_CMIP6$EcoOcean$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$diff_8p5)

data_ipsl_CMIP6$DBEM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$hist$fishvar)
data_ipsl_CMIP6$DBEM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$fut126$fishvar)
data_ipsl_CMIP6$DBEM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$fut585$fishvar)
data_ipsl_CMIP6$DBEM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$DBEM$diff_2p6)
data_ipsl_CMIP6$DBEM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$DBEM$diff_8p5)


move_hemispheres<- function(data_to_flip){
  temp= data_to_flip
  data_to_flip[1:180,] = temp[181:360,]
  data_to_flip[181:360,] = temp[1:180,]
  data_to_flip
}
  
data_ipsl_CMIP6$EcoOcean$hist$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$hist$fishvar)
data_ipsl_CMIP6$EcoOcean$fut126$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$fut126$fishvar)
data_ipsl_CMIP6$EcoOcean$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$fut585$fishvar)
data_ipsl_CMIP6$EcoOcean$diff_2p6<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$diff_2p6)
data_ipsl_CMIP6$EcoOcean$diff_8p5<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$diff_8p5)

map_ipsl585_CMIP6<-list()
names(data_ipsl_CMIP6)

model_type_ipsl<-ifelse(names(data_ipsl_CMIP6) == "DBEM","DBEM", NA) # this is because DBEM need to be plotted in 0.5 deg

for (i in 1:length(data_ipsl_CMIP6)){ 
  
  # i = 3
  tit <- paste(names(data_ipsl_CMIP6)[i], "IPSL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_ipsl585_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl585_CMIP6)[[i]]<-names(data_ipsl_CMIP6)[[i]]
  
  rm(tit)
  
}

names(map_ipsl585_CMIP6)
map_ipsl585_CMIP6$DBPM

# plot GFDL ----

# flip matrix 

data_gfdl_CMIP6$MACROECOLOGICAL$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$hist$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$fut126$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$fut585$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$diff_2p6)
data_gfdl_CMIP6$MACROECOLOGICAL$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$diff_8p5)

data_gfdl_CMIP6$ZooMSS$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$hist$fishvar)
data_gfdl_CMIP6$ZooMSS$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$fut126$fishvar)
data_gfdl_CMIP6$ZooMSS$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$fut585$fishvar)
data_gfdl_CMIP6$ZooMSS$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$diff_2p6)
data_gfdl_CMIP6$ZooMSS$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$diff_8p5)

data_gfdl_CMIP6$FEISTY$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$hist$fishvar)
data_gfdl_CMIP6$FEISTY$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$fut126$fishvar)
data_gfdl_CMIP6$FEISTY$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$fut585$fishvar)
data_gfdl_CMIP6$FEISTY$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$diff_2p6)
data_gfdl_CMIP6$FEISTY$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$diff_8p5)

data_gfdl_CMIP6$EcoTroph$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$hist$fishvar)
data_gfdl_CMIP6$EcoTroph$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$fut126$fishvar)
data_gfdl_CMIP6$EcoTroph$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$fut585$fishvar)
data_gfdl_CMIP6$EcoTroph$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$diff_2p6)
data_gfdl_CMIP6$EcoTroph$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$diff_8p5)

data_gfdl_CMIP6$EcoOcean$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$hist$fishvar)
data_gfdl_CMIP6$EcoOcean$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$fut126$fishvar)
data_gfdl_CMIP6$EcoOcean$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$fut585$fishvar)
data_gfdl_CMIP6$EcoOcean$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$diff_2p6)
data_gfdl_CMIP6$EcoOcean$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$diff_8p5)

data_gfdl_CMIP6$DBEM$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$hist$fishvar)
data_gfdl_CMIP6$DBEM$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$fut126$fishvar)
data_gfdl_CMIP6$DBEM$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$fut585$fishvar)
data_gfdl_CMIP6$DBEM$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$DBEM$diff_2p6)
data_gfdl_CMIP6$DBEM$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$DBEM$diff_8p5)

# move hemisphere  
data_gfdl_CMIP6$EcoOcean$hist$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$hist$fishvar)
data_gfdl_CMIP6$EcoOcean$fut126$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$fut126$fishvar)
data_gfdl_CMIP6$EcoOcean$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$fut585$fishvar)
data_gfdl_CMIP6$EcoOcean$diff_2p6<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$diff_2p6)
data_gfdl_CMIP6$EcoOcean$diff_8p5<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$diff_8p5)

map_gfdl585_CMIP6<-list()
names(data_gfdl_CMIP6)

model_type_gfdl<-ifelse(names(data_gfdl_CMIP6) == "DBEM","DBEM", NA) # this is because DBEM need to be plotted in 0.5 deg

names(data_gfdl_CMIP6)

for (i in 1:length(data_gfdl_CMIP6)){ 
  
  # i = 1
  tit <- paste(names(data_gfdl_CMIP6)[i], "GFDL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_gfdl585_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl585_CMIP6)[[i]]<-names(data_gfdl_CMIP6)[[i]]
  
  rm(tit)
  
}

names(map_gfdl585_CMIP6)
map_gfdl585_CMIP6$DBPM

```

# Deal with model set 

```{r}

# # remove models that you don't want to include first 
data_ipsl_CMIP6$APECOSM<-NULL
data_gfdl_CMIP6$APECOSM<-NULL
data_gfdl_CMIP6$DBPM<-NULL # need to update when white parallel lines problem is solved, but the code doeas allow for DBPM inclusion now 


```

# Model average for CMIP6

```{r}

# RCP 8.5
# # MAKE SURE THAT ALL MATRICES ARE ON ONE DEGREE SCALE - if not see CMIP5 above for DBEM 
lons_to_use = seq(1,719,2)
lats_to_use = seq(1,359,2)

data_ipsl_CMIP6$DBEM$diff_8p5 = data_ipsl_CMIP6$DBEM$diff_8p5[lons_to_use, lats_to_use] 
data_gfdl_CMIP6$DBEM$diff_8p5 = data_gfdl_CMIP6$DBEM$diff_8p5[lons_to_use, lats_to_use] 

res_ipsl<-model_stat(data_ipsl_CMIP6)
model_average_ipsl_CMIP6<-res_ipsl$model_average
model_sd_ipsl_CMIP6<-res_ipsl$model_sd
model_agreement_ipsl_CMIP6<- res_ipsl$model_agreement

res_gfdl<-model_stat(data_gfdl_CMIP6)
model_average_gfdl_CMIP6<-res_gfdl$model_average
model_sd_gfdl_CMIP6<-res_gfdl$model_sd
model_agreement_gfdl_CMIP6<- res_gfdl$model_agreement

res_all<-model_stat(c(data_ipsl_CMIP6, data_gfdl_CMIP6))
model_average_all_CMIP6<-res_all$model_average
model_sd_all_CMIP6<-res_all$model_sd
model_agreement_all_CMIP6<- res_all$model_agreement

# # define title IPSL
# maptitle_average = paste("Mean % change IPSL RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
# maptitle_sd = paste("Standard Deviation IPSL RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
# maptitle_agreement = paste("Agreement IPSL RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
# 
# # Plot the model average and standard deviation
# avarage_CMIP6_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
# sd_CMIP6_ipsl<-plot_FISH_MIP(model_sd_ipsl_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
# agreement_CMIP6_ipsl<-plot_FISH_MIP(model_agreement_ipsl_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") # why is this white along all coasts?!
# 
# # define title GFDL
# maptitle_average = paste("Mean % change GFDL RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
# maptitle_sd = paste("Standard Deviation GFDL RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
# maptitle_agreement = paste("Agreement GFDL RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
# 
# # Plot the model average and standard deviation
# avarage_CMIP6_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
# sd_CMIP6_gfdl<-plot_FISH_MIP(model_sd_gfdl_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
# agreement_CMIP6_gfdl<-plot_FISH_MIP(model_agreement_gfdl_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") 

# define title All
maptitle_average = paste("Mean % change RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
maptitle_agreement = paste("Agreement RCP 8.5, 1990s to 2090s CMIP6", sep=" ")

# Plot the model average and standard deviation
avarage_CMIP6_all<-plot_FISH_MIP(model_average_all_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP6_all<-plot_FISH_MIP(model_sd_all_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP6_all<-plot_FISH_MIP(model_agreement_all_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") 

# plot averadge by esm 
avarage_CMIP6_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP6, "Mean % change RCP 8.5, 1990s to 2090s CMIP6 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP6_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP6, "Mean % change RCP 8.5, 1990s to 2090s CMIP6 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

```

# save outputs ISIMIP3b temp 

```{r}

data_summaries_CMIP6<-list(res_all= res_all, res_ipsl = res_ipsl, res_gfdl = res_gfdl)
map_summaries_CMIP6<-list(avarage_CMIP6_all = avarage_CMIP6_all, sd_CMIP6_all = sd_CMIP6_all, agreement_CMIP6_all = agreement_CMIP6_all, avarage_CMIP6_ipsl = avarage_CMIP6_ipsl, avarage_CMIP6_gfdl = avarage_CMIP6_gfdl)
save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_noApecosm.RData")

```

# load data 

```{r}

rm(list=ls())
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5.RData")
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_noApecosm.RData")

```

# Load libraries for netcdf and define variables

```{r load CMIP5}

library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

# variables 
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values = c(0,10000) # these need to change for each model? 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c(low = "#fdb863", mid = "#f7f7f7", high = "#b2abd2") # for delta plots (between cmips change) # purple to green shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# Delta plot 

```{r}

# get lat and long from random file 
filename<-"ZooMSS/_tmp/gfdl-esm4/future/zoomss_gfdl-esm4_nobasd_ssp585_nat_default_tcb_global_annual_2015_2100.nc"
directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/"
nc <- nc_open(paste(directory, filename, sep = ""))
longitude <- ncvar_get(nc, "lon")
latitude <- ncvar_get(nc, "lat")

delta_average_limits = c(-100, 100)
delta_sd_limits = c(0,100)

# calculate delta as scatter plot of CMIP5 vs CMIP6

delta_fun<-function(data5, data6, plot_limits = delta_limits, labels){
  
  # data5 = model_average_all_CMIP5
  # data6 = model_average_all_CMIP6
  
  # transform in df with lat and long 
  delta_CMIP5<-as.data.frame(data5) %>% 
    `colnames<-`(latitude) %>% 
    mutate(lon = longitude) %>% 
    gather(lat, value_cmip5, -lon) 

  delta_CMIP6<-as.data.frame(data6) %>% 
    `colnames<-`(latitude) %>% 
    mutate(lon = longitude) %>% 
    gather(lat, value_cmip6, -lon) 

  # combine 
  delta<-delta_CMIP5 %>% 
    full_join(delta_CMIP6) # %>% 
    # mutate(color = ifelse(lat> 66.5 | lat < -66.5, "polar", ifelse(lat <23.5 & lat> -23.5, "tropic", "temperate"))) # but need to fix code to appropriately consider ranges - also could color by temperature? See Ryan?
  
  st<-summary(lm(delta$value_cmip6~delta$value_cmip5))
  int = st$coefficients[1,1]
  sl = st$coefficients[2,1]
  rsqr = st$r.squared
  
  # plot 
  delta_plot<-ggplot(delta, aes(x = value_cmip5, y = value_cmip6))+
    geom_point(color = "grey70", alpha=0.5, shape = 16)+ # alpha=0.1
    geom_abline()+
    geom_vline(xintercept = 0, linetype = "dashed")+
    geom_hline(yintercept = 0, linetype = "dashed")+
    xlim(plot_limits)+
    ylim(plot_limits)+
    xlab(labels[1]) + 
    ylab(labels[2]) + 
    # geom_abline(intercept = int, slope = sl, color = "red")+ # this does not give exactly the same line... 
    geom_smooth(method='lm', se = FALSE, formula= y~x)+
    annotate("text", label = paste("r = ", rsqr), x = -75, y = 75)+
    theme_bw()+
    theme(text = element_text(size=18),
          axis.title.y = element_text(vjust=0.4, size = 12),
          axis.title.x = element_text(vjust=0.3, size = 12),
          # axis.text.x = element_text(angle=90, hjust=0.5),
          panel.grid.major = element_blank(), 
          strip.background =element_rect(fill="white"),
          legend.position = "none")
  delta_plot
  
  return(delta_plot = delta_plot)
}

delta_average_ipsl<-delta_fun(data_summaries_CMIP5$res_ipsl$model_average, data_summaries_CMIP6$res_ipsl$model_average, delta_average_limits, labels = c("Biomass mean % change IPSL RCP 8.5 CMIP5","Biomass mean % change IPSL RCP 8.5 CMIP6"))
delta_sd_ipsl<-delta_fun(data_summaries_CMIP5$res_ipsl$model_sd, data_summaries_CMIP6$res_ipsl$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 8.5 CMIP5","Biomass SD IPSL RCP 8.5 CMIP6"))

delta_average_gfdl<-delta_fun(data_summaries_CMIP5$res_gfdl$model_average, data_summaries_CMIP6$res_gfdl$model_average, delta_average_limits, labels = c("Biomass mean % change GFDL RCP 8.5 CMIP5","Biomass mean % change GFDL RCP 8.5 CMIP6"))
delta_sd_gfdl<-delta_fun(data_summaries_CMIP5$res_gfdl$model_sd, data_summaries_CMIP6$res_gfdl$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 8.5 CMIP5","Biomass SD IPSL RCP 8.5 CMIP6"))

delta_average_all<-delta_fun(data_summaries_CMIP5$res_all$model_average, data_summaries_CMIP6$res_all$model_average, delta_average_limits,labels = c("Biomass mean % change RCP 8.5 CMIP5","Biomass mean % change RCP 8.5 CMIP6"))
delta_sd_all<-delta_fun(data_summaries_CMIP5$res_all$model_sd, data_summaries_CMIP6$res_all$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 8.5 CMIP5","Biomass SD IPSL RCP 8.5 CMIP6"))

# delta map 
# option 1 - subtract (julia) - OK
delta_map_data_all<-data_summaries_CMIP6$res_all$model_average - data_summaries_CMIP5$res_all$model_average
maptitle_detla<-"Delta (CMIP6 change - CMIP5 change)"
delta_map_all_difference<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 
# if (+1) - (+5) = -4 # CMIP6 decreased 4 times
# if (+1) - (-5) = 6 # CMIP6 increased 6 times 
# if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
# if (-1) - (-5) = 4 # CMIP6 increased 4 times 
# e.g. 
# model_average_all_CMIP5 = -5 (tcb 5% decrease between 1990 and 2090) # where model_average_all_CMIP5 is the mean of diff_8p5 (diff in tcb between the 2 decades) across all models
# model_average_all_CMIP6 = -3 (tcb 3% decrease between 1990 and 2090)
# -3 - -5 = 2 CMIP6 decreased less than CMIP5 by 2 - i.e. positive values indicate that tcb in CMIP6 increased more or decreased less between 1990 and 2090 than tcb in CMIP5 for the same period.  

delta_map_data_ipsl<-data_summaries_CMIP6$res_ipsl$model_average - data_summaries_CMIP5$res_ipsl$model_average
maptitle_detla<-"Delta IPSL (CMIP6 change - CMIP5 change)"
delta_map_ipsl_difference<-plot_FISH_MIP(delta_map_data_ipsl, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_gfdl<-data_summaries_CMIP6$res_gfdl$model_average - data_summaries_CMIP5$res_gfdl$model_average
maptitle_detla<-"Delta GFDL (CMIP6 change - CMIP5 change)"
delta_map_gfdl_difference<-plot_FISH_MIP(delta_map_data_gfdl, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

# # option 2 divide (Derek but in another contest as here we have negative values so we use the below)
# delta_map_data_all<-(model_average_all_CMIP6 / model_average_all_CMIP5) * 100 - 100
# maptitle_detla<-"Delta ((CMIP6 change / CMIP5 change)*100)"
# delta_map_all_divide<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-100, 100), colour_scheme = c("#fdb863", "#f7f7f7","#b2abd2"), coltitle = "Difference \nin \nchange \n", legend_ticks = 3)
# # if 1/5*100 - 100 = -80% # CMIP6 decreased
# # if 1/-5*100 - 100 = -120% # CMIP6 decreased - WRONG

# option 3 percentage - same as Julia above if you do abs() but less meaningful as inputs are already % 
# TO DO - DELETE
# delta_map_data_all<-((model_average_all_CMIP6 - model_average_all_CMIP5)/abs(model_average_all_CMIP5)) * 100
# maptitle_detla<-"Delta (((CMIP6 change - CMIP5 change)/|CMIP5 change|) * 100)"
# delta_map_all_percentage<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-100, 100), colour_scheme = c("#fdb863", "#f7f7f7","#b2abd2"), coltitle = "(%) Difference \nin \nchange \n", legend_ticks = 5)
# if ((1 - 5)/5)*100 = -80 # CMIP6 decreased 4 times
# if ((1 - -5)/5)*100 = 120 # CMIP6 increased 6 times 
# if ((-1 - 5)/-5)*100 = 120 # WRONG
# if ((-1 - -5)/-5)*100 = -80 # WRONG
# if ((-1 - 5)/5)*100 = -120 # CMIP6 decrease 6 times - ok if denominator is absolute
# if ((-1 - -5)/5)*100 = 80 # CMIP increase 4 times - ok if denominator is absolute

# agreement on the direction of change between CMIPs see model_stat. this gives 100%  agreement if biomass in both cmips is decreasing/increasing and 50% is they disagree... (agreement on the direction of change....but  does not tell you which direction.)
# create array with both matrices 
# TO DO - weight according to degree of change or used delta as an alpha factor - not particularly usefull... I decided not to do

trial<-array(NA, dim=c(dim(data_summaries_CMIP5$res_all$model_average)[1],dim(data_summaries_CMIP5$res_all$model_average)[2],2))
trial[,,1]<-data_summaries_CMIP5$res_all$model_average
trial[,,2]<-data_summaries_CMIP6$res_all$model_average
# apply model_stat code to calculate agreement in biomass changes between cmips
temp<-apply(trial, c(1,2), function(x) length(x[which(x>0)])) 
temp2<-apply(trial, c(1,2), function(x) length(x[which(!is.na(x))])) #
temp4<-temp/temp2
trial_data<-ifelse(is.na(temp4), NA, ifelse(temp4>0.5, temp4*100, (1-temp4)*100))
trial_data[which(trial_data ==100)]<-1
trial_data[which(trial_data ==50)]<-0
delta_map_all_agreement<-plot_FISH_MIP(trial_data, "CMIPs agreement on the direction of change", c(0,1) ,colour_scheme = colour_scheme3, coltitle = "CMIPs \nagreement", legend_ticks = 2) 

# # model's discrepancy from average (withing the CMIP6) 
# # can do with either IPSL or GFDL but not with ALL as you don't have a mean of the 2 for each model 
# delta_average_boats<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$BOATS$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_dbmp<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$DBPM$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_macroecological<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_feisty<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$FEISTY$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_zoomss<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$ZooMSS$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_ecotroph<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$EcoTroph$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# 
# # model's discrepancy from average (withing the CMIP5) 
# delta_average_boats_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$BOATS$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_dbmp_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$DBPM$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_macroecological_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$MACROECOLOGICAL$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_apecosm_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$APECOSM$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_ecoocean_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$EcoOcean$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))

```

# flip sign plot 

Similar but more sophisticated than agreement

```{r}

# highlights cells that have switched sign from CMIP5 to CMIP6

flip_sign<-function(temp, temp1){
  
  # find cells where the sign is opposite
  temp2<-temp*temp1 
  temp2<-ifelse(temp2<0, 1, 0) # if negative, sign flipped

  # consider only flipped sign in CMIP5 and CMIP6 matrices
  temp<-temp*temp2
  temp<-ifelse(temp==0, NA, temp)
  temp1<-temp1*temp2
  temp1<-ifelse(temp1==0, NA, temp1)
  # check
  # temp[1:10,1:10]
  # temp1[1:10,1:10]

  # from + to -
  # consider only cells that flipped from + (in cmip5) to - (in cmip6)
  temp_neg<-temp
  temp1_neg<-temp1
  temp_neg<-ifelse(temp_neg<0, NA, temp_neg) # SHOULD THESE BE >= 0 ??? 0 to positive or 0 to negative does not qualify as changing sign I think
  temp1_neg<-ifelse(temp1_neg>0, NA, temp1_neg)

  # by how much? # calcualte delta as above 
  data_negative<-temp1_neg - temp_neg # CMIP6 -CMIP5
  # if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
  # if (-5) - (+1) = -6 # CMIP6 decreased 6 times 
  # check 
  # temp[1,153] # positive 
  # temp1[1,153] # negative
  # trial[1,153]
  
  # from - to +
  # consider only cells that flipped from + (in cmip5) to - (in cmip6)
  temp_pos<-temp
  temp1_pos<-temp1
  temp_pos<-ifelse(temp_pos>0, NA, temp_pos)
  temp1_pos<-ifelse(temp1_pos<0, NA, temp1_pos)

  # by how much? # calcualte delta as above 
  data_positive<-temp1_pos - temp_pos # CMIP6 -CMIP5
  # if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
  # if (-5) - (+1) = -6 # CMIP6 decreased 6 times 
  # check 
  # temp[1,153] # positive 
  # temp1[1,153] # negative
  # trial[1,153]

  return(list(data_negative = data_negative, data_positive = data_positive))
}

flip_sign_data<-flip_sign(data_summaries_CMIP5$res_all$model_average, data_summaries_CMIP6$res_all$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data$data_negative))
c<-sum(!is.na(flip_sign_data$data_positive))
(b/a)*100
(c/a)*100

# plot
colour_scheme4 <- c(low = "#fc9617", mid = "#fecf95",  high = "#fef4e7")
maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in CMIP6"
map_sign_negative<-plot_FISH_MIP(flip_sign_data$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

colour_scheme5 <- c(low = "#f4f3f9", mid = "#bab4d7",  high = "#8479b7") 
maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in CMIP6"
map_sign_positive<-plot_FISH_MIP(flip_sign_data$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

# by esm now 
flip_sign_data_ipsl<-flip_sign(data_summaries_CMIP5$res_ipsl$model_average, data_summaries_CMIP6$res_ipsl$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data_ipsl$data_negative))
c<-sum(!is.na(flip_sign_data_ipsl$data_positive))
(b/a)*100
(c/a)*100

maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in IPSL CMIP6"
map_sign_negative_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in IPSL CMIP6"
map_sign_positive_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

flip_sign_data_gfdl<-flip_sign(data_summaries_CMIP5$res_gfdl$model_average, data_summaries_CMIP6$res_gfdl$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data_gfdl$data_negative))
c<-sum(!is.na(flip_sign_data_gfdl$data_positive))
(b/a)*100
(c/a)*100

maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in GFDL CMIP6"
map_sign_negative_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in GFDL CMIP6"
map_sign_positive_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

```

# save plot data that you have not saved yet 

```{r}

# delta plots and flipped signed figures data 
save(delta_average_all, delta_average_ipsl, delta_average_gfdl,flip_sign_data,flip_sign_data_ipsl,flip_sign_data_gfdl, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIPs_deltaFigures.RData")

```

# Put all maps together 

```{r multipanel plot}

library(patchwork)

# FIG 2 model average CMIP5, model average CMIP6, delta CMIP5 vs CMIP6
layout <- "
AB
C#
DE
"

pt<-map_summaries_CMIP5$avarage_CMIP5_all + map_summaries_CMIP6$avarage_CMIP6_all + delta_map_all_difference + map_sign_positive +
  map_sign_negative + plot_layout(design = layout)

# pdf(paste0(save_loc,"Fig2_new.pdf"), height=5, width=20) # when 3 maps only 
pdf(paste0(save_loc,"Fig2_new_noApecosm.pdf"), height=10, width=15) # when 3 maps only 
pt 
dev.off()

# FIG 2 model average CMIP5, model average CMIP6, delta CMIP5 vs CMIP6 by ESM 
layout <- "
AB
CD
EF
GH
IJ
"

# see what's already there 
# avarage_CMIP5_all<-avarage_CMIP5_all + ggtitle("A") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
# avarage_CMIP6_all<-avarage_CMIP6_all + ggtitle("B") + theme(plot.title = element_text(size = 16, face = "bold",hjust = 0))
# delta_map_all<-delta_map_all + ggtitle("C") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-map_summaries_CMIP5$avarage_CMIP5_ipsl + map_summaries_CMIP6$avarage_CMIP6_ipsl +
  map_summaries_CMIP5$avarage_CMIP5_gfdl + map_summaries_CMIP6$avarage_CMIP6_gfdl +
  delta_map_ipsl_difference + delta_map_gfdl_difference +
  map_sign_positive_ipsl + map_sign_negative_ipsl + 
  map_sign_positive_gfdl + map_sign_negative_gfdl + 
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig2_noApecosm_ipsl_gfdl.pdf"), height=20, width=15) 
pt 
dev.off()

# FIG S2
# All protocols models summaries (average, sd and agreement) 
# can  be done with GFDL or IPSL too 
# can be done with spp126 if 'diff_8p5' line 318 is changed too  

layout <- "
AB
CD
EF
"

pt<-map_summaries_CMIP5$avarage_CMIP5_all + map_summaries_CMIP6$avarage_CMIP6_all + # this is same as Fig2 first raw
    map_summaries_CMIP5$sd_CMIP5_all + map_summaries_CMIP6$sd_CMIP6_all +  
    map_summaries_CMIP5$agreement_CMIP5_all + map_summaries_CMIP6$agreement_CMIP6_all +  
    plot_layout(design = layout)

pt<-pt + plot_annotation(
  title = 'Spatial patterns of projected biomass changes RCP8.5 CMIP5 vs CMIP6, 1990s to 2090s
  ',
  theme = theme(plot.title = element_text(size = 20)))

pdf(paste0(save_loc,"FigS2_noApecosm.pdf"), height=10, width=15)
# tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
pt 
dev.off()

# FIG S3
# all models map of change IPSL spp585 CMIP5 vs CMIP6

layout <- "
AB 
CD
EF
GH
IJ
KL
#M
#N
"

pt<-map_ipsl585_CMIP5$DBPM + map_ipsl585_CMIP6$DBPM + # AB
    map_ipsl585_CMIP5$MACROECOLOGICAL + map_ipsl585_CMIP6$MACROECOLOGICAL +# CD
    map_ipsl585_CMIP5$DBEM + map_ipsl585_CMIP6$DBEM + # EF
    # map_ipsl585_CMIP5$APECOSM + map_ipsl585_CMIP6$APECOSM + # EF
    map_ipsl585_CMIP5$EcoOcean + map_ipsl585_CMIP6$EcoOcean + # GH
    map_ipsl585_CMIP5$BOATS+ map_ipsl585_CMIP6$BOATS + # IJ
    map_ipsl585_CMIP5$ZooMSS + map_ipsl585_CMIP6$ZooMSS + # KL
    map_ipsl585_CMIP6$FEISTY + # #M
    map_ipsl585_CMIP6$EcoTroph + # #N
  plot_layout(design = layout)
    
    
pt<-pt + plot_annotation(
  title = 'Change in tcb 1990s-2090s, IPSL RCP8.5 CMIP5 vs CMIP6',
  theme = theme(plot.title = element_text(size = 20)))

# try the smallest option possible.... 
jpeg(paste0(save_loc,"FigS3_noApecosm_ipsl.jpeg"), height=40, width=30, units ='in', res=300)
# tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_summary.tiff"), height=30, width=20, units ='in', res=300)
pt 
dev.off()

# FIG S4 - as S3 but with GFDL
# all models map of change GFDL spp585 CMIP5 vs CMIP6

layout <- "
AB
CD
EF
GH
IJ
#K
#L
"

pt<-# map_gfdl585_CMIP6$DBPM + # AB
    map_gfdl585_CMIP5$MACROECOLOGICAL + map_gfdl585_CMIP6$MACROECOLOGICAL +# CD
    map_gfdl585_CMIP5$DBEM + map_gfdl585_CMIP6$DBEM + # EF
    # map_gfdl585_CMIP5$APECOSM + map_gfdl585_CMIP6$APECOSM + # EF
    map_gfdl585_CMIP5$EcoOcean + map_gfdl585_CMIP6$EcoOcean + # GH
    map_gfdl585_CMIP5$BOATS+ map_gfdl585_CMIP6$BOATS + # IJ
    map_gfdl585_CMIP5$ZooMSS + map_gfdl585_CMIP6$ZooMSS + # KL
    map_gfdl585_CMIP6$FEISTY + # #M
    map_gfdl585_CMIP6$EcoTroph + # #N
  plot_layout(design = layout)


pt<-pt + plot_annotation(
  title = 'Change in tcb 1990s-2090s, GFDL RCP8.5 CMIP5 vs CMIP6',
  theme = theme(plot.title = element_text(size = 20)))

jpeg(paste0(save_loc,"FigS3_noApecosm_gfdl.jpeg"), height=40, width=30, units ='in', res=300)
pt
dev.off()

# # Delta mean over all models and all earth inputs  
# layout <- "
# A
# B
# C
# "
# 
# # delta_average_ipsl<-delta_average_ipsl + ggtitle("IPSL") + theme(plot.title = element_text(size = 12, face = "bold"))
# # delta_average_gfdl<-delta_average_gfdl + ggtitle("GFDL") + theme(plot.title = element_text(size = 12, face = "bold"))
# # delta_average_all<-delta_average_all + ggtitle("ALL") + theme(plot.title = element_text(size = 12, face = "bold"))
# 
# pt<-delta_average_ipsl + delta_average_gfdl + delta_average_all +
#     plot_layout(design = layout)
# 
# pt<-pt + plot_annotation(
#   title = 'Delta average RCP 8.5',
#   theme = theme(plot.title = element_text(size = 20)))

# pdf(paste0(save_loc,"delta_scatterplot.pdf"), height=12, width=8)
# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# pt 
# dev.off()

# # only all instead - can also be colored by lat?
# pdf(paste0(save_loc,"delta_scatterplot.pdf"), height=12, width=8)
# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# delta_average_all 
# dev.off()

```

# random and model-specific plots *can skyp*

```{r}
# Delta models ipsl vs mean over all model ipsl CMIP6 
# can do CMIP5 too

layout <- "
AB
CD
EF
"
# plot titles - should add to code creating plots above 
delta_average_boats<-delta_average_boats + ggtitle("BOATS") + theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_dbmp<-delta_average_dbmp + ggtitle("DBPM")+  theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_ecotroph<-delta_average_ecotroph + ggtitle("EcoTroph")+  theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_feisty<-delta_average_feisty + ggtitle("FEISTY")+  theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_macroecological<- delta_average_macroecological + ggtitle("MACROECOLOGICAL")+  theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_zoomss<- delta_average_zoomss + ggtitle("ZooMSS")+  theme(plot.title = element_text(size = 12, face = "bold"))

pt<-delta_average_boats + delta_average_dbmp + 
  delta_average_ecotroph + delta_average_feisty +
  delta_average_macroecological + delta_average_zoomss +
  plot_layout(design = layout)

pt<-pt + plot_annotation(
  title = 'Delta average models IPSL RCP 8.5 CMIP6',
  theme = theme(plot.title = element_text(size = 20)))

pdf(paste0(save_loc,"20201104_delta_models_cmip6_noApecosm.pdf"), height=10, width=15)
# tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
pt 
dev.off()

# for CMIP5 

layout <- "
AB
CD
"
# plot titles - should add to code creating plots above 
delta_average_boats_cmip5<-delta_average_boats_cmip5 + ggtitle("BOATS") + theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_dbmp_cmip5<-delta_average_dbmp_cmip5 + ggtitle("DBPM")+  theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_macroecological_cmip5<- delta_average_macroecological_cmip5 + ggtitle("MACROECOLOGICAL")+  theme(plot.title = element_text(size = 12, face = "bold"))
delta_average_ecoocean_cmip5<- delta_average_ecoocean_cmip5 + ggtitle("EcoOcean")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_apecosm_cmip5<- delta_average_apecosm_cmip5 + ggtitle("Apecosm")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_avarave_dbem_cmip5<- delta_average_dbem_cmip5 + ggtitle("DBEM")+  theme(plot.title = element_text(size = 12, face = "bold"))

pt<-delta_average_boats_cmip5 + delta_average_dbmp_cmip5 + 
  delta_average_macroecological_cmip5 + delta_average_ecoocean_cmip5 +
  # delta_average_apecosm_cmip5 + # delta_avarave_dbem_cmip5 +
  plot_layout(design = layout)

pt<-pt + plot_annotation(
  title = 'Delta average models IPSL RCP 8.5 CMIP5',
  theme = theme(plot.title = element_text(size = 20)))

pdf(paste0(save_loc,"20201104_delta_models_cmip5_noApecosm.pdf"), height=10, width=15)
# tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
pt 
dev.off()

```