---
title: "Plotting global models outputs"
author: "Camilla Novaglio & Derek Tittensor"
date: "04/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script analysis Marine Ecosystem Models' outputs. It is structured in three steps:

Step 1 extracts ocean biomass from MEMs netcdfs and collapses them into a time-averaged (1990s for the historical period and 2090s for future scenarios) spatial dataset (1 grid cell resolution) for CMIP5.  
Step 2 extracts ocean biomass from MEMs netcdfs and collapses them into a time-averaged (1990s for the historical period and 2090s for future scenarios) spatial dataset (1 grid cell resolution) for CMIP6.  
Step 3 load CMIP5 and CMIP6 data, averages the data across MEMs and scenarios and produces Figure 5 along with supplementary figures.  

# STEP 1 extract data CMIP5

## Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())

install_load <- function (this_package)  {   

   package <- c(this_package)
   if(package %in% rownames(installed.packages()))
        do.call('library', list(package))

    # if package is not installed locally, download, then load
    else {
        install.packages(package)
         do.call("library", list(package))
    }
}

### load/install libraries ###
install_load("grid")
install_load("zoo")
install_load("viridis")
install_load("tidyr")
install_load("dplyr")
install_load("ncdf4")
install_load("ggplot2")
install_load("patchwork")

### load helper scripts with functions to extract data from netcdfs ###
source("R/HelperScripts.r")
source("R/Funcs_maps.r")

### create folders where temporary data can be stored ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep1 = "temp_data"
ifelse(!dir.exists(file.path(mainDir, DirStep1)), dir.create(file.path(mainDir, DirStep1)), FALSE)

### define variables ###
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

### create folders where figures can be saved ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep2 = "figures"
ifelse(!dir.exists(file.path(mainDir, DirStep2)), dir.create(file.path(mainDir, DirStep2)), FALSE)
save_loc<-"../CMIP5vsCMIP6_data/figures/"

```

## Load libraries for plotting and define criteria 

```{r}

### Define color/legend limits ###
main_plot_colour_values = c(0,10000) 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)
mean_plot_colour_values = c(-50,50)
sd_plot_colour_values = c(0,50)
model_agreement_plot_colour_values = c(50,100)

#### define color schemes ###
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values 

### Download and process world outline ###
install_load("sf")
install_load("rnaturalearth")
install_load("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) 

### other mapping libraries ####
install_load("raster")
install_load("maptools")
install_load("RColorBrewer")
install_load("scales")

```

## Load global CMIP5 model data 

```{r}

# CMIP5 data location
directory = "../CMIP5vsCMIP6_data/fishmip_outputs/marine-fishery_global_ISIMIP2b/"
# directory = "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/"

# APECOSM ----
h_yearsA <- "1950_2005"
f_yearsA<- "2006_2100"
outputA<-"monthly"
oaA<-"no-oa"

# BOATS ----
h_yearsB <- "1971_2005"
f_yearsB<- "2006_2099"
outputB<-"monthly"
oaB<-"no-oa"

# DBEM ----
h_yearsD <- "1951_2005"
f_yearsD<- "2006_2099"
outputD<-"annual"
oaD<-"oa"

# DBPM ----
h_yearsDB <- "1950_2005"
f_yearsDB<- "2006_2100"
outputDB<-"monthly"
oaDB<-"no-oa"

# EcoOcean ----  
h_yearsE <- "1971_2005"
f_yearsE<- "2006_2100"
outputE<-"monthly"
oaE<-"no-oa"

# macroecological ----  
h_yearsM <- "1950_2005"
f_yearsM<- "2006_2100"
outputM<-"annual"
oaM<-"no-oa"

# extract data IPSL ---- 
h_years <-c(h_yearsA, h_yearsB, h_yearsD, h_yearsDB, h_yearsE, h_yearsM)
f_years <-c(f_yearsA, f_yearsB, f_yearsD, f_yearsDB, f_yearsE, f_yearsM)
output <-c(outputA, outputB, outputD, outputDB, outputE, outputM)
oa <-c(oaA, oaB, oaD, oaDB, oaE, oaM)

yearmonth1<- rep(as.yearmon("1990-01"), length(mod_ipsl))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- rep(as.yearmon("2090-01"), length(mod_ipsl))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_ipsl_CMIP5<-list()

for (i in 1:length(mod_ipsl)){

  filename<-paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[2],"/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_hist_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], ".nc4")
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_rcp2p6_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_rcp8p5_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_ipsl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

# add Zoom IPSL ----

# directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/historical/"
# filename<-"zoomss_ipsl-cm5a-lr_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"

directory_zoom<-paste0(directory, "ZooMSS/_tmp/historical/")

# hist
filename<-"zoomss_ipsl-cm5a-lr_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"
yearmonth1 = as.yearmon("1990-01")
yearmonth2 = as.yearmon("1999-01")
hist<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

# directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/future/"
# 126
directory_zoom<-paste0(directory, "ZooMSS/_tmp/future/")
filename<-"zoomss_ipsl-cm5a-lr_nobc_rcp26_nosoc_co2_tcb_global_annual_2006_2100.nc4"
yearmonth1 = as.yearmon("2090-01")
yearmonth2 = as.yearmon("2099-01")
fut126<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

# 585
filename<-"zoomss_ipsl-cm5a-lr_nobc_rcp85_nosoc_co2_tcb_global_annual_2006_2100.nc4"
fut585<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP5$ZooMSS<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# extract data GFDL ---- 

h_years <-c(h_yearsB, h_yearsD, h_yearsE, h_yearsM)
f_years <-c(f_yearsB, f_yearsD, f_yearsE, f_yearsM)
f_years[3]<-"2006_2099" # ecoOcean changes 
output <-c(outputB, outputD, outputE, outputM)
oa <-c(oaB, oaD, oaE, oaM)

yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_gfdl_CMIP5<-list()

for (i in 1:length(mod_gfdl)){

  filename<-paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[2],"/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_hist_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], ".nc4")
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[3], "/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_rcp2p6_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[3], "/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_rcp8p5_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_gfdl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

# add zoom GFDL ----

# directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/historical/"

# hist
directory_zoom<-paste0(directory, "ZooMSS/_tmp/historical/")
filename<-"zoomss_gfdl-esm2m_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"
yearmonth1 = as.yearmon("1990-01")
yearmonth2 = as.yearmon("1999-01")
hist<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

# directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/future/"
# 126
directory_zoom<-paste0(directory, "ZooMSS/_tmp/future/")
filename<-"zoomss_gfdl-esm2m_nobc_rcp26_nosoc_co2_tcb_global_annual_2006_2100.nc4"
yearmonth1 = as.yearmon("2090-01")
yearmonth2 = as.yearmon("2099-01")
fut126<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

# 585
filename<-"zoomss_gfdl-esm2m_nobc_rcp85_nosoc_co2_tcb_global_annual_2006_2100.nc4"
fut585<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP5$ZooMSS<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

```

## Plot global CMIP5 model outputs 

```{r map CMIP5}

## plot IPSL ----

# RCP 8.5

map_ipsl585_CMIP5<-list()

mod_ipsl<-c(mod_ipsl, "ZooMSS")
model_type_ipsl<-ifelse(mod_ipsl == "DBEM","DBEM", NA) # DBEM resolution is 0.5 deg

for (i in 1:length(data_ipsl_CMIP5)){ 
  
  tit <- paste(mod_ipsl[i], "IPSL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_ipsl585_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl585_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(tit)
  
}

### plot GFDL ----

mod_gfdl<-c(mod_gfdl, "ZooMSS")
model_type_gfdl<-ifelse(mod_gfdl == "DBEM","DBEM", NA) 
map_gfdl585_CMIP5<-list()

for (i in 1:length(data_gfdl_CMIP5)){ 
  
  tit <- paste(mod_gfdl[i], "GFDL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_gfdl585_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl585_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(tit)
  
}

# RCP 2.6

## plot IPSL ----

map_ipsl126_CMIP5<-list()

for (i in 1:length(data_ipsl_CMIP5)){ 
  
  tit <- paste(mod_ipsl[i], "IPSL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_ipsl126_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl126_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(tit)
  
}

### plot GFDL ----

map_gfdl126_CMIP5<-list()

for (i in 1:length(data_gfdl_CMIP5)){ 
  
  tit <- paste(mod_gfdl[i], "GFDL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_gfdl126_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl126_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(tit)
  
}

```

## Deal with model set 

```{r}

# if model set == "full", we are considering all models and creating figures for the Main Document, otherwise we are considering the subset of models considered in Lotze et al. 2019 and producing figures for the Supplemntary Information. 

set = "not_full"

if(set != "full"){
  data_ipsl_CMIP5$ZooMSS<-NULL
  data_gfdl_CMIP5$ZooMSS<-NULL 
}

```

## Model average for CMIP5 and plotting

```{r}

# RCP 8.5

# MAKE SURE THAT ALL MATRICES ARE ON ONE DEGREE SCALE
### DBEM - TAKE THE VALUE FROM CLOSE POINT
lons_to_use = seq(1,719,2)
lats_to_use = seq(1,359,2)

data_ipsl_CMIP5$DBEM$diff_8p5 = data_ipsl_CMIP5$DBEM$diff_8p5[lons_to_use, lats_to_use] 
data_gfdl_CMIP5$DBEM$diff_8p5 = data_gfdl_CMIP5$DBEM$diff_8p5[lons_to_use, lats_to_use] 

# model average
res_ipsl<-model_stat(data_ipsl_CMIP5, esm = 'diff_8p5')
model_average_ipsl_CMIP5<-res_ipsl$model_average
model_sd_ipsl_CMIP5<-res_ipsl$model_sd
model_agreement_ipsl_CMIP5<- res_ipsl$model_agreement

res_gfdl<-model_stat(data_gfdl_CMIP5, esm = 'diff_8p5')
model_average_gfdl_CMIP5<-res_gfdl$model_average
model_sd_gfdl_CMIP5<-res_gfdl$model_sd
model_agreement_gfdl_CMIP5<- res_gfdl$model_agreement

res_all<-model_stat(c(data_ipsl_CMIP5, data_gfdl_CMIP5), esm = 'diff_8p5')
model_average_all_CMIP5<-res_all$model_average
model_sd_all_CMIP5<-res_all$model_sd
model_agreement_all_CMIP5<- res_all$model_agreement 

# define titles
maptitle_average = paste("Mean % change RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
maptitle_agreement = paste("Agreement RCP 8.5, 1990s to 2090s CMIP5", sep=" ")

# Plot the model average and standard deviation
avarage_CMIP5_all<-plot_FISH_MIP(model_average_all_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP5_all<-plot_FISH_MIP(model_sd_all_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP5_all<-plot_FISH_MIP(model_agreement_all_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot averadge by esm 
avarage_CMIP5_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP5, "Mean % change RCP 8.5, 1990s to 2090s CMIP5 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP5_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP5, "Mean % change RCP 8.5, 1990s to 2090s CMIP5 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

# RCP 2.6

data_ipsl_CMIP5$DBEM$diff_2p6 = data_ipsl_CMIP5$DBEM$diff_2p6[lons_to_use, lats_to_use] 
data_gfdl_CMIP5$DBEM$diff_2p6 = data_gfdl_CMIP5$DBEM$diff_2p6[lons_to_use, lats_to_use] 

# model average
res_ipsl_126<-model_stat(data_ipsl_CMIP5, esm = 'diff_2p6')
model_average_ipsl_CMIP5_126<-res_ipsl_126$model_average
model_sd_ipsl_CMIP5_126<-res_ipsl_126$model_sd
model_agreement_ipsl_CMIP5_126<- res_ipsl_126$model_agreement

res_gfdl_126<-model_stat(data_gfdl_CMIP5, esm = 'diff_2p6')
model_average_gfdl_CMIP5_126<-res_gfdl_126$model_average
model_sd_gfdl_CMIP5_126<-res_gfdl_126$model_sd
model_agreement_gfdl_CMIP5_126<- res_gfdl_126$model_agreement

res_all_126<-model_stat(c(data_ipsl_CMIP5, data_gfdl_CMIP5), esm = 'diff_2p6')
model_average_all_CMIP5_126<-res_all_126$model_average
model_sd_all_CMIP5_126<-res_all_126$model_sd
model_agreement_all_CMIP5_126<- res_all_126$model_agreement 

# define titles
maptitle_average = paste("Mean % change RCP 2.6, 1990s to 2090s CMIP5", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 2.6, 1990s to 2090s CMIP5", sep=" ")
maptitle_agreement = paste("Agreement RCP 2.6, 1990s to 2090s CMIP5", sep=" ")

# Plot the model average and standard deviation

avarage_CMIP5_all_126<-plot_FISH_MIP(model_average_all_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP5_all_126<-plot_FISH_MIP(model_sd_all_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP5_all_126<-plot_FISH_MIP(model_agreement_all_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot average by ESMs 
avarage_CMIP5_ipsl_126<-plot_FISH_MIP(model_average_ipsl_CMIP5, "Mean % change RCP 2.6, 1990s to 2090s CMIP5 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP5_gfdl_126<-plot_FISH_MIP(model_average_gfdl_CMIP5, "Mean % change RCP 2.6, 1990s to 2090s CMIP5 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

```

## Save temporary output CMIP5 

```{r}

data_summaries_CMIP5<-list(res_all= res_all, res_ipsl = res_ipsl, res_gfdl = res_gfdl, res_all_126= res_all_126, res_ipsl_126 = res_ipsl_126, res_gfdl_126 = res_gfdl_126)

map_summaries_CMIP5<-list(avarage_CMIP5_all = avarage_CMIP5_all, sd_CMIP5_all = sd_CMIP5_all, agreement_CMIP5_all = agreement_CMIP5_all, avarage_CMIP5_ipsl = avarage_CMIP5_ipsl, avarage_CMIP5_gfdl = avarage_CMIP5_gfdl, avarage_CMIP5_all_126 = avarage_CMIP5_all_126, sd_CMIP5_all_126 = sd_CMIP5_all_126, agreement_CMIP5_all_126 = agreement_CMIP5_all_126, avarage_CMIP5_ipsl_126 = avarage_CMIP5_ipsl_126, avarage_CMIP5_gfdl_126 = avarage_CMIP5_gfdl_126)

if(set == "full"){
  # save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, map_ipsl126_CMIP5, map_gfdl126_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5.RData")
  save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, map_ipsl126_CMIP5, map_gfdl126_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "../CMIP5vsCMIP6_data/temp_data/data_CMIP5.RData")
}else{
  # save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, map_ipsl126_CMIP5, map_gfdl126_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5_reducedModelSet.RData")
  save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, map_ipsl126_CMIP5, map_gfdl126_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "../CMIP5vsCMIP6_data/temp_data/data_CMIP5_reducedModelSet.RData")
}

```


# STEP 2 extract data CMIP6

## Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())

install_load <- function (this_package)  {   

   package <- c(this_package)
   if(package %in% rownames(installed.packages()))
        do.call('library', list(package))

    # if package is not installed locally, download, then load
    else {
        install.packages(package)
         do.call("library", list(package))
    }
}

### load/install libraries ###
install_load("grid")
install_load("zoo")
install_load("viridis")
install_load("tidyr")
install_load("dplyr")
install_load("ncdf4")
install_load("ggplot2")
install_load("patchwork")
install_load("reshape2")

### load helper scripts with functions to extract data from netcdfs ###
source("R/HelperScripts.r")
source("R/Funcs_maps.r")

### create folders where temporary data can be stored ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep1 = "temp_data"
ifelse(!dir.exists(file.path(mainDir, DirStep1)), dir.create(file.path(mainDir, DirStep1)), FALSE)

### define variables ###
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

### create folders where figures can be saved ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep2 = "figures"
ifelse(!dir.exists(file.path(mainDir, DirStep2)), dir.create(file.path(mainDir, DirStep2)), FALSE)
save_loc<-"../CMIP5vsCMIP6_data/figures/"

```

## Load libraries for plotting and define criteria 

```{r}

### Define color/legend limits ###
main_plot_colour_values = c(0,10000) 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)
mean_plot_colour_values = c(-50,50)
sd_plot_colour_values = c(0,50)
model_agreement_plot_colour_values = c(50,100)

#### define color schemes ###
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values 

### Download and process world outline ###
install_load("sf")
install_load("rnaturalearth")
install_load("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) 

### other mapping libraries ####
install_load("raster")
install_load("maptools")
install_load("RColorBrewer")
install_load("scales")

```

## Load global CMIP6 model data

```{r load CMIP6}

# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/"
directory = "../CMIP5vsCMIP6_data/fishmip_outputs/marine-fishery_global_ISIMIP3b/"

mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL", "EcoTroph", "FEISTY", "ZooMSS") 
mod_ipsl <- c("APECOSM","BOATS","DBPM","MACROECOLOGICAL","FEISTY","ZooMSS") 

# APECOSM ----
h_yearsA <- "1850_2014"
f_yearsA<- "2015_2100"
earthA<-"_ipsl-esm4_nobc_" 
outputA<-"monthly"
extensionA<-".nc" 

# BOATS ----
h_yearsB <- "1950_2014"
f_yearsB<- "2015_2100"
earthB<-"_ipsl-cm6a-lr_nobc_"
outputB<-"monthly"
extensionB<-".nc"

# DBEM ----
# added below

# DBPM ----
h_yearsDB <- "1850_2014"
f_yearsDB<- "2015_2100"
earthDB<-"_ipsl-cm6a-lr_nobasd_"
outputDB<-"monthly" 
extensionDB <-".nc"

# EcoOcean ----  
# added below  

# macroecological ----  
h_yearsM <- "1950_2014"
f_yearsM<- "2015-2100"
earthM<-"_ipsl-cm6a-lr_nobc_"
outputM<-"annual"
extensionM<-".nc"

# EcoTroph ----  
h_yearsE <- "1950-2014"
f_yearsE<- "2015-2100"
earthE<-"_ipsl-cm6a_nobc_"
outputE<-"annual"
extensionE<-".nc"

# FEISTY ----  
h_yearsF <- "1950_2014"
f_yearsF<- "2015_2100"
earthF<-"_ipsl-cm6a-lr_nobasd_" 
outputF<-"monthly"
extensionF<-".nc"

# ZooMSS ----  
h_yearsZ <- "1950_2014"
f_yearsZ<- "2015_2100"
earthZ<-"_ipsl-cm6a-lr_nobasd_"
outputZ<-"annual"
extensionZ<-".nc"

# extract data IPSL ---- 
h_years <-c(h_yearsA,h_yearsB, h_yearsDB, h_yearsM,h_yearsF, h_yearsZ) 
f_years <-c(f_yearsA, f_yearsB, f_yearsDB, f_yearsM,f_yearsF, f_yearsZ) 
earth <-c(earthA, earthB, earthDB, earthM, earthF, earthZ) 
output <-c(outputA, outputB, outputDB, outputM, outputF, outputZ) 
extension <-c(extensionA, extensionB, extensionDB,extensionM,extensionF,extensionZ) 

# same as above but need to re-do as here outputs are from a different set of models
yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

# ## prepare data and fig for IPCC report: Laurent Bopp
# # reference year for maps: 1995-2014 to compare to 2081-2100
# 
# yearmonth1<- ifelse(output=="annual", as.yearmon("1995-01"), as.yearmon("1995-01"))
# yearmonth2<- ifelse(output!="annual", as.yearmon("2014-12"), as.yearmon("2014-01"))
# yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2081-01"), as.yearmon("2081-01"))
# yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_ipsl_CMIP6<-list()

# NOTE: warning for FEISTY are OK - see above 

for (i in 1:length(mod_ipsl)){

  filename<-paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[2],"/", tolower(mod_ipsl[i]), earth[i], "historical_nat_default_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], extension[i])
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE, CMIP =  6)
  
  filename <- paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), earth[i], "ssp126_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE, CMIP = 6)
  
  filename <- paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), earth[i], "ssp585_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE,CMIP = 6)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_ipsl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP6)[[i]]<-mod_ipsl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

# add EcoTrpoh IPSL ----

time1_h = 1990 
time2_h = 1999
time1_f = 2090 
time2_f = 2099

# # for IPCC
# time1_h = 1995
# time2_h = 2014
# time1_f = 2081
# time2_f = 2099

averageFishCDF_EcoTroph<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE){
  
  # Open the netcdf file
  nc <- nc_open(file)
  var <-names(nc$var)
  
  # Extract important information
  data_attributes <- ncatt_get(nc, var) # variable is called "Band1" instead of "tcb"
  main_title <- data_attributes$long_field_name
  data_units <- data_attributes$units
    
  lon <- ncvar_get(nc, "lon")
  lat <- ncvar_get(nc, "lat")
  time_months <- ncvar_get(nc, "time")
  
  yearmonth = as.yearmon("1950-01")
  time_months = floor(as.numeric(as.yearmon(yearmonth + seq(0, (length(time_months) - 1)))))
  time_vector<-time_months

  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  temp_array1 <-ncvar_get(nc, var)[, , tpte$start_point_to_extract:tpte$end_point_to_extract]
  # Extract averages
  for (ii in 1:length(lon)){
    for (jj in 1:length(lat))
      {
      # Fill in 2D matrix of whole time-period averages 
      new_var_mat[ii, jj] = mean(temp_array1[ii, jj, ])
    }
    }
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

if(can_model_units_be_standardized(data_units, convert_to_kg_km))
    {
      new_var_mat = new_var_mat * 1000
      data_units = "kg km-2" 
      }
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

# hist is the beginning of the future files 

# hist & 126
# file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc"
file<-paste0(directory,"EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc")
hist<-averageFishCDF_EcoTroph(file, time1_h, time2_h)
fut126<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

# 585
file<-paste0(directory,"EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp585_nat_default_tcb_annual_1950_2100.nc")
fut585<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$EcoTroph<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add EcoOcean IPSL ----

time1_h = as.yearmon("1990-01") 
time2_h = as.yearmon("1999-12")
time1_f = as.yearmon("2090-01")
time2_f = as.yearmon("2099-12")

# # for IPCC
# time1_h = as.yearmon("1995-01")
# time2_h = as.yearmon("2005-12") # PROBLEM here as historical runs are up to 2005, then we have protocols' projections.
# time1_f = as.yearmon("2081-01")
# time2_f = as.yearmon("2099-12")

averageFishCDF_EcoOcean<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE, type = "hist"){
    
  # Open the netcdf file
  nc <- file
  
  # Extract important information
  data_attributes <- "guess" # should be "tcb"
  main_title <- "guess"
  data_units <- "guess"
    
  lon <- data_ipsl_CMIP6$BOATS$hist$lon
  lat <- data_ipsl_CMIP6$BOATS$hist$lat

  time_months <- seq(1, dim(nc)[3])
  length(time_months)
  
  if(type == "hist"){
    yearmonth = as.yearmon("1949-12") + time_months[1] / 12
    }else{
      yearmonth = as.yearmon("2006-01") + time_months[1] / 12 # this should be 2015 for CMIP6 but these files adopted CMIP5 convention
      }

  time_months = as.yearmon(yearmonth + seq(0, (length(time_months) - 1)) / 12)     
  time_vector<-time_months

  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  temp_array1 <-nc[, , tpte$start_point_to_extract:tpte$end_point_to_extract]
  dim(temp_array1)
  
  # Extract averages
  for (ii in 1:length(lon)){
    for (jj in 1:length(lat))
      {
      # Fill in 2D matrix of whole time-period averages 
      new_var_mat[ii, jj] = mean(temp_array1[ii, jj, ])
    }
    }
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

  # this should be done when we know the data units 
  new_var_mat = new_var_mat * 1000
  data_units = "kg km-2" 
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

# hist
file<-readRDS(paste0(directory,"EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_historical_nosoc_default_tcb_global_monthly_1950-2005.RDS"))
hist<-averageFishCDF_EcoOcean(file, time1_h, time2_h, type = "hist")

# 126
file<-readRDS(paste0(directory,"EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp126_nosoc_default_tcb_global_monthly_2006_2100.RDS"))
fut126<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

# 585
file<-readRDS(paste0(directory,"EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp585_nosoc_default_tcb_global_monthly_2006_2100.RDS"))
fut585<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$EcoOcean<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add DBEM IPSL ----

time1_h = 1990 
time2_h = 1999
time1_f = 2090 
time2_f = 2099

# # for IPCC
# time1_h = 1995
# time2_h = 2014
# time1_f = 2081
# time2_f = 2099

averageFishCDF_DBEM<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE){
  
  # Open the netcdf file
  nc <- file
  
  # Extract important information
  data_attributes <- "tcb"
  main_title <- "guess"
  data_units <- "guess"
    
  lon <- unique(coord$lon)
  lat <- unique(coord$lat)

  time_months <- seq(1951, 2100)
  yearmonth = as.yearmon("1951-01")

  time_months = as.yearmon(yearmonth + seq(0, (length(time_months) - 1)))     
  time_vector<-time_months

  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  # dimension and data format are different from other models, so need different way of extracting data. GRID CELL X YEAR
  temp_array1 <-nc[,tpte$start_point_to_extract:tpte$end_point_to_extract]
  
  # Extract averages
  new_var_vec<-rowMeans(temp_array1)
  new_var_df<-cbind(coord, new_var_vec)
  new_var_df<-new_var_df[,-1]
  new_var_mat<-acast(new_var_df, lon~lat, value.var="new_var_vec")
  
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

  # this should be done when we know the data units 
  new_var_mat = new_var_mat * 1000
  data_units = "kg km-2" 
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

coord<-read.delim(paste0(directory,"DBEM_RData/Lat_Lon.txt"),header = FALSE, sep = ",")
colnames(coord)<-c("grid", "lon", "lat")

# hist & 126
file<-load(paste0(directory,"DBEM_RData/C6IPSL26F0_t2_Abd.RData"))
file<-sppfnlmap
hist<-averageFishCDF_DBEM(file, time1_h, time2_h)
fut126<-averageFishCDF_DBEM(file, time1_f, time2_f)

# 585
file<-load(paste0(directory,"DBEM_RData/C6IPSL85F0_t2_Abd.RData"))
file<-sppfnlmap
fut585<-averageFishCDF_DBEM(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$DBEM<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# extract data GFDL ---- 

mod_gfdl <- c("BOATS","DBPM" ,"MACROECOLOGICAL","ZooMSS", "FEISTY") 

h_years <-c(h_yearsB,h_yearsDB, h_yearsM, h_yearsZ,h_yearsF) 
f_years <-c(f_yearsB,f_yearsDB, f_yearsM, f_yearsZ, f_yearsF) 
earth<-c("_gfdl-esm4_nobc_","_gfdl-esm4_nobasd_","_gfdl-esm4_nobc_","_gfdl-esm4_nobasd_","_gfdl-esm4_nobasd_")
output <-c(outputB,outputDB, outputM, outputZ, outputF) 
extension <-c(extensionB, extensionDB,extensionM, extensionZ, extensionF) 

yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))
yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

# # for IPCC
# yearmonth1<- ifelse(output=="annual", as.yearmon("1995-01"), as.yearmon("1995-01"))
# yearmonth2<- ifelse(output!="annual", as.yearmon("2014-12"), as.yearmon("2014-01"))
# yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2081-01"), as.yearmon("2081-01"))
# yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_gfdl_CMIP6<-list()

for (i in 1:length(mod_gfdl)){

  filename<-paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[2],"/", tolower(mod_gfdl[i]), earth[i], "historical_nat_default_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], extension[i])
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE, CMIP =  6)

  filename <- paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[3], "/", tolower(mod_gfdl[i]), earth[i], "ssp126_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE, CMIP = 6)
  
  filename <- paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[3], "/", tolower(mod_gfdl[i]), earth[i], "ssp585_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE,CMIP = 6)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_gfdl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP6)[[i]]<-mod_gfdl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

# add EcoTroph GFDL ----

time1_h = 1990 
time2_h = 1999
time1_f = 2090 
time2_f = 2099

# # for IPCC
# time1_h = 1995
# time2_h = 2014
# time1_f = 2081
# time2_f = 2099

# hist & 126
file<-paste0(directory,"EcoTroph/_tmp/gfdl-esm4/future/ecotroph_gfdl-esm4_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc")
hist<-averageFishCDF_EcoTroph(file, time1_h, time2_h)
fut126<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

# 585
file<-paste0(directory,"EcoTroph/_tmp/gfdl-esm4/future/ecotroph_gfdl-esm4_nobc_ssp585_nat_default_tcb_annual_1950_2100.nc")
fut585<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
data_gfdl_CMIP6$EcoTroph<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add EcoOcean GFDL ----

time1_h = as.yearmon("1990-01") 
time2_h = as.yearmon("1999-12")
time1_f = as.yearmon("2090-01")
time2_f = as.yearmon("2099-12")

# # for IPCC
# time1_h = as.yearmon("1995-01")
# time2_h = as.yearmon("2005-12") # problem here - see above
# time1_f = as.yearmon("2081-01")
# time2_f = as.yearmon("2099-12")

# hist
file<-readRDS(paste0(directory,"EcoOcean CMIP6 RDS files/ecoocean_gfdl_nobc_historical_nosoc_default_tcb_global_monthly_1950-2005.RDS"))
hist<-averageFishCDF_EcoOcean(file, time1_h, time2_h, type = "hist")

# 126
file<-readRDS(paste0(directory,"EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp126_nosoc_default_tcb_global_monthly_2006_2100.RDS"))
fut126<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

# 585
file<-readRDS(paste0(directory,"EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp585_nosoc_default_tcb_global_monthly_2006_2100.RDS"))
fut585<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP6$EcoOcean<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add DBEM GFDL ----

time1_h = 1990 
time2_h = 1999
time1_f = 2090 
time2_f = 2099

# # for IPCC
# time1_h = 1995
# time2_h = 2014
# time1_f = 2081
# time2_f = 2099

# hist & 126
file<-load(paste0(directory,"DBEM_RData/C6GFDL26F0_t2_Abd.RData"))
file<-sppfnlmap
hist<-averageFishCDF_DBEM(file, time1_h, time2_h)
fut126<-averageFishCDF_DBEM(file, time1_f, time2_f)

# 585
file<-load(paste0(directory,"DBEM_RData/C6GFDL85F0_t2_Abd.RData"))
file<-sppfnlmap
fut585<-averageFishCDF_DBEM(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP6$DBEM<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

```

## Plot global CMIP6 model outputs 

```{r plot CMIP6}

## function to flip matrices  

fliplr_matrix<- function(data_to_flip){
  temp= data_to_flip
  for (ii in 1:dim(data_to_flip)[2])
    data_to_flip[,ii] = temp[,dim(data_to_flip)[2] - ii + 1]
  
  data_to_flip
}

# plot IPSL ----

data_ipsl_CMIP6$MACROECOLOGICAL$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$hist$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$fut126$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$fut585$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$diff_2p6)
data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5)

data_ipsl_CMIP6$ZooMSS$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$hist$fishvar)
data_ipsl_CMIP6$ZooMSS$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$fut126$fishvar)
data_ipsl_CMIP6$ZooMSS$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$fut585$fishvar)
data_ipsl_CMIP6$ZooMSS$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$diff_2p6)
data_ipsl_CMIP6$ZooMSS$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$diff_8p5)

data_ipsl_CMIP6$FEISTY$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$hist$fishvar)
data_ipsl_CMIP6$FEISTY$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$fut126$fishvar)
data_ipsl_CMIP6$FEISTY$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$fut585$fishvar)
data_ipsl_CMIP6$FEISTY$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$diff_2p6)
data_ipsl_CMIP6$FEISTY$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$diff_8p5)

data_ipsl_CMIP6$EcoTroph$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$hist$fishvar)
data_ipsl_CMIP6$EcoTroph$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$fut126$fishvar)
data_ipsl_CMIP6$EcoTroph$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$fut585$fishvar)
data_ipsl_CMIP6$EcoTroph$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$diff_2p6)
data_ipsl_CMIP6$EcoTroph$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$diff_8p5)

data_ipsl_CMIP6$EcoOcean$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$hist$fishvar)
data_ipsl_CMIP6$EcoOcean$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$fut126$fishvar)
data_ipsl_CMIP6$EcoOcean$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$fut585$fishvar)
data_ipsl_CMIP6$EcoOcean$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$diff_2p6)
data_ipsl_CMIP6$EcoOcean$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$diff_8p5)

data_ipsl_CMIP6$DBEM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$hist$fishvar)
data_ipsl_CMIP6$DBEM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$fut126$fishvar)
data_ipsl_CMIP6$DBEM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$fut585$fishvar)
data_ipsl_CMIP6$DBEM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$DBEM$diff_2p6)
data_ipsl_CMIP6$DBEM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$DBEM$diff_8p5)

# function to change hemisphere 
move_hemispheres<- function(data_to_flip){
  temp= data_to_flip
  data_to_flip[1:180,] = temp[181:360,]
  data_to_flip[181:360,] = temp[1:180,]
  data_to_flip
}
  
data_ipsl_CMIP6$EcoOcean$hist$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$hist$fishvar)
data_ipsl_CMIP6$EcoOcean$fut126$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$fut126$fishvar)
data_ipsl_CMIP6$EcoOcean$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$fut585$fishvar)
data_ipsl_CMIP6$EcoOcean$diff_2p6<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$diff_2p6)
data_ipsl_CMIP6$EcoOcean$diff_8p5<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$diff_8p5)

map_ipsl585_CMIP6<-list()

model_type_ipsl<-ifelse(names(data_ipsl_CMIP6) == "DBEM","DBEM", NA) # DBEM resolution is 0.5 deg

for (i in 1:length(data_ipsl_CMIP6)){ 

  tit <- paste(names(data_ipsl_CMIP6)[i], "IPSL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_ipsl585_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl585_CMIP6)[[i]]<-names(data_ipsl_CMIP6)[[i]]
  
  rm(tit)
  
}

# plot GFDL ----

data_gfdl_CMIP6$MACROECOLOGICAL$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$hist$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$fut126$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$fut585$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$diff_2p6)
data_gfdl_CMIP6$MACROECOLOGICAL$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$diff_8p5)

data_gfdl_CMIP6$ZooMSS$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$hist$fishvar)
data_gfdl_CMIP6$ZooMSS$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$fut126$fishvar)
data_gfdl_CMIP6$ZooMSS$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$fut585$fishvar)
data_gfdl_CMIP6$ZooMSS$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$diff_2p6)
data_gfdl_CMIP6$ZooMSS$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$diff_8p5)

data_gfdl_CMIP6$EcoTroph$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$hist$fishvar)
data_gfdl_CMIP6$EcoTroph$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$fut126$fishvar)
data_gfdl_CMIP6$EcoTroph$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$fut585$fishvar)
data_gfdl_CMIP6$EcoTroph$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$diff_2p6)
data_gfdl_CMIP6$EcoTroph$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$diff_8p5)

data_gfdl_CMIP6$EcoOcean$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$hist$fishvar)
data_gfdl_CMIP6$EcoOcean$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$fut126$fishvar)
data_gfdl_CMIP6$EcoOcean$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$fut585$fishvar)
data_gfdl_CMIP6$EcoOcean$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$diff_2p6)
data_gfdl_CMIP6$EcoOcean$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$diff_8p5)

data_gfdl_CMIP6$DBEM$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$hist$fishvar)
data_gfdl_CMIP6$DBEM$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$fut126$fishvar)
data_gfdl_CMIP6$DBEM$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$fut585$fishvar)
data_gfdl_CMIP6$DBEM$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$DBEM$diff_2p6)
data_gfdl_CMIP6$DBEM$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$DBEM$diff_8p5)

# move hemisphere  
data_gfdl_CMIP6$EcoOcean$hist$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$hist$fishvar)
data_gfdl_CMIP6$EcoOcean$fut126$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$fut126$fishvar)
data_gfdl_CMIP6$EcoOcean$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$fut585$fishvar)
data_gfdl_CMIP6$EcoOcean$diff_2p6<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$diff_2p6)
data_gfdl_CMIP6$EcoOcean$diff_8p5<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$diff_8p5)

map_gfdl585_CMIP6<-list()

model_type_gfdl<-ifelse(names(data_gfdl_CMIP6) == "DBEM","DBEM", NA) 

for (i in 1:length(data_gfdl_CMIP6)){ 
  
  tit <- paste(names(data_gfdl_CMIP6)[i], "GFDL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_gfdl585_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl585_CMIP6)[[i]]<-names(data_gfdl_CMIP6)[[i]]
  
  rm(tit)
  
}

## RCP 2.6

# IPSL

map_ipsl126_CMIP6<-list()

for (i in 1:length(data_ipsl_CMIP6)){ 

  tit <- paste(names(data_ipsl_CMIP6)[i], "IPSL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_ipsl126_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl126_CMIP6)[[i]]<-names(data_ipsl_CMIP6)[[i]]
  
  rm(tit)
  
}

# GFDL

map_gfdl126_CMIP6<-list()

for (i in 1:length(data_gfdl_CMIP6)){ 

  tit <- paste(names(data_gfdl_CMIP6)[i], "GFDL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_gfdl126_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl126_CMIP6)[[i]]<-names(data_gfdl_CMIP6)[[i]]
  
  rm(tit)
  
}

```

## Deal with model set 

```{r}

# if model set == "full", we are considering all models and creating figures for the Main Document, otherwise we are considering the subset of models considered in Lotze et al. 2019 and producing figures for the Supplemntary Information.

set = "not_full"

if(set == "full"){
  data_gfdl_CMIP6$DBPM<-NULL # exclude DBPM GFDL CMIP6 anyways as this are not final runs 
}else{
  data_gfdl_CMIP6$DBPM<-NULL
  data_ipsl_CMIP6$ZooMSS<-NULL
  data_gfdl_CMIP6$ZooMSS<-NULL
  data_ipsl_CMIP6$FEISTY<-NULL
  data_gfdl_CMIP6$FEISTY<-NULL
  data_ipsl_CMIP6$EcoTroph<-NULL
  data_gfdl_CMIP6$EcoTroph<-NULL
}

```

## Model average for CMIP6 

```{r}

# RCP 8.5

# MAKE SURE THAT ALL MATRICES ARE ON ONE DEGREE SCALE
### DBEM - TAKE THE VALUE FROM CLOSE POINT
lons_to_use = seq(1,719,2)
lats_to_use = seq(1,359,2)

data_ipsl_CMIP6$DBEM$diff_8p5 = data_ipsl_CMIP6$DBEM$diff_8p5[lons_to_use, lats_to_use] 
data_gfdl_CMIP6$DBEM$diff_8p5 = data_gfdl_CMIP6$DBEM$diff_8p5[lons_to_use, lats_to_use] 

res_ipsl<-model_stat(data_ipsl_CMIP6, esm = 'diff_8p5')
model_average_ipsl_CMIP6<-res_ipsl$model_average
model_sd_ipsl_CMIP6<-res_ipsl$model_sd
model_agreement_ipsl_CMIP6<- res_ipsl$model_agreement

res_gfdl<-model_stat(data_gfdl_CMIP6, esm = 'diff_8p5')
model_average_gfdl_CMIP6<-res_gfdl$model_average
model_sd_gfdl_CMIP6<-res_gfdl$model_sd
model_agreement_gfdl_CMIP6<- res_gfdl$model_agreement

res_all<-model_stat(c(data_ipsl_CMIP6, data_gfdl_CMIP6), esm = 'diff_8p5')
model_average_all_CMIP6<-res_all$model_average
model_sd_all_CMIP6<-res_all$model_sd
model_agreement_all_CMIP6<- res_all$model_agreement

# define titles
maptitle_average = paste("Mean % change RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
maptitle_agreement = paste("Agreement RCP 8.5, 1990s to 2090s CMIP6", sep=" ")

# Plot the model average and standard deviation
avarage_CMIP6_all<-plot_FISH_MIP(model_average_all_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP6_all<-plot_FISH_MIP(model_sd_all_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP6_all<-plot_FISH_MIP(model_agreement_all_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") 

# plot average by ESM 
avarage_CMIP6_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP6, "Mean % change RCP 8.5, 1990s to 2090s CMIP6 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP6_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP6, "Mean % change RCP 8.5, 1990s to 2090s CMIP6 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

# RCP 2.6 

data_ipsl_CMIP6$DBEM$diff_2p6 = data_ipsl_CMIP6$DBEM$diff_2p6[lons_to_use, lats_to_use] 
data_gfdl_CMIP6$DBEM$diff_2p6 = data_gfdl_CMIP6$DBEM$diff_2p6[lons_to_use, lats_to_use] 

# model average
res_ipsl_126<-model_stat(data_ipsl_CMIP6, esm = 'diff_2p6')
model_average_ipsl_CMIP6_126<-res_ipsl_126$model_average
model_sd_ipsl_CMIP6_126<-res_ipsl_126$model_sd
model_agreement_ipsl_CMIP6_126<- res_ipsl_126$model_agreement

res_gfdl_126<-model_stat(data_gfdl_CMIP6, esm = 'diff_2p6')
model_average_gfdl_CMIP6_126<-res_gfdl_126$model_average
model_sd_gfdl_CMIP6_126<-res_gfdl_126$model_sd
model_agreement_gfdl_CMIP6_126<- res_gfdl_126$model_agreement

res_all_126<-model_stat(c(data_ipsl_CMIP6, data_gfdl_CMIP6), esm = 'diff_2p6')
model_average_all_CMIP6_126<-res_all_126$model_average
model_sd_all_CMIP6_126<-res_all_126$model_sd
model_agreement_all_CMIP6_126<- res_all_126$model_agreement 

# define titles
maptitle_average = paste("Mean % change RCP 2.6, 1990s to 2090s CMIP6", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 2.6, 1990s to 2090s CMIP6", sep=" ")
maptitle_agreement = paste("Agreement RCP 2.6, 1990s to 2090s CMIP6", sep=" ")

# Plot the model average and standard deviation
avarage_CMIP6_all_126<-plot_FISH_MIP(model_average_all_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP6_all_126<-plot_FISH_MIP(model_sd_all_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP6_all_126<-plot_FISH_MIP(model_agreement_all_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot average by ESM 
avarage_CMIP6_ipsl_126<-plot_FISH_MIP(model_average_ipsl_CMIP6, "Mean % change RCP 2.6, 1990s to 2090s CMIP6 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP6_gfdl_126<-plot_FISH_MIP(model_average_gfdl_CMIP6, "Mean % change RCP 2.6, 1990s to 2090s CMIP6 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

```

## Save temporary outputs CMIP6 

```{r}

data_summaries_CMIP6<-list(res_all= res_all, res_ipsl = res_ipsl, res_gfdl = res_gfdl, res_all_126= res_all_126, res_ipsl_126 = res_ipsl_126, res_gfdl_126 = res_gfdl_126)

map_summaries_CMIP6<-list(avarage_CMIP6_all = avarage_CMIP6_all, sd_CMIP6_all = sd_CMIP6_all, agreement_CMIP6_all = agreement_CMIP6_all, avarage_CMIP6_ipsl = avarage_CMIP6_ipsl, avarage_CMIP6_gfdl = avarage_CMIP6_gfdl, avarage_CMIP6_all_126 = avarage_CMIP6_all_126, sd_CMIP6_all_126 = sd_CMIP6_all_126, agreement_CMIP6_all_126 = agreement_CMIP6_all_126, avarage_CMIP6_ipsl_126 = avarage_CMIP6_ipsl_126, avarage_CMIP6_gfdl_126 = avarage_CMIP6_gfdl_126)

if(set == "full"){
  # save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, map_ipsl126_CMIP6, map_gfdl126_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6.RData")
  save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, map_ipsl126_CMIP6, map_gfdl126_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "../CMIP5vsCMIP6_data/temp_data/data_CMIP6.RData")
}else{
  # save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_reducedModelSet.RData")
  save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "../CMIP5vsCMIP6_data/temp_data/data_CMIP6_reducedModelSet.RData")
}

# # for IPCC - Laurent Bopp
# data_summaries_CMIP6<-list(res_all_ssp5 = res_all, res_ipsl_ssp5 = res_ipsl, res_gfdl_ssp5 = res_gfdl, res_all_ssp1= res_all_126, res_ipsl_ssp1 = res_ipsl_126, res_gfdl_ssp1 = res_gfdl_126)
# 
# lat<-data_gfdl_CMIP6$BOATS$hist$lat
# lon<-data_gfdl_CMIP6$BOATS$hist$lon
# 
# save(data_summaries_CMIP6, lat, lon, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_map_CMIP6_IPCC.RData")

```

# STEP 3 averadge and plot data

## Load data 

```{r}

rm(list=ls())

set = "full"

if(set == "full"){
  load("../CMIP5vsCMIP6_data/temp_data/data_CMIP5.RData")
  load("../CMIP5vsCMIP6_data/temp_data/data_CMIP6.RData")
}else{
  load("../CMIP5vsCMIP6_data/temp_data/data_CMIP5_reducedModelSet.RData")
  load("../CMIP5vsCMIP6_data/temp_data/data_CMIP6_reducedModelSet.RData")
}

```

## Load libraries for netcdf and define variables

```{r load CMIP5}

install_load <- function (this_package)  {   

   package <- c(this_package)
   if(package %in% rownames(installed.packages()))
        do.call('library', list(package))

    # if package is not installed locally, download, then load
    else {
        install.packages(package)
         do.call("library", list(package))
    }
}

### load/install libraries ###
install_load("grid")
install_load("zoo")
install_load("viridis")
install_load("tidyr")
install_load("dplyr")
install_load("ncdf4")
install_load("ggplot2")
install_load("patchwork")

### load helper scripts with functions to extract data from netcdfs ###
source("R/HelperScripts.r")
source("R/Funcs_maps.r")

### create folders where temporary data can be stored ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep1 = "temp_data"
ifelse(!dir.exists(file.path(mainDir, DirStep1)), dir.create(file.path(mainDir, DirStep1)), FALSE)

### define variables ###
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

### create folders where figures can be saved ###
mainDir = "../CMIP5vsCMIP6_data/"
DirStep2 = "figures"
ifelse(!dir.exists(file.path(mainDir, DirStep2)), dir.create(file.path(mainDir, DirStep2)), FALSE)
save_loc<-"../CMIP5vsCMIP6_data/figures/"

```

## Load libraries for plotting and define criteria 

```{r}

### Define color/legend limits ###
main_plot_colour_values = c(0,10000) 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)
mean_plot_colour_values = c(-50,50)
sd_plot_colour_values = c(0,50)
model_agreement_plot_colour_values = c(50,100)

#### define color schemes ###
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values 

### Download and process world outline ###
install_load("sf")
install_load("rnaturalearth")
install_load("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) 

### other mapping libraries ####
install_load("raster")
install_load("maptools")
install_load("RColorBrewer")
install_load("scales")

```

## Delta plot 

```{r}

# Delta map 

## RCP 8.5

delta_map_data_all<-data_summaries_CMIP6$res_all$model_average - data_summaries_CMIP5$res_all$model_average
maptitle_detla<-"Delta (CMIP6 change - CMIP5 change)"
delta_map_all_difference<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 
# if (+1) - (+5) = -4 # CMIP6 decreased 4 times
# if (+1) - (-5) = 6 # CMIP6 increased 6 times 
# if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
# if (-1) - (-5) = 4 # CMIP6 increased 4 times 

delta_map_data_ipsl<-data_summaries_CMIP6$res_ipsl$model_average - data_summaries_CMIP5$res_ipsl$model_average
maptitle_detla<-"Delta IPSL (CMIP6 change - CMIP5 change)"
delta_map_ipsl_difference<-plot_FISH_MIP(delta_map_data_ipsl, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_gfdl<-data_summaries_CMIP6$res_gfdl$model_average - data_summaries_CMIP5$res_gfdl$model_average
maptitle_detla<-"Delta GFDL (CMIP6 change - CMIP5 change)"
delta_map_gfdl_difference<-plot_FISH_MIP(delta_map_data_gfdl, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

## RCP 2.6

delta_map_data_all_126<-data_summaries_CMIP6$res_all_126$model_average - data_summaries_CMIP5$res_all_126$model_average
maptitle_detla_126<-"Delta (CMIP6 change - CMIP5 change) RCP 2.6"
delta_map_all_difference_126<-plot_FISH_MIP(delta_map_data_all_126, maptitle_detla_126, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_ipsl_126<-data_summaries_CMIP6$res_ipsl_126$model_average - data_summaries_CMIP5$res_ipsl_126$model_average
maptitle_detla<-"Delta IPSL (CMIP6 change - CMIP5 change) RCP 2.6"
delta_map_ipsl_difference_126<-plot_FISH_MIP(delta_map_data_ipsl_126, maptitle_detla_126, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_gfdl_126<-data_summaries_CMIP6$res_gfdl_126$model_average - data_summaries_CMIP5$res_gfdl_126$model_average
maptitle_detla<-"Delta GFDL (CMIP6 change - CMIP5 change) RCP 2.6"
delta_map_gfdl_difference_126<-plot_FISH_MIP(delta_map_data_gfdl_126, maptitle_detla_126, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

```

## Flip sign grid-cells

```{r}

# function to identify cells that have switched sign (from increase to decrease in biomass and vice versa) from CMIP5 to CMIP6

flip_sign<-function(temp, temp1){

  # find celles where the sign is the same between CMIP5 and CMIP6
  temp2B<-temp*temp1
  temp2B<-ifelse(temp2B<0, NA, 1) 
  
  # consider only these cells
  tempB<-temp*temp2B
  temp1B<-temp1*temp2B
  # calculate delta as above 
  data_neutral<-temp1B - tempB 

  # find cells where the sign changed
  temp2<-temp*temp1 
  temp2<-ifelse(temp2<0, 1, NA) # if negative, sign change 
  
  # consider only these cells
  temp<-temp*temp2
  temp1<-temp1*temp2

  # from + (CMIP5) to - (CMIP6)
  temp_neg<-temp
  temp1_neg<-temp1
  temp_neg<-ifelse(temp_neg<0, NA, temp_neg) 
  temp1_neg<-ifelse(temp1_neg>0, NA, temp1_neg)

  # by how much? # calculate delta as above 
  data_negative<-temp1_neg - temp_neg # CMIP6 - CMIP5
  
  # from - (CMIP5) to + (CMIP6)
  temp_pos<-temp
  temp1_pos<-temp1
  temp_pos<-ifelse(temp_pos>0, NA, temp_pos)
  temp1_pos<-ifelse(temp1_pos<0, NA, temp1_pos)

  # by how much? # calculate delta as above 
  data_positive<-temp1_pos - temp_pos # CMIP6 -CMIP5

  return(list(data_negative = data_negative, data_positive = data_positive, data_neutral = data_neutral))
}

flip_sign_data<-flip_sign(data_summaries_CMIP5$res_all$model_average, data_summaries_CMIP6$res_all$model_average)

# % of cell that changed
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data$data_negative))
c<-sum(!is.na(flip_sign_data$data_positive))
d<-sum(!is.na(flip_sign_data$data_neutral))
(b/a)*100 # turned negative 
(c/a)*100 # turned positive
(d/a)*100 # did not change sign  

(b/a)*100 + (c/a)*100 + (d/a)*100 
# not perfect match to 100%  

# full set
# > (b/a)*100 # turned negative 
# [1] 13.54085
# > (c/a)*100 # turned positive
# [1] 14.93126
# > (d/a)*100 # did not change sign  
# [1] 71.09784

# plot
colour_scheme4 <- c(low = "#fc9617", mid = "#fecf95",  high = "#fef4e7")
maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in CMIP6"
map_sign_negative<-plot_FISH_MIP(flip_sign_data$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

colour_scheme5 <- c(low = "#f4f3f9", mid = "#bab4d7",  high = "#8479b7") 
maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in CMIP6"
map_sign_positive<-plot_FISH_MIP(flip_sign_data$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

maptitle_sign_neutral<-"Delta for cells that did not change direction between CMIPs"
map_sign_neutral<-plot_FISH_MIP(flip_sign_data$data_neutral, maptitle_sign_neutral, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5)

# by ESM

## IPSL

flip_sign_data_ipsl<-flip_sign(data_summaries_CMIP5$res_ipsl$model_average, data_summaries_CMIP6$res_ipsl$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data_ipsl$data_negative))
c<-sum(!is.na(flip_sign_data_ipsl$data_positive))
d<-sum(!is.na(flip_sign_data_ipsl$data_neutral))
(b/a)*100 # turned negative 
(c/a)*100 # turned positive
(d/a)*100 # did not change sign 

maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in IPSL CMIP6"
map_sign_negative_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in IPSL CMIP6"
map_sign_positive_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

maptitle_sign_neutral<-"Delta for cells that did not change direction between CMIPs in IPSL"
map_sign_neutral_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_neutral, maptitle_sign_neutral, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5)

## GFDL
flip_sign_data_gfdl<-flip_sign(data_summaries_CMIP5$res_gfdl$model_average, data_summaries_CMIP6$res_gfdl$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data_gfdl$data_negative))
c<-sum(!is.na(flip_sign_data_gfdl$data_positive))
d<-sum(!is.na(flip_sign_data_gfdl$data_neutral))
(b/a)*100 # turned negative 
(c/a)*100 # turned positive
(d/a)*100 # did not change sign 

maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in GFDL CMIP6"
map_sign_negative_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in GFDL CMIP6"
map_sign_positive_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

maptitle_sign_neutral<-"Delta for cells that did not change direction between CMIPs in GFDL"
map_sign_neutral_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_neutral, maptitle_sign_neutral, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5)

## RCP 2.6

flip_sign_data_126<-flip_sign(data_summaries_CMIP5$res_all_126$model_average, data_summaries_CMIP6$res_all_126$model_average)

# plot
colour_scheme4 <- c(low = "#fc9617", mid = "#fecf95",  high = "#fef4e7")
map_sign_negative_126<-plot_FISH_MIP(flip_sign_data_126$data_negative, NA, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

colour_scheme5 <- c(low = "#f4f3f9", mid = "#bab4d7",  high = "#8479b7") 
map_sign_positive_126<-plot_FISH_MIP(flip_sign_data_126$data_positive, NA, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

map_sign_neutral_126<-plot_FISH_MIP(flip_sign_data_126$data_neutral, NA, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5)

# by ESM 

## IPSL 
flip_sign_data_ipsl_126<-flip_sign(data_summaries_CMIP5$res_ipsl_126$model_average, data_summaries_CMIP6$res_ipsl_126$model_average)

map_sign_negative_ipsl_126<-plot_FISH_MIP(flip_sign_data_ipsl_126$data_negative, NA, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

map_sign_positive_ipsl_126<-plot_FISH_MIP(flip_sign_data_ipsl_126$data_positive, NA, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

map_sign_neutral_ipsl_126<-plot_FISH_MIP(flip_sign_data_ipsl_126$data_neutral, NA, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5)

## GFDL
flip_sign_data_gfdl_126<-flip_sign(data_summaries_CMIP5$res_gfdl_126$model_average, data_summaries_CMIP6$res_gfdl_126$model_average)

map_sign_negative_gfdl_126<-plot_FISH_MIP(flip_sign_data_gfdl_126$data_negative, NA, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

map_sign_positive_gfdl_126<-plot_FISH_MIP(flip_sign_data_gfdl_126$data_positive, NA, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

map_sign_neutral_gfdl_126<-plot_FISH_MIP(flip_sign_data_gfdl_126$data_neutral, NA, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5)

```

## FIG 5 and SI figures - maps of change in ocean biomass

```{r multipanel plot}

### FIG 5 & S9 ####

layout <- "
AB
CD
EF
"

a <- map_summaries_CMIP5$avarage_CMIP5_all + ggtitle("a) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b <- map_summaries_CMIP6$avarage_CMIP6_all + ggtitle("b) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c <- delta_map_all_difference + ggtitle("c) Change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<- map_sign_neutral + ggtitle("d) Same direction of change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- map_sign_positive + ggtitle("e) Shift to positive change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- map_sign_negative + ggtitle("f) Shift to negative change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a + b + c + d + e + f + plot_layout(design = layout)

if(set == "full"){name = "Fig5.pdf"}else{name = "FigS9.pdf"}

pdf(paste0(save_loc,name), height=10, width=15) 
pt
dev.off()

### FIG S12 & S18 - 2.6 scenario ####

a126 <- map_summaries_CMIP5$avarage_CMIP5_all_126 + ggtitle("a) CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b126 <- map_summaries_CMIP6$avarage_CMIP6_all_126 + ggtitle("b) CMIP6 SSP1-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c126 <- delta_map_all_difference_126 + ggtitle("c) Change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d126 <- map_sign_neutral_126 + ggtitle("d) Same direction of change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e126 <- map_sign_positive_126 + ggtitle("e) Shift to positive change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f126 <- map_sign_negative_126 + ggtitle("f) Shift to negative change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a126 + b126 + c126 + d126 + e126 + f126+ plot_layout(design = layout)

if(set == "full"){name = "FigS12.pdf"}else{name = "FigS18.pdf"}

pdf(paste0(save_loc,name), height=10, width=15) 
pt
dev.off()

### FIG S5 ####

layout <- "
AB
CD
EF
GH
IJ
KL
"

a2 <- map_summaries_CMIP5$avarage_CMIP5_ipsl + ggtitle("a) CMIP5 IPSL-CM5A-LR RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b2 <- map_summaries_CMIP6$avarage_CMIP6_ipsl + ggtitle("b) CMIP6 IPSL-CM6A-LR SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c <- map_summaries_CMIP5$avarage_CMIP5_gfdl + ggtitle("c) CMIP5 GFDL-ESM2M RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d <- map_summaries_CMIP6$avarage_CMIP6_gfdl + ggtitle("d) CMIP6 GFDL-ESM4 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- delta_map_ipsl_difference + ggtitle("e) Change between CMIPs IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- delta_map_gfdl_difference + ggtitle("f) Change between CMIPs GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_sign_neutral_ipsl + ggtitle("g) Same direction of change between CMIPs IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_sign_neutral_gfdl + ggtitle("h) Same direction of change between CMIPs GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_sign_positive_ipsl + ggtitle("i) Shift to positive change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_sign_positive_gfdl + ggtitle("j) Shift to positive change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k <- map_sign_negative_ipsl + ggtitle("k) Shift to negative change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_sign_negative_gfdl + ggtitle("l) Shift to negative change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a2 + b2 + 
  c + d +
  e + f +
  g + h + 
  i + j + 
  k + l +
  plot_layout(design = layout)

if(set == "full"){name = "FigS5.pdf"}else{name = "FigS?.pdf"}

pdf(paste0(save_loc,name), height=20, width=15) 
pt
dev.off()

### FIG S13 & S19 - 2.6 scenario ####

a2126 <- map_summaries_CMIP5$avarage_CMIP5_ipsl_126 + ggtitle("a) CMIP5 IPSL-CM5A-LR RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b2126 <- map_summaries_CMIP6$avarage_CMIP6_ipsl_126 + ggtitle("b) CMIP6 IPSL-CM6A-LR SSP1-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c126 <- map_summaries_CMIP5$avarage_CMIP5_gfdl_126 + ggtitle("c) CMIP5 GFDL-ESM2M RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d126 <- map_summaries_CMIP6$avarage_CMIP6_gfdl_126 + ggtitle("d) CMIP6 GFDL-ESM4 SSP1-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e126 <- delta_map_ipsl_difference_126 + ggtitle("e) Change between CMIPs IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f126 <- delta_map_gfdl_difference_126 + ggtitle("f) Change between CMIPs GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g126 <- map_sign_neutral_ipsl_126 + ggtitle("g) Same direction of change between CMIPs IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h126 <- map_sign_neutral_gfdl_126 + ggtitle("h) Same direction of change between CMIPs GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i126 <- map_sign_positive_ipsl_126 + ggtitle("i) Shift to positive change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j126 <- map_sign_positive_gfdl_126 + ggtitle("j) Shift to positive change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k126 <- map_sign_negative_ipsl_126 + ggtitle("k) Shift to negative change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l126 <- map_sign_negative_gfdl_126 + ggtitle("l) Shift to negative change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a2126 + b2126 + 
  c126 + d126 +
  e126 + f126 +
  g126 + h126 + 
  i126 + j126 +
  k126 + l126 +
  plot_layout(design = layout)

if(set == "full"){name = "FigS13.pdf"}else{name = "FigS19.pdf"}

pdf(paste0(save_loc, name), height=20, width=15) 
pt
dev.off()

### FIG S6 & S10 ####

layout <- "
AB
CD
EF
"

c<-map_summaries_CMIP5$sd_CMIP5_all +  ggtitle("c) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_summaries_CMIP6$sd_CMIP6_all +  ggtitle("d) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e<-map_summaries_CMIP5$agreement_CMIP5_all + ggtitle("e) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_summaries_CMIP6$agreement_CMIP6_all + ggtitle("f) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a + b + 
    c + d +  
    e + f +  
    plot_layout(design = layout)

if(set == "full"){name = "FigS6.pdf"}else{name = "FigS10.pdf"}

pdf(paste0(save_loc,name), height=10, width=15) 
pt
dev.off()


### FIG S16 & S20 - 2.6 scenario ####

c126<-map_summaries_CMIP5$sd_CMIP5_all_126 +  ggtitle("c) CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d126<-map_summaries_CMIP6$sd_CMIP6_all_126 +  ggtitle("d) CMIP6 SSP1-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e126<-map_summaries_CMIP5$agreement_CMIP5_all_126 + ggtitle("e) CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f126<-map_summaries_CMIP6$agreement_CMIP6_all_126 + ggtitle("f) CMIP6 SSP1-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a126 + b126 + 
    c126 + d126 +  
    e126 + f126 +  
    plot_layout(design = layout)

if(set == "full"){name = "FigS16.pdf"}else{name = "FigS20.pdf"}

pdf(paste0(save_loc,name), height=10, width=15) 
pt
dev.off()

```

## FIG S4, S15, S3 & S14 - all models outputs

```{r}

# RUN ONLY IF set == "full

### FIG S4 ####  
  
layout <- "
AB 
CD
EF
GH
IJ
#K
LM
#N
OP
"

a<-map_ipsl585_CMIP5$APECOSM +  ggtitle("a) APECOSM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_ipsl585_CMIP6$APECOSM +  ggtitle("b) APECOSM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_ipsl585_CMIP5$BOATS +  ggtitle("c) BOATS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_ipsl585_CMIP6$BOATS +  ggtitle("d) BOATS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e<-map_ipsl585_CMIP5$DBEM + ggtitle("e) DBEM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_ipsl585_CMIP6$DBEM + ggtitle("f) DBEM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_ipsl585_CMIP5$DBPM + ggtitle("g) DBPM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_ipsl585_CMIP6$DBPM + ggtitle("h) DBPM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_ipsl585_CMIP5$EcoOcean + ggtitle("i) EcoOcean CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_ipsl585_CMIP6$EcoOcean + ggtitle("j) EcoOcean CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k <- map_ipsl585_CMIP6$EcoTroph + ggtitle("k) EcoTroph CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_ipsl585_CMIP5$MACROECOLOGICAL + ggtitle("l) MACROECOLOGICAL CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
m <- map_ipsl585_CMIP6$MACROECOLOGICAL + ggtitle("m) MACROECOLOGICAL CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
n <- map_ipsl585_CMIP6$FEISTY  + ggtitle("n) FEISTY CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
o<- map_ipsl585_CMIP5$ZooMSS +ggtitle("o) ZooMSS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
p <- map_ipsl585_CMIP6$ZooMSS  +ggtitle("p) ZooMSS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a + b + 
  c + d + 
  e + f + 
  g + h + 
  i + j + 
  k + 
  l + m + 
  n + 
  o + p + 
  plot_layout(design = layout)
    
jpeg(paste0(save_loc,"FigS4.jpeg"), height=40, width=30, units ='in', res=300)
pt 
dev.off()

### FIG S15 - 2.6 scenario ####

a<-map_ipsl126_CMIP5$APECOSM +  ggtitle("a) APECOSM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_ipsl126_CMIP6$APECOSM +  ggtitle("b) APECOSM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_ipsl126_CMIP5$BOATS +  ggtitle("c) BOATS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_ipsl126_CMIP6$BOATS +  ggtitle("d) BOATS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e<-map_ipsl126_CMIP5$DBEM + ggtitle("e) DBEM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_ipsl126_CMIP6$DBEM + ggtitle("f) DBEM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_ipsl126_CMIP5$DBPM + ggtitle("g) DBPM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_ipsl126_CMIP6$DBPM + ggtitle("h) DBPM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_ipsl126_CMIP5$EcoOcean + ggtitle("i) EcoOcean CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_ipsl126_CMIP6$EcoOcean + ggtitle("j) EcoOcean CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k <- map_ipsl126_CMIP6$EcoTroph + ggtitle("k) EcoTroph CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_ipsl126_CMIP5$MACROECOLOGICAL + ggtitle("l) MACROECOLOGICAL CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
m <- map_ipsl126_CMIP6$MACROECOLOGICAL + ggtitle("m) MACROECOLOGICAL CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
n <- map_ipsl126_CMIP6$FEISTY  + ggtitle("n) FEISTY CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
o<- map_ipsl126_CMIP5$ZooMSS +ggtitle("o) ZooMSS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
p <- map_ipsl126_CMIP6$ZooMSS  +ggtitle("p) ZooMSS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a + b + 
  c + d + 
  e + f + 
  g + h + 
  i + j + 
  k + 
  l + m + 
  n + 
  o + p + 
  plot_layout(design = layout)
    
jpeg(paste0(save_loc,"FigS15.jpeg"), height=40, width=30, units ='in', res=300)
pt 
dev.off()

### FIG S3 ####

layout <- "
AB 
CD
EF
#G
HI
#J
KL
"

a<-map_gfdl585_CMIP5$BOATS +  ggtitle("a) BOATS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_gfdl585_CMIP6$BOATS +  ggtitle("b) BOATS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_gfdl585_CMIP5$DBEM + ggtitle("c) DBEM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_gfdl585_CMIP6$DBEM + ggtitle("d) DBEM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- map_gfdl585_CMIP5$EcoOcean + ggtitle("e) EcoOcean CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- map_gfdl585_CMIP6$EcoOcean + ggtitle("f) EcoOcean CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_gfdl585_CMIP6$EcoTroph + ggtitle("g) EcoTroph CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_gfdl585_CMIP5$MACROECOLOGICAL + ggtitle("h) MACROECOLOGICAL CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_gfdl585_CMIP6$MACROECOLOGICAL + ggtitle("i) MACROECOLOGICAL CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_gfdl585_CMIP6$FEISTY  + ggtitle("j) FEISTY CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k<- map_gfdl585_CMIP5$ZooMSS +ggtitle("k) ZooMSS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_gfdl585_CMIP6$ZooMSS  +ggtitle("l) ZooMSS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a+ b + 
  c + d + 
  e + f + 
  g + 
  h + i +
  j+ 
  k+ l + 
  plot_layout(design = layout)

jpeg(paste0(save_loc,"FigS3.jpeg"), height=35, width=30, units ='in', res=300)
pt
dev.off()

### FIG S14 - 2.6 scenario ####

a<-map_gfdl126_CMIP5$BOATS +  ggtitle("a) BOATS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_gfdl126_CMIP6$BOATS +  ggtitle("b) BOATS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_gfdl126_CMIP5$DBEM + ggtitle("c) DBEM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_gfdl126_CMIP6$DBEM + ggtitle("d) DBEM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- map_gfdl126_CMIP5$EcoOcean + ggtitle("e) EcoOcean CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- map_gfdl126_CMIP6$EcoOcean + ggtitle("f) EcoOcean CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_gfdl126_CMIP6$EcoTroph + ggtitle("g) EcoTroph CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_gfdl126_CMIP5$MACROECOLOGICAL + ggtitle("h) MACROECOLOGICAL CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_gfdl126_CMIP6$MACROECOLOGICAL + ggtitle("i) MACROECOLOGICAL CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_gfdl126_CMIP6$FEISTY  + ggtitle("j) FEISTY CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k<- map_gfdl126_CMIP5$ZooMSS +ggtitle("k) ZooMSS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_gfdl126_CMIP6$ZooMSS  +ggtitle("l) ZooMSS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a+ b +
  c + d + 
  e + f + 
  g + 
  h + i +
  j+ 
  k+ l + 
  plot_layout(design = layout)

jpeg(paste0(save_loc,"FigS14.jpeg"), height=35, width=30, units ='in', res=300)
pt
dev.off()

```

