---
title: "Plotting global models' time series inputs"
author: "Camilla Novaglio"
date: "18/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# TO DO 

you added a new argument to get_timeSeries(), output = ..., you need to re-run batch_run_timeSeries.Rmd to check that it is running ok, also for some of the models outside the loop (e.g. zoomss cmip5) output[i] was unspecified before so not sure how the code handled that 

I will call the protocols ‘RCP’ for CMIP5 and ‘SSP’ for CMIP6 in all figs

# Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

```

# extract data and calcaulte % change in time CMIP5 

```{r}

# extract data IPSL ---- 

directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP2b/IPSL_CM5A_LR/"

variable_to_extract <-c("to", "pp") # , "phy", "zoo")

yearmonth1<- as.yearmon("1971-01")
yearmonth2<- as.yearmon("2005-01") # yearly values - extract all 

yearmonth1_fut<- as.yearmon("2006-01")
yearmonth2_fut<- as.yearmon("2100-01")

output = "yearly"
cmip = 5

data_ipsl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # i = 2
  # the variable is temperature,extract and convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], ".nc4.zs.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 # can be done later on if this is going to be merged with the loop below
    hist$data_units<-"C"
    
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp261_20060101_21001231_1Y.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp851_20060101_21001231_1Y.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
    
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")   
    # `colnames<-`(all)<-c("year","C","CChange","color")
  
  }else{ # the variable is other than temperature, extract both small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
      
      filename<-paste0("l",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 
      
      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      if(variable_to_extract[i] == "pp"){ # always the case as to and pp are the only data you are extracting for this fig. 
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }

    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")   
    # `colnames<-`(all)<-c("year","pp","ppChange","color")
      
  }

  data_ipsl_CMIP5[[i]]<-list(all = all)
  names(data_ipsl_CMIP5)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
  
}

names(data_ipsl_CMIP5)

# extract data GFDL ---- 

directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP2b/GFDL_ESM2M/"

variable_to_extract <-c("to", "pp") 
# the variable inside the netcdf is called differently than the variable in the file name.  
variable_to_extract2 <-c("TO_ZS", "PP_ZINT")

output = "yearly"
cmip = 5

data_gfdl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # i = 2
  # the variable is temperature,extract adn convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], "_gfdl-esm2m_historical_zs_annual_195001-200512.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 # can be done later on if this is going to be merged with the loop below
    hist$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp26_zs_annual_200601-210012.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp85_zs_annual_200601-210012.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
    
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")   
  
  }else{ # # the variable is other than temperature, extract both small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
      filename<-paste0("l",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
  
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 

      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      if(variable_to_extract[i] == "pp"){
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }
      
    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")   
    # `colnames<-`(all)<-c("year","pp","ppChange","color")  
    
  }
  
  data_gfdl_CMIP5[[i]]<-list(all = all)
  names(data_gfdl_CMIP5)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
  
}

names(data_gfdl_CMIP5)

```

# save outputs ISIMIP2b temp 

```{r}

save(data_ipsl_CMIP5, data_gfdl_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_trends_inputs_CMIP5.RData")

```

# extract data and calcaulte % change in time CMIP6 

```{r}

# CMIP6 data location
directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP3b/"

# extract data IPSL ---- 

variable_to_extract <-c("to", "pp")# , "phy", "zoo") # just to be consistent with names across cmips and earth models 
variable_to_extract3 <-c("tos", "intpp") #, "phyc-vint", "zooc-vint")

yearmonth1<- as.yearmon("1971-01")
yearmonth2<- as.yearmon("2014-12") # monthly values - do the mean 

yearmonth1_fut<- as.yearmon("2015-01")
yearmonth2_fut<- as.yearmon("2099-12") # should this be 2100-12?? 

output = "monthly"
cmip = 6

data_ipsl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  if (variable_to_extract3[[i]] == "tos"){
     # output[i]<-"yearly" # should this be yearly here as the inputs data is not years.. yes. in batch_run_timeSeries you are using extractFishCDF() which does not average yearly so you need to do it here. 
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")
  }else {
    
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }
    
    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")
  }
  
  
  data_ipsl_CMIP6[[i]]<-list(all = all)
  names(data_ipsl_CMIP6)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
 
}

names(data_ipsl_CMIP6)

# extract data GFDL ---- 

data_gfdl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("gfdl-esm4_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut126<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = FALSE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  if (variable_to_extract3[[i]] == "tos"){
    all<-get_timeSeries_temperature(hist, fut126, fut585, output = "yearly")
  }else {
    
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }

    all<-get_timeSeries(hist, fut126, fut585, output = "yearly")
  }
  
  data_gfdl_CMIP6[[i]]<-list(all = all)
  names(data_gfdl_CMIP6)[[i]]<-variable_to_extract[i]

  rm(hist, fut126, fut585, all)
 
}

names(data_gfdl_CMIP6)

```

# save outputs ISIMIP3b temp 

```{r}

save(data_ipsl_CMIP6, data_gfdl_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_trends_inputs_CMIP6.RData")

```

# load data

```{r}

rm(list=ls())
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_trends_inputs_CMIP5.RData")
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_trends_inputs_CMIP6.RData")

```

# Load libraries for netcdf and define variables

```{r load CMIP5}

library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")

variable_to_extract <-c("to", "pp")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

```

# mean and sd of the above across models and ssp for both CMIP5 and CMIP6

```{r}

# need to loop through variables. 

all<-list()

for (i in 1:length(variable_to_extract)){
  
  # i = 2
  # CMIP5 
  data_ipsl_CMIP5_tcb<-as.data.frame(data_ipsl_CMIP5[[i]]$all) %>% 
    mutate(cmip = 5, 
           earth = "ipsl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  data_gfdl_CMIP5_tcb<-as.data.frame(data_gfdl_CMIP5[[i]]$all) %>% 
    mutate(cmip = 5, 
           earth = "gfdl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  # CMIP6
  data_ipsl_CMIP6_tcb<-as.data.frame(data_ipsl_CMIP6[[i]]$all) %>% 
    mutate(cmip = 6, 
           earth = "ipsl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  data_gfdl_CMIP6_tcb<-as.data.frame(data_gfdl_CMIP6[[i]]$all) %>% 
    mutate(cmip = 6, 
           earth = "gfdl") %>% 
    `colnames<-`(c("year", "tcb", "tcbChange", "protocol", "cmip", "earth"))
  
  # add all together and  mean  it
  all[[i]]<-data_ipsl_CMIP5_tcb %>% 
    full_join(data_gfdl_CMIP5_tcb) %>% 
    full_join(data_ipsl_CMIP6_tcb) %>% 
    full_join(data_gfdl_CMIP6_tcb) %>% 
    group_by(protocol, year, cmip) %>% 
    summarise(mean = mean(tcbChange, na.rm = TRUE), 
              sd = sd(tcbChange, na.rm = TRUE)) %>% 
    mutate(sd_min = mean - sd, 
           sd_max = mean + sd) 
  
  names(all)[i]<-variable_to_extract[i]
  
  }


# create dots when CMIP6 < CMIP6 
# it shows when Cmip5 is smaller - i.e. temp increased less (better) 
trial<-all$to %>% 
  dplyr::select(cmip, mean, protocol, year) %>%
  spread(cmip, mean) %>% 
  mutate(A = ifelse(`6`> `5`,`5`, NA)) %>% 
  gather("cmip","mean", -c(protocol, year, A)) %>% 
  mutate(cmip = as.numeric(cmip))

all$to<-all$to %>% 
  full_join(trial)

# create dots when CMIP6 < CMIP6 
# it shows when cmip5 is bigger - i.e. decreased less (better)
trial<-all$pp %>% 
  dplyr::select(cmip, mean, protocol, year) %>%
  spread(cmip, mean) %>% 
  mutate(A = ifelse(`6` < `5`,`5`, NA)) %>% 
  gather("cmip","mean", -c(protocol, year, A)) %>% 
  mutate(cmip = as.numeric(cmip))

all$pp<-all$pp %>% 
  full_join(trial)


```

# FIG 3: trends in tcb  

```{r}

# transform in functions and move to Funcs_plot.r ... this is lasiness.... 
library("ggplot2")

a_to<-ggplot(filter(all$to, cmip==5), aes(group = protocol, x=year, y = mean, ymin = sd_min, ymax = sd_max))+
  annotate("rect", xmin = 1990, xmax = 2000, ymin = -Inf, ymax = Inf, alpha = .2)+
  geom_ribbon(aes(fill = protocol), alpha=0.2)+
  geom_line(aes(color = protocol)) +
  geom_vline(xintercept = 2005.5, color = "grey60", size = 2)+
  geom_vline(xintercept = 2030, linetype = "dashed", color = "grey60", size = 1)+
  geom_hline(yintercept = 0, color = "grey60", size = 1)+
  scale_y_continuous(limits = c(-5, 37), breaks = pretty(seq(37, -5), n = 10), name = "Change in temperature (%)") +
  scale_x_continuous(limits = c(1970, 2100), breaks = pretty(all$to$year, n = 10), name = "Year")+
  scale_color_manual(values = c("black","blue" ,"red"), name = NULL, labels = c("Historical", "RCP2.6", "RCP8.6"))+
  scale_fill_manual(values = c("black","blue" ,"red"), name = NULL, labels = c("Historical", "RCP2.6", "RCP8.6"))+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.title.y = element_text(vjust=0.4, size = 22),
        axis.title.x = element_text(vjust=0.3, size = 22),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.minor = element_blank(),
        legend.background=element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text.x = element_text(face = "bold"),
        legend.position = c(0.15, 0.8))

b_to<-ggplot(filter(all$to, cmip==6), aes(group = protocol, x=year, y = mean))+
  annotate("rect", xmin = 1990, xmax = 2000, ymin = -Inf, ymax = Inf, alpha = .2)+
  geom_ribbon(aes(ymin = sd_min, ymax = sd_max, fill = protocol), alpha=0.2)+
  geom_line(aes(color = protocol)) +
  geom_point(aes(y = A, color = protocol), size = 0.8)+
  geom_vline(xintercept = 2015, color = "grey60", size = 2)+
  geom_vline(xintercept = 2030, linetype = "dashed", color = "grey60", size = 1)+
  geom_hline(yintercept = 0, color = "grey60", size = 1)+
  scale_y_continuous(limits = c(-5, 37), breaks = pretty(seq(37, -5), n = 10), name = "Change in temperature (%)") +
  scale_x_continuous(limits = c(1970, 2100), breaks = pretty(all$to$year, n = 10), name = "Year")+
  scale_color_manual(values = c("black","blue" ,"red"), name = "", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  scale_fill_manual(values = c("black","blue" ,"red"), name = "", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.title.y = element_text(vjust=0.4, size = 22),
        axis.title.x = element_text(vjust=0.3, size = 22),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text.x = element_text(face = "bold"),
        legend.position = "none")

a_pp<-ggplot(filter(all$pp, cmip==5), aes(group = protocol, x=year,y = mean, ymin = sd_min, ymax = sd_max))+
  annotate("rect", xmin = 1990, xmax = 2000, ymin = -Inf, ymax = Inf, alpha = .2)+
  geom_ribbon(aes(fill = protocol), alpha=0.2)+
  geom_line(aes(color = protocol)) +
  geom_vline(xintercept = 2005.5, color = "grey60", size = 2)+
  geom_vline(xintercept = 2030, linetype = "dashed", color = "grey60", size = 1)+
  geom_hline(yintercept = 0, color = "grey60", size = 1)+
  scale_y_continuous(limits = c(-15, 15), breaks = pretty(seq(-15, 15), n = 10), name = "Change in net primary production (%)") +
  scale_x_continuous(limits = c(1970, 2100), breaks = pretty(all$pp$year, n = 10), name = "Year")+
  scale_color_manual(values = c("black","blue" ,"red"), name = NULL, labels = c("Historical", "RCP2.6", "RCP8.6"))+
  scale_fill_manual(values = c("black","blue" ,"red"), name = NULL, labels = c("Historical", "RCP2.6", "RCP8.6"))+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.title.y = element_text(vjust=0.4, size = 22),
        axis.title.x = element_text(vjust=0.3, size = 22),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.minor = element_blank(),
        legend.background=element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text.x = element_text(face = "bold"),
        legend.position = "none")

b_pp<-ggplot(filter(all$pp, cmip==6), aes(group = protocol, x=year, y = mean))+
  annotate("rect", xmin = 1990, xmax = 2000, ymin = -Inf, ymax = Inf, alpha = .2)+
  geom_ribbon(aes(ymin = sd_min, ymax = sd_max, fill = protocol), alpha=0.2)+
  geom_line(aes(color = protocol)) +
  geom_point(aes(y = A, color = protocol), size = 0.8)+
  geom_vline(xintercept = 2015, color = "grey60", size = 2)+
  geom_vline(xintercept = 2030, linetype = "dashed", color = "grey60", size = 1)+
  geom_hline(yintercept = 0, color = "grey60", size = 1)+
  scale_y_continuous(limits = c(-15, 15), breaks = pretty(seq(15, -15), n = 10), name = "Change in net primary production (%)") +
  scale_x_continuous(limits = c(1970, 2100), breaks = pretty(all$pp$year, n = 10), name = "Year")+
  scale_color_manual(values = c("black","blue" ,"red"), name = "", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  scale_fill_manual(values = c("black","blue" ,"red"), name = "", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.title.y = element_text(vjust=0.4, size = 22),
        axis.title.x = element_text(vjust=0.3, size = 22),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text.x = element_text(face = "bold"),
        legend.position = "none")

```

# FIG 4 

```{r}

library(patchwork)

# FIG 2 trends in tcb CMIP5 vs CMIP6
layout <- "
AB
CD
"

a_to<-a_to + ggtitle("A) CMIP5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b_to<-b_to + ggtitle("B) CMIP6") + theme(plot.title = element_text(size = 16, face = "bold",hjust = 0))

a_pp<-a_pp + ggtitle(" ") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b_pp<-b_pp + ggtitle(" ") + theme(plot.title = element_text(size = 16, face = "bold",hjust = 0))


plot<- a_to + b_to + 
  a_pp + b_pp + 
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig4.pdf"), height=12, width=15)
plot 
dev.off()

```


