---
title: "Plotting global models outputs"
author: "Camilla Novaglio"
date: "04/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# TO DO 

# TO CHECK 

Models maps CMIP6 - why do i have to invert matrices?  

# Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

# variables 
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values = c(0,10000) # these need to change for each model? 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)
# Define a layout function
mean_plot_colour_values = c(-50,50)
sd_plot_colour_values = c(0,50)
model_agreement_plot_colour_values = c(50,100)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots (between cmips change) # purple to green shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# Load global ISIMIP2b model data 

```{r}

# CMIP5 data location
directory = "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/"

# APECOSM ----
h_yearsA <- "1950_2005"
f_yearsA<- "2006_2100"
outputA<-"monthly"
oaA<-"no-oa"

# BOATS ----
h_yearsB <- "1971_2005"
f_yearsB<- "2006_2099"
outputB<-"monthly"
oaB<-"no-oa"

# DBEM ----
h_yearsD <- "1951_2005"
f_yearsD<- "2006_2099"
outputD<-"annual"
oaD<-"oa"

# DBPM ----
h_yearsDB <- "1950_2005"
f_yearsDB<- "2006_2100"
outputDB<-"monthly"
oaDB<-"no-oa"

# EcoOcean ----  
h_yearsE <- "1971_2005"
f_yearsE<- "2006_2100"
outputE<-"monthly"
oaE<-"no-oa"

# macroecological ----  
h_yearsM <- "1950_2005"
f_yearsM<- "2006_2100"
outputM<-"annual"
oaM<-"no-oa"

# extract data IPSL ---- 
h_years <-c(h_yearsA, h_yearsB, h_yearsD, h_yearsDB, h_yearsE, h_yearsM)
f_years <-c(f_yearsA, f_yearsB, f_yearsD, f_yearsDB, f_yearsE, f_yearsM)
output <-c(outputA, outputB, outputD, outputDB, outputE, outputM)
oa <-c(oaA, oaB, oaD, oaDB, oaE, oaM)

yearmonth1<- rep(as.yearmon("1990-01"), length(mod_ipsl))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- rep(as.yearmon("2090-01"), length(mod_ipsl))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_ipsl_CMIP5<-list()

for (i in 1:length(mod_ipsl)){

  # i = 1
  filename<-paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[2],"/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_hist_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], ".nc4")
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_rcp2p6_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_ipsl[i], "/ipsl-cm5a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), "_ipsl-cm5a-lr_nobc_rcp8p5_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_ipsl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_ipsl_CMIP5)

# add Zoom IPSL ----

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/historical/"
filename<-"zoomss_ipsl-cm5a-lr_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"
yearmonth1 = as.yearmon("1990-01")
yearmonth2 = as.yearmon("1999-01")
hist<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/future/"
filename<-"zoomss_ipsl-cm5a-lr_nobc_rcp26_nosoc_co2_tcb_global_annual_2006_2100.nc4"
yearmonth1 = as.yearmon("2090-01")
yearmonth2 = as.yearmon("2099-01")
fut126<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

filename<-"zoomss_ipsl-cm5a-lr_nobc_rcp85_nosoc_co2_tcb_global_annual_2006_2100.nc4"
fut585<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP5$ZooMSS<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# extract data GFDL ---- 

h_years <-c(h_yearsB, h_yearsD, h_yearsE, h_yearsM)
f_years <-c(f_yearsB, f_yearsD, f_yearsE, f_yearsM)
f_years[3]<-"2006_2099" #  # ecoOcean changes 
output <-c(outputB, outputD, outputE, outputM)
oa <-c(oaB, oaD, oaE, oaM)

yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_gfdl_CMIP5<-list()

for (i in 1:length(mod_gfdl)){

  # i = 1
  filename<-paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[2],"/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_hist_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], ".nc4")
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[3], "/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_rcp2p6_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  filename <- paste0(mod_gfdl[i], "/gfdl-esm2m/", protocol[3], "/", tolower(mod_gfdl[i]), "_gfdl-esm2m_nobc_rcp8p5_wo-diaz_no-fishing_",oa[i],"_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],".nc4")
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_gfdl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_gfdl_CMIP5)

# add zoom GFDL ----

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/historical/"
filename<-"zoomss_gfdl-esm2m_nobc_historical_nosoc_co2_tcb_global_annual_1950_2005.nc4"
yearmonth1 = as.yearmon("1990-01")
yearmonth2 = as.yearmon("1999-01")
hist<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

directory_zoom<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP2b/ZooMSS/_tmp/future/"
filename<-"zoomss_gfdl-esm2m_nobc_rcp26_nosoc_co2_tcb_global_annual_2006_2100.nc4"
yearmonth1 = as.yearmon("2090-01")
yearmonth2 = as.yearmon("2099-01")
fut126<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

filename<-"zoomss_gfdl-esm2m_nobc_rcp85_nosoc_co2_tcb_global_annual_2006_2100.nc4"
fut585<-averageFishCDF(directory_zoom, filename , variable_to_extract[1], yearmonth1, yearmonth2, average_whole_period = TRUE)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP5$ZooMSS<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

```

NOTES   
average_whole_period: if TRUE you are averaging data between 1990 and 1999, if FALSE you are extrapolating data for each one of the years between 1990 and 1999  
the  printed info on year is the file year extent   
here you are considering only ipsl, no fishing - but can apply the same code to the other scenarios   
DBEM dimension 0.5 deg - here taken care of   

# Plot global ISIMIP2b model outputs 

```{r map CMIP5}

## plot IPSL ----

map_ipsl585_CMIP5<-list()

mod_ipsl<-c(mod_ipsl, "ZooMSS")
model_type_ipsl<-ifelse(mod_ipsl == "DBEM","DBEM", NA) # this is because DBEM need to be plotted in 0.5 deg

for (i in 1:length(data_ipsl_CMIP5)){ 
  
  tit <- paste(mod_ipsl[i], "IPSL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_ipsl585_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl585_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(tit)
  
}

names(map_ipsl585_CMIP5)
# map_ipsl585_CMIP5$ZooMSS

### plot GFDL ----

mod_gfdl<-c(mod_gfdl, "ZooMSS")
model_type_gfdl<-ifelse(mod_gfdl == "DBEM","DBEM", NA) 
map_gfdl585_CMIP5<-list()

for (i in 1:length(data_gfdl_CMIP5)){ 
  
  tit <- paste(mod_gfdl[i], "GFDL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_gfdl585_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl585_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(tit)
  
}

names(map_gfdl585_CMIP5)
# map_gfdl585_CMIP5$ZooMSS

# RCP 2.6
## plot IPSL ----

map_ipsl126_CMIP5<-list()

for (i in 1:length(data_ipsl_CMIP5)){ 
  
  tit <- paste(mod_ipsl[i], "IPSL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_ipsl126_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl126_CMIP5)[[i]]<-mod_ipsl[[i]]
  
  rm(tit)
  
}

names(map_ipsl126_CMIP5)

### plot GFDL ----

map_gfdl126_CMIP5<-list()

for (i in 1:length(data_gfdl_CMIP5)){ 
  
  tit <- paste(mod_gfdl[i], "GFDL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP5[[i]]$hist$data_units, cmip[1], sep =" ")
  map_gfdl126_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl126_CMIP5)[[i]]<-mod_gfdl[[i]]
  
  rm(tit)
  
}

names(map_gfdl126_CMIP5)

```

# Deal with model set  

```{r}

# # if still missing from CMIP6... remove from Lotze model set, otherwise include...  
# data_ipsl_CMIP5$APECOSM<-NULL
# data_gfdl_CMIP5$APECOSM<-NULL
# 
# names(data_ipsl_CMIP5)
# names(data_gfdl_CMIP5)
# data_ipsl_CMIP5$APECOSM

```


# Model average for CMIP5 

```{r}

# RCP 8.5
# MAKE SURE THAT ALL MATRICES ARE ON ONE DEGREE SCALE
### TEMPORARY - JUST TAKE THE VALUE FROM CLOSE POINT
lons_to_use = seq(1,719,2)
lats_to_use = seq(1,359,2)

data_ipsl_CMIP5$DBEM$diff_8p5 = data_ipsl_CMIP5$DBEM$diff_8p5[lons_to_use, lats_to_use] 
data_gfdl_CMIP5$DBEM$diff_8p5 = data_gfdl_CMIP5$DBEM$diff_8p5[lons_to_use, lats_to_use] 

# model average - see model_stat() in HelperScripts.R

res_ipsl<-model_stat(data_ipsl_CMIP5, esm = 'diff_8p5')
model_average_ipsl_CMIP5<-res_ipsl$model_average
model_sd_ipsl_CMIP5<-res_ipsl$model_sd
model_agreement_ipsl_CMIP5<- res_ipsl$model_agreement

res_gfdl<-model_stat(data_gfdl_CMIP5, esm = 'diff_8p5')
model_average_gfdl_CMIP5<-res_gfdl$model_average
model_sd_gfdl_CMIP5<-res_gfdl$model_sd
model_agreement_gfdl_CMIP5<- res_gfdl$model_agreement

# if you want the plot to be exactly as per Lotze (DBEM gfdl in agreement was not considered)
# data_gfdl_CMIP52$DBEM$diff_8p5<-NULL

res_all<-model_stat(c(data_ipsl_CMIP5, data_gfdl_CMIP5), esm = 'diff_8p5')
model_average_all_CMIP5<-res_all$model_average
model_sd_all_CMIP5<-res_all$model_sd
model_agreement_all_CMIP5<- res_all$model_agreement 

# # define title IPSL
# maptitle_average = paste("Mean % change IPSL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_sd = paste("Standard Deviation IPSL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_agreement = paste("Agreement IPSL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# 
# # Plot the model average and standard deviation
# avarage_CMIP5_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
# sd_CMIP5_ipsl<-plot_FISH_MIP(model_sd_ipsl_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
# agreement_CMIP5_ipsl<-plot_FISH_MIP(model_agreement_ipsl_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") # why is this white along all coasts?!
# 
# # define title GFDL
# maptitle_average = paste("Mean % change GFDL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_sd = paste("Standard Deviation GFDL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# maptitle_agreement = paste("Agreement GFDL RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
# 
# # Plot the model average and standard deviation
# avarage_CMIP5_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
# sd_CMIP5_gfdl<-plot_FISH_MIP(model_sd_gfdl_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
# agreement_CMIP5_gfdl<-plot_FISH_MIP(model_agreement_gfdl_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") 

# define title All
maptitle_average = paste("Mean % change RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 8.5, 1990s to 2090s CMIP5", sep=" ")
maptitle_agreement = paste("Agreement RCP 8.5, 1990s to 2090s CMIP5", sep=" ")

# Plot the model average and standard deviation

# NEED CONTOURS X 3 plots below bt average only - added an argument to below function contours = TRUE but this is not working yet... 

avarage_CMIP5_all<-plot_FISH_MIP(model_average_all_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP5_all<-plot_FISH_MIP(model_sd_all_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP5_all<-plot_FISH_MIP(model_agreement_all_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot averadge by esm 
avarage_CMIP5_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP5, "Mean % change RCP 8.5, 1990s to 2090s CMIP5 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP5_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP5, "Mean % change RCP 8.5, 1990s to 2090s CMIP5 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

# RCP 2.6

data_ipsl_CMIP5$DBEM$diff_2p6 = data_ipsl_CMIP5$DBEM$diff_2p6[lons_to_use, lats_to_use] 
data_gfdl_CMIP5$DBEM$diff_2p6 = data_gfdl_CMIP5$DBEM$diff_2p6[lons_to_use, lats_to_use] 

# model average - see model_stat() in HelperScripts.R

res_ipsl_126<-model_stat(data_ipsl_CMIP5, esm = 'diff_2p6')
model_average_ipsl_CMIP5_126<-res_ipsl_126$model_average
model_sd_ipsl_CMIP5_126<-res_ipsl_126$model_sd
model_agreement_ipsl_CMIP5_126<- res_ipsl_126$model_agreement

res_gfdl_126<-model_stat(data_gfdl_CMIP5, esm = 'diff_2p6')
model_average_gfdl_CMIP5_126<-res_gfdl_126$model_average
model_sd_gfdl_CMIP5_126<-res_gfdl_126$model_sd
model_agreement_gfdl_CMIP5_126<- res_gfdl_126$model_agreement

# if you want the plot to be exactly as per Lotze (DBEM gfdl in agreemetn was not considered)
# data_gfdl_CMIP52$DBEM$diff_8p5<-NULL

res_all_126<-model_stat(c(data_ipsl_CMIP5, data_gfdl_CMIP5), esm = 'diff_2p6')
model_average_all_CMIP5_126<-res_all_126$model_average
model_sd_all_CMIP5_126<-res_all_126$model_sd
model_agreement_all_CMIP5_126<- res_all_126$model_agreement 

# define title All
maptitle_average = paste("Mean % change RCP 2.6, 1990s to 2090s CMIP5", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 2.6, 1990s to 2090s CMIP5", sep=" ")
maptitle_agreement = paste("Agreement RCP 2.6, 1990s to 2090s CMIP5", sep=" ")

# Plot the model average and standard deviation

# NEED CONTOURS X 3 plots below bt average only - added an argument to below function contours = TRUE but this is not working yet... 

avarage_CMIP5_all_126<-plot_FISH_MIP(model_average_all_CMIP5, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP5_all_126<-plot_FISH_MIP(model_sd_all_CMIP5, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP5_all_126<-plot_FISH_MIP(model_agreement_all_CMIP5, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot averadge by esm 
avarage_CMIP5_ipsl_126<-plot_FISH_MIP(model_average_ipsl_CMIP5, "Mean % change RCP 2.6, 1990s to 2090s CMIP5 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP5_gfdl_126<-plot_FISH_MIP(model_average_gfdl_CMIP5, "Mean % change RCP 2.6, 1990s to 2090s CMIP5 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

```

# save outputs ISIMIP2b temp 

```{r}

data_summaries_CMIP5<-list(res_all= res_all, res_ipsl = res_ipsl, res_gfdl = res_gfdl, res_all_126= res_all_126, res_ipsl_126 = res_ipsl_126, res_gfdl_126 = res_gfdl_126)

map_summaries_CMIP5<-list(avarage_CMIP5_all = avarage_CMIP5_all, sd_CMIP5_all = sd_CMIP5_all, agreement_CMIP5_all = agreement_CMIP5_all, avarage_CMIP5_ipsl = avarage_CMIP5_ipsl, avarage_CMIP5_gfdl = avarage_CMIP5_gfdl, avarage_CMIP5_all_126 = avarage_CMIP5_all_126, sd_CMIP5_all_126 = sd_CMIP5_all_126, agreement_CMIP5_all_126 = agreement_CMIP5_all_126, avarage_CMIP5_ipsl_126 = avarage_CMIP5_ipsl_126, avarage_CMIP5_gfdl_126 = avarage_CMIP5_gfdl_126)

save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, map_ipsl126_CMIP5, map_gfdl126_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5.RData")

# save(data_ipsl_CMIP5, data_gfdl_CMIP5, map_ipsl585_CMIP5, map_gfdl585_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5_noApecosm.RData")

```

# Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/"

# variables 
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values = c(0,10000) # these need to change for each model? 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)
# Define a layout function
mean_plot_colour_values = c(-50,50)
sd_plot_colour_values = c(0,50)
model_agreement_plot_colour_values = c(50,100)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots (between cmips change) # purple to green shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# Load global ISIMIP3b model data

```{r load CMIP6}

# run first 2 sections if you are not running the CMIP5 sections

directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/"
# 
# # # CHECK GFDL DBPM .... is it corrupted? YES - need to rerun .... re-run and it's OK now but the map shows some white parallel lines which migth be due to cell not being run ... strange! re-run but still the same.... ned to check with Ryan! 
# filename<-"dbpm_gfdl-esm4_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBPM/_tmp/gfdl-esm4/future/"
# 
# fut126<- averageFishCDF(directory, filename, variable_to_extract[1], as.yearmon("2090-01"), as.yearmon("2099-12"), average_whole_period = TRUE, CMIP = 6)
# 
# image(fut126$fishvar)

# # CHECK IPSL DBPM .... is it corrupted? NO - I don't understand why the same code now produces corrupted new outputs (GFDL + size-spectrum) - I might have deleted print(lat) and print(log) when printing output to the matrix between IPSL and GFDL + size-spectrum netdfs runs... that was the bug for GFDL and the size-spectrum outputs
# # print("-169")
# # paste("-169")
# filename<-"dbpm_ipsl-cm6a-lr_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBPM/_tmp/ipsl-cm6a-lr/future/"
# 
# fut126<- averageFishCDF(directory, filename, variable_to_extract[1], as.yearmon("2090-01"), as.yearmon("2099-12"), average_whole_period = TRUE, CMIP = 6)
# 
# dim(fut126$fishvar)
# image(fut126$fishvar)
# fut126$fishvar[90:92, 90:92]
# 
# 
# # CHECK IPSL DBPM .... all good when you overwrite the outputs by mistake? - all good 
# # print("-169")
# # paste("-169")
# filename<-"dbpm_ipsl-cm6a-lr_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/Desktop/"
# 
# fut1262<- averageFishCDF(directory, filename, variable_to_extract[1], as.yearmon("2090-01"), as.yearmon("2099-12"), average_whole_period = TRUE, CMIP = 6)
# 
# dim(fut1262$fishvar)
# image(fut1262$fishvar)
# fut1262$fishvar[90:92, 90:92]

# # # CHECK FEISTY ... dimension order changed between versions (before after last Matthias correction)? NO and warning below is OK because the order in which the dimensions are specified is different than the order of the dimension in the data array...  
# filename<-"feisty_ipsl-cm6a-lr_nobasd_ssp126_nat_default_tcb_global_monthly_2015_2100.nc"
# directory <- "/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/FEISTY_beforeUpdate/_tmp/ipsl-cm6a-lr/future/"
# nc <- nc_open(paste(directory, filename, sep = ""))
# print(nc)

mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL", "EcoTroph", "FEISTY", "ZooMSS") 
mod_ipsl <- c("APECOSM","BOATS","DBPM","MACROECOLOGICAL","FEISTY","ZooMSS") 

# APECOSM ----
# will be updated 
h_yearsA <- "1950_2014"
f_yearsA<- "2015_2100"
earthA<-"_ipsl-cm6a-lr_nobasd_"
outputA<-"monthly"
extensionA<-".nc"

# APECOSM ----
# to update 
h_yearsA <- "1850_2014"
f_yearsA<- "2015_2100"
earthA<-"_ipsl-esm4_nobc_" # will change ....
outputA<-"monthly"
extensionA<-".nc" 

# BOATS ----
h_yearsB <- "1950_2014"
f_yearsB<- "2015_2100"
earthB<-"_ipsl-cm6a-lr_nobc_"
outputB<-"monthly"
extensionB<-".nc"

# DBEM ----
# added below

# DBPM ----
h_yearsDB <- "1850_2014"
f_yearsDB<- "2015_2100"
earthDB<-"_ipsl-cm6a-lr_nobasd_"
outputDB<-"monthly" 
extensionDB <-".nc"

# EcoOcean ----  
# added below  

# macroecological ----  
h_yearsM <- "1950_2014"
f_yearsM<- "2015-2100"
earthM<-"_ipsl-cm6a-lr_nobc_"
outputM<-"annual"
extensionM<-".nc"

# EcoTroph ----  
h_yearsE <- "1950-2014"
f_yearsE<- "2015-2100"
earthE<-"_ipsl-cm6a_nobc_"
outputE<-"annual"
extensionE<-".nc"

# FEISTY ----  
h_yearsF <- "1950_2014"
f_yearsF<- "2015_2100"
earthF<-"_ipsl-cm6a-lr_nobasd_" 
outputF<-"monthly"
extensionF<-".nc"

# ZooMSS ----  
h_yearsZ <- "1950_2014"
f_yearsZ<- "2015_2100"
earthZ<-"_ipsl-cm6a-lr_nobasd_"
outputZ<-"annual"
extensionZ<-".nc"

# extract data IPSL ---- 
h_years <-c(h_yearsA,h_yearsB, h_yearsDB, h_yearsM,h_yearsF, h_yearsZ) 
f_years <-c(f_yearsA, f_yearsB, f_yearsDB, f_yearsM,f_yearsF, f_yearsZ) 
earth <-c(earthA, earthB, earthDB, earthM, earthF, earthZ) 
output <-c(outputA, outputB, outputDB, outputM, outputF, outputZ) 
extension <-c(extensionA, extensionB, extensionDB,extensionM,extensionF,extensionZ) 

# same as above but need to re-do as here outputs are from a different set of models
yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_ipsl_CMIP6<-list()

# NOTE: warning for Feisty are OK - see above 

for (i in 1:length(mod_ipsl)){

  # i = 1
  # file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/APECOSM/_tmp/ipsl-cm6a-lr/historical/apecosm_ipsl-esm4_nobc_historical_nat_default_tcb_global_monthly_1950_1989.nc"
  filename<-paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[2],"/", tolower(mod_ipsl[i]), earth[i], "historical_nat_default_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], extension[i])
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE, CMIP =  6)
  
  filename <- paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), earth[i], "ssp126_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE, CMIP = 6)
  
  filename <- paste0(mod_ipsl[i], "/_tmp/ipsl-cm6a-lr/", protocol[3], "/", tolower(mod_ipsl[i]), earth[i], "ssp585_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE,CMIP = 6)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_ipsl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP6)[[i]]<-mod_ipsl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_ipsl_CMIP6)

# add EcoTrpoh IPSL ----
# naming mistakes that complicate uploading - Matthias check will fix them 
# write function for ecothroph 

time1_h = 1990 
time2_h = 1999
time1_f = 2090 # here the file is one so need to read-in the same file and  use it to calculate these averages
time2_f = 2099

averageFishCDF_EcoTroph<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE){
  
  # Open the netcdf file
  nc <- nc_open(file)
  var <-names(nc$var)
  # Extract important information
  data_attributes <- ncatt_get(nc, var) # variable is called "Band1" instead of "tcb"
  main_title <- data_attributes$long_field_name
  data_units <- data_attributes$units
    
  lon <- ncvar_get(nc, "lon")
  lat <- ncvar_get(nc, "lat")

  # time_vector <- convert_model_dates_CMIP6(nc, model_type) 
  # new convert_model_dates_CMIP6 for this model 
  time_months <- ncvar_get(nc, "time")
  print(nc$dim$time$units) # annual since 1950.....
  yearmonth = as.yearmon("1950-01")
  time_months = floor(as.numeric(as.yearmon(yearmonth + seq(0, (length(time_months) - 1)))))
  time_vector<-time_months
  print(time_months[1])
  print(time_months[length(time_months)])
  # print("but  hist and fut will extract at different time points")

  #  opposite of averaging the whole period ... line 488 in original function
  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  temp_array1 <-ncvar_get(nc, var)[, , tpte$start_point_to_extract:tpte$end_point_to_extract]
  # Extract averages
  for (ii in 1:length(lon)){
    for (jj in 1:length(lat))
      {
      # Fill in 2D matrix of whole time-period averages 
      new_var_mat[ii, jj] = mean(temp_array1[ii, jj, ])
    }
    }
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

if(can_model_units_be_standardized(data_units, convert_to_kg_km))
    {
      new_var_mat = new_var_mat * 1000
      data_units = "kg km-2" 
      }
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

# hist is the beginning of the future files and  I am assuming is the same for both futures 
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc"
hist<-averageFishCDF_EcoTroph(file, time1_h, time2_h)
fut126<-averageFishCDF_EcoTroph(file, time1_f, time2_f)
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/ipsl-cm6a-lr/future/ecotroph_ipsl-cm6a-lr_nobc_ssp585_nat_default_tcb_annual_1950_2100.nc"
fut585<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$EcoTroph<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add EcoOcean IPSL ----

# this is very different as inputs are RDS files ... I hope it changes so that we don't have to guess stuff

averageFishCDF_EcoOcean<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE, type = "hist"){
  
  # data_ipsl_CMIP6$BOATS$hist
  # time1 = time1_h
  # time2 = time2_h
  # type = "fut"
  
  # Open the netcdf file
  nc <- file
  # Extract important information
  data_attributes <- "guess" # should be "tcb"
  main_title <- "guess"
  data_units <- "guess"
    
  lon <- data_ipsl_CMIP6$BOATS$hist$lon
  lat <- data_ipsl_CMIP6$BOATS$hist$lat

  # time_vector <- convert_model_dates_CMIP6(nc, model_type) 
  time_months <- seq(1, dim(nc)[3])
  
  if(type == "hist"){
    yearmonth = as.yearmon("1949-12") + time_months[1] / 12
    }else{
      yearmonth = as.yearmon("2006-01") + time_months[1] / 12 # this should be 2015 for CMIP6 but these files adopted CMIP5 convention
      }

  time_months = as.yearmon(yearmonth + seq(0, (length(time_months) - 1)) / 12)     
  tail(time_months)
  time_vector<-time_months
  print(time_months[1])
  print(time_months[length(time_months)])

  # line 488 in original function
  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  temp_array1 <-nc[, , tpte$start_point_to_extract:tpte$end_point_to_extract]
  dim(temp_array1)
  
  # Extract averages
  for (ii in 1:length(lon)){
    for (jj in 1:length(lat))
      {
      # Fill in 2D matrix of whole time-period averages 
      new_var_mat[ii, jj] = mean(temp_array1[ii, jj, ])
    }
    }
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

  # this should be done when we know the data units 
  new_var_mat = new_var_mat * 1000
  data_units = "kg km-2" 
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_historical_nosoc_default_tcb_global_monthly_1950-2005.RDS")
hist<-averageFishCDF_EcoOcean(file, time1_h, time2_h, type = "hist")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp126_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut126<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp585_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut585<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$EcoOcean<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add DBEM IPSL ----

# these are RData files similar to EcoOcean but the data layout is very different

averageFishCDF_DBEM<-function(file, time1, time2, average_whole_period = TRUE, convert_to_kg_km = TRUE){
  
  # # data_ipsl_CMIP6$BOATS$hist
  # time1 = time1_h
  # time2 = time2_h
  # type = "hist"
  
  # Open the netcdf file
  nc <- file
  # Extract important information
  data_attributes <- "tcb"
  main_title <- "guess"
  data_units <- "guess"
    
  lon <- unique(coord$lon)
  lat <- unique(coord$lat)

  # time_vector <- convert_model_dates_CMIP6(nc, model_type) 
  time_months <- seq(1951, 2100)
  yearmonth = as.yearmon("1951-01")

  time_months = as.yearmon(yearmonth + seq(0, (length(time_months) - 1)))     
  time_vector<-time_months
  print(time_months[1])
  print(time_months[length(time_months)])

  # line 488 in original function
  # Create a new matrix to hold the results
  new_var_mat = array(rep(0, length(lon) * length(lat)), c(length(lon), length(lat)))
      
  # Get the correct time period to extract
  tpte = time_period_to_extract(time1, time2, time_vector)

  # Now get the variable of interest
  # dimension and data format are different than for other models, so need different way of extracting data. GRID CELL X YEAR
  temp_array1 <-nc[,tpte$start_point_to_extract:tpte$end_point_to_extract]
  # Extract averages
  new_var_vec<-rowMeans(temp_array1)
  new_var_df<-cbind(coord, new_var_vec)
  new_var_df<-new_var_df[,-1]
  library(reshape2)
  new_var_mat<-acast(new_var_df, lon~lat, value.var="new_var_vec")
  
  years = paste(as.character(time1_h), "to", as.character(time2_h), sep=" ")

  # this should be done when we know the data units 
  new_var_mat = new_var_mat * 1000
  data_units = "kg km-2" 
    
  return_list <- list(
        main_title = main_title,
        data_units = data_units,
        lon = lon,
        lat = lat,
        years = years,
        fishvar = new_var_mat
      )
}

coord<-read.delim("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/Lat_Lon.txt", header = FALSE, sep = ",")
colnames(coord)<-c("grid", "lon", "lat")
file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6IPSL26F0_t2_Abd.RData")
file<-sppfnlmap
hist<-averageFishCDF_DBEM(file, time1_h, time2_h)
fut126<-averageFishCDF_DBEM(file, time1_f, time2_f)
file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6IPSL85F0_t2_Abd.RData")
file<-sppfnlmap
fut585<-averageFishCDF_DBEM(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_ipsl_CMIP6$DBEM<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# extract data GFDL ---- 

mod_gfdl <- c("BOATS","DBPM" ,"MACROECOLOGICAL","ZooMSS", "FEISTY") 

h_years <-c(h_yearsB,h_yearsDB, h_yearsM, h_yearsZ,h_yearsF) 
f_years <-c(f_yearsB,f_yearsDB, f_yearsM, f_yearsZ, f_yearsF) 
earth<-c("_gfdl-esm4_nobc_","_gfdl-esm4_nobasd_","_gfdl-esm4_nobc_","_gfdl-esm4_nobasd_","_gfdl-esm4_nobasd_")
output <-c(outputB,outputDB, outputM, outputZ, outputF) 
extension <-c(extensionB, extensionDB,extensionM, extensionZ, extensionF) 

yearmonth1<- ifelse(output=="annual", as.yearmon("1990-01"), as.yearmon("1990-01"))
yearmonth2<- ifelse(output!="annual", as.yearmon("1999-12"), as.yearmon("1999-01"))

yearmonth1_fut<- ifelse(output=="annual", as.yearmon("2090-01"), as.yearmon("2090-01"))
yearmonth2_fut<- ifelse(output!="annual", as.yearmon("2099-12"), as.yearmon("2099-01"))

data_gfdl_CMIP6<-list()

for (i in 1:length(mod_gfdl)){

  # i = 4
  filename<-paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[2],"/", tolower(mod_gfdl[i]), earth[i], "historical_nat_default_",variable_to_extract[1],"_global_", output[i], "_", h_years[i], extension[i])
  
  hist<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1[i], yearmonth2[i], average_whole_period = TRUE, CMIP =  6)

  filename <- paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[3], "/", tolower(mod_gfdl[i]), earth[i], "ssp126_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut126<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE, CMIP = 6)
  
  filename <- paste0(mod_gfdl[i], "/_tmp/gfdl-esm4/", protocol[3], "/", tolower(mod_gfdl[i]), earth[i], "ssp585_nat_default_",variable_to_extract[1],"_global_",output[i], "_",f_years[i],extension[i])
  
  fut585<- averageFishCDF(directory, filename , variable_to_extract[1], yearmonth1_fut[i], yearmonth2_fut[i], average_whole_period = TRUE,CMIP = 6)
  
  diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
  diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
  data_gfdl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP6)[[i]]<-mod_gfdl[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_gfdl_CMIP6)

# add EcoTroph GFDL ----

# hist is the beginning of the future files and  I am assuming is the same for both futures 
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/gfdl-esm4/future/ecotroph_gfdl-esm4_nobc_ssp126_nat_default_tcb_annual_1950_2100.nc"
hist<-averageFishCDF_EcoTroph(file, time1_h, time2_h)
fut126<-averageFishCDF_EcoTroph(file, time1_f, time2_f)
file<-"/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoTroph/_tmp/gfdl-esm4/future/ecotroph_gfdl-esm4_nobc_ssp585_nat_default_tcb_annual_1950_2100.nc"
fut585<-averageFishCDF_EcoTroph(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  
data_gfdl_CMIP6$EcoTroph<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

names(data_gfdl_CMIP6)

# add EcoOcean GFDL ----

file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_gfdl_nobc_historical_nosoc_default_tcb_global_monthly_1950-2005.RDS")
hist<-averageFishCDF_EcoOcean(file, time1_h, time2_h, type = "hist")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp126_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut126<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")
file<-readRDS("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/EcoOcean CMIP6 RDS files/ecoocean_ipsl_nobc_ssp585_nosoc_default_tcb_global_monthly_2006_2100.RDS")
fut585<-averageFishCDF_EcoOcean(file, time1_f, time2_f, type = "fut")

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100 
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP6$EcoOcean<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

# add DBEM GFDL ----

file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6GFDL26F0_t2_Abd.RData")
file<-sppfnlmap
hist<-averageFishCDF_DBEM(file, time1_h, time2_h)
fut126<-averageFishCDF_DBEM(file, time1_f, time2_f)
file<-load("/Users/camillan/fishmip_outputs/marine-fishery_global_ISIMIP3b/DBEM_RData/C6GFDL85F0_t2_Abd.RData")
file<-sppfnlmap
fut585<-averageFishCDF_DBEM(file, time1_f, time2_f)

diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100  
diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100

data_gfdl_CMIP6$DBEM<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)

```

# Plot global ISIMIP3b model outputs 

```{r plot CMIP6}

########## first you need to FLIP MATRICES 

fliplr_matrix<- function(data_to_flip){
  temp= data_to_flip
  for (ii in 1:dim(data_to_flip)[2])
    data_to_flip[,ii] = temp[,dim(data_to_flip)[2] - ii + 1]
  
  data_to_flip
}

# plot IPSL ----

# # I re-grid everything from -180 to 180 inside the plot function
# # FEISTY should be an example of the final/Mathias checked file (though still from -179.5, as used old inputs) and apecosm should be en example of model using the newest inputs (-180 to 180).... 
# data_ipsl_CMIP6$DBPM$hist$lon
# data_ipsl_CMIP5$DBPM$hist$lon
# data_ipsl_CMIP6$ZooMSS$hist$lon
# data_ipsl_CMIP5$ZooMSS$hist$lon
# # tit <- paste("a")
# # trial<-plot_FISH_MIP(data_ipsl_CMIP6$DBPM$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)")

# not necessary any more for APECOSm given the new runs .... not sure why... 
# data_ipsl_CMIP6$APECOSM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$hist$fishvar)
# data_ipsl_CMIP6$APECOSM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$fut126$fishvar)
# data_ipsl_CMIP6$APECOSM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$fut585$fishvar)
# data_ipsl_CMIP6$APECOSM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$diff_2p6)
# data_ipsl_CMIP6$APECOSM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$APECOSM$diff_8p5)

# not necessary anymore ...! why?! with the new runs
# dim(data_ipsl_CMIP6$DBPM$hist$fishvar)
# image(data_ipsl_CMIP6$DBPM$diff_8p5)
# image(data_ipsl_CMIP6$APECOSM$diff_8p5)
# image(data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5)
# data_ipsl_CMIP6$DBPM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBPM$hist$fishvar)
# data_ipsl_CMIP6$DBPM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBPM$fut126$fishvar)
# data_ipsl_CMIP6$DBPM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBPM$fut585$fishvar)
# data_ipsl_CMIP6$DBPM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$DBPM$diff_2p6)
# data_ipsl_CMIP6$DBPM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$DBPM$diff_8p5)

data_ipsl_CMIP6$MACROECOLOGICAL$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$hist$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$fut126$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$fut585$fishvar)
data_ipsl_CMIP6$MACROECOLOGICAL$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$diff_2p6)
data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5)

data_ipsl_CMIP6$ZooMSS$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$hist$fishvar)
data_ipsl_CMIP6$ZooMSS$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$fut126$fishvar)
data_ipsl_CMIP6$ZooMSS$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$fut585$fishvar)
data_ipsl_CMIP6$ZooMSS$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$diff_2p6)
data_ipsl_CMIP6$ZooMSS$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$ZooMSS$diff_8p5)

data_ipsl_CMIP6$FEISTY$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$hist$fishvar)
data_ipsl_CMIP6$FEISTY$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$fut126$fishvar)
data_ipsl_CMIP6$FEISTY$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$fut585$fishvar)
data_ipsl_CMIP6$FEISTY$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$diff_2p6)
data_ipsl_CMIP6$FEISTY$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$FEISTY$diff_8p5)

data_ipsl_CMIP6$EcoTroph$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$hist$fishvar)
data_ipsl_CMIP6$EcoTroph$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$fut126$fishvar)
data_ipsl_CMIP6$EcoTroph$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$fut585$fishvar)
data_ipsl_CMIP6$EcoTroph$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$diff_2p6)
data_ipsl_CMIP6$EcoTroph$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$EcoTroph$diff_8p5)

data_ipsl_CMIP6$EcoOcean$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$hist$fishvar)
data_ipsl_CMIP6$EcoOcean$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$fut126$fishvar)
data_ipsl_CMIP6$EcoOcean$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$fut585$fishvar)
data_ipsl_CMIP6$EcoOcean$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$diff_2p6)
data_ipsl_CMIP6$EcoOcean$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$EcoOcean$diff_8p5)

data_ipsl_CMIP6$DBEM$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$hist$fishvar)
data_ipsl_CMIP6$DBEM$fut126$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$fut126$fishvar)
data_ipsl_CMIP6$DBEM$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP6$DBEM$fut585$fishvar)
data_ipsl_CMIP6$DBEM$diff_2p6<- fliplr_matrix(data_ipsl_CMIP6$DBEM$diff_2p6)
data_ipsl_CMIP6$DBEM$diff_8p5<- fliplr_matrix(data_ipsl_CMIP6$DBEM$diff_8p5)


move_hemispheres<- function(data_to_flip){
  temp= data_to_flip
  data_to_flip[1:180,] = temp[181:360,]
  data_to_flip[181:360,] = temp[1:180,]
  data_to_flip
}
  
data_ipsl_CMIP6$EcoOcean$hist$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$hist$fishvar)
data_ipsl_CMIP6$EcoOcean$fut126$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$fut126$fishvar)
data_ipsl_CMIP6$EcoOcean$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$fut585$fishvar)
data_ipsl_CMIP6$EcoOcean$diff_2p6<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$diff_2p6)
data_ipsl_CMIP6$EcoOcean$diff_8p5<- move_hemispheres(data_ipsl_CMIP6$EcoOcean$diff_8p5)

map_ipsl585_CMIP6<-list()
names(data_ipsl_CMIP6)

model_type_ipsl<-ifelse(names(data_ipsl_CMIP6) == "DBEM","DBEM", NA) # this is because DBEM need to be plotted in 0.5 deg

for (i in 1:length(data_ipsl_CMIP6)){ 
  
  # i = 3
  tit <- paste(names(data_ipsl_CMIP6)[i], "IPSL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_ipsl585_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl585_CMIP6)[[i]]<-names(data_ipsl_CMIP6)[[i]]
  
  rm(tit)
  
}

names(map_ipsl585_CMIP6)
map_ipsl585_CMIP6$DBPM

# plot GFDL ----

# flip matrix 

data_gfdl_CMIP6$MACROECOLOGICAL$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$hist$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$fut126$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$fut585$fishvar)
data_gfdl_CMIP6$MACROECOLOGICAL$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$diff_2p6)
data_gfdl_CMIP6$MACROECOLOGICAL$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$MACROECOLOGICAL$diff_8p5)

data_gfdl_CMIP6$ZooMSS$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$hist$fishvar)
data_gfdl_CMIP6$ZooMSS$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$fut126$fishvar)
data_gfdl_CMIP6$ZooMSS$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$fut585$fishvar)
data_gfdl_CMIP6$ZooMSS$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$diff_2p6)
data_gfdl_CMIP6$ZooMSS$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$ZooMSS$diff_8p5)

# ### POSSIBLE PROBLEMS HERE .... working without flipping matrix but done for IPSL...
# data_gfdl_CMIP6$FEISTY$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$hist$fishvar)
# data_gfdl_CMIP6$FEISTY$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$fut126$fishvar)
# data_gfdl_CMIP6$FEISTY$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$fut585$fishvar)
# data_gfdl_CMIP6$FEISTY$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$diff_2p6)
# data_gfdl_CMIP6$FEISTY$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$FEISTY$diff_8p5)

data_gfdl_CMIP6$EcoTroph$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$hist$fishvar)
data_gfdl_CMIP6$EcoTroph$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$fut126$fishvar)
data_gfdl_CMIP6$EcoTroph$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$fut585$fishvar)
data_gfdl_CMIP6$EcoTroph$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$diff_2p6)
data_gfdl_CMIP6$EcoTroph$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$EcoTroph$diff_8p5)

data_gfdl_CMIP6$EcoOcean$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$hist$fishvar)
data_gfdl_CMIP6$EcoOcean$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$fut126$fishvar)
data_gfdl_CMIP6$EcoOcean$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$fut585$fishvar)
data_gfdl_CMIP6$EcoOcean$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$diff_2p6)
data_gfdl_CMIP6$EcoOcean$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$EcoOcean$diff_8p5)

data_gfdl_CMIP6$DBEM$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$hist$fishvar)
data_gfdl_CMIP6$DBEM$fut126$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$fut126$fishvar)
data_gfdl_CMIP6$DBEM$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$DBEM$fut585$fishvar)
data_gfdl_CMIP6$DBEM$diff_2p6<- fliplr_matrix(data_gfdl_CMIP6$DBEM$diff_2p6)
data_gfdl_CMIP6$DBEM$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$DBEM$diff_8p5)

# move hemisphere  
data_gfdl_CMIP6$EcoOcean$hist$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$hist$fishvar)
data_gfdl_CMIP6$EcoOcean$fut126$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$fut126$fishvar)
data_gfdl_CMIP6$EcoOcean$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$fut585$fishvar)
data_gfdl_CMIP6$EcoOcean$diff_2p6<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$diff_2p6)
data_gfdl_CMIP6$EcoOcean$diff_8p5<- move_hemispheres(data_gfdl_CMIP6$EcoOcean$diff_8p5)

map_gfdl585_CMIP6<-list()
names(data_gfdl_CMIP6)

model_type_gfdl<-ifelse(names(data_gfdl_CMIP6) == "DBEM","DBEM", NA) # this is because DBEM need to be plotted in 0.5 deg

names(data_gfdl_CMIP6)

for (i in 1:length(data_gfdl_CMIP6)){ 
  
  # i = 1
  tit <- paste(names(data_gfdl_CMIP6)[i], "GFDL RCP8.5 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_gfdl585_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl585_CMIP6)[[i]]<-names(data_gfdl_CMIP6)[[i]]
  
  rm(tit)
  
}

names(map_gfdl585_CMIP6)

## RCP 2.6

#IPSL

map_ipsl126_CMIP6<-list()

for (i in 1:length(data_ipsl_CMIP6)){ 

  tit <- paste(names(data_ipsl_CMIP6)[i], "IPSL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_ipsl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_ipsl126_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_ipsl[i])
  names(map_ipsl126_CMIP6)[[i]]<-names(data_ipsl_CMIP6)[[i]]
  
  rm(tit)
  
}

# GFDL

map_gfdl126_CMIP6<-list()

for (i in 1:length(data_gfdl_CMIP6)){ 

  tit <- paste(names(data_gfdl_CMIP6)[i], "GFDL RCP2.6 no-fishing percentage change", variable_to_extract[1], data_gfdl_CMIP6[[i]]$hist$data_units, cmip[2], sep =" ")
  map_gfdl126_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_2p6, tit, delta_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n Change \n (%)", model_type = model_type_gfdl[i])
  names(map_gfdl126_CMIP6)[[i]]<-names(data_gfdl_CMIP6)[[i]]
  
  rm(tit)
  
}

```

# Deal with model set *2 set of models for main and SI for CMIP6*  

```{r}

# # remove models that you don't want to include first 
# data_ipsl_CMIP6$APECOSM<-NULL
# data_gfdl_CMIP6$APECOSM<-NULL
data_gfdl_CMIP6$DBPM<-NULL # need to update when white parallel lines problem is solved, but the code doeas allow for DBPM inclusion now 

# # otherwise as per Lotze model set + zoom (FIG 3 + 4)
# # data_ipsl_CMIP5$ZooMSS<-NULL
# # data_gfdl_CMIP5$ZooMSS<-NULL
# # data_ipsl_CMIP6$ZooMSS<-NULL
# # data_gfdl_CMIP6$ZooMSS<-NULL
data_ipsl_CMIP6$FEISTY<-NULL
data_gfdl_CMIP6$FEISTY<-NULL
data_ipsl_CMIP6$EcoTroph<-NULL
data_gfdl_CMIP6$EcoTroph<-NULL

```

# Model average for CMIP6 

```{r}

# RCP 8.5

# # MAKE SURE THAT ALL MATRICES ARE ON ONE DEGREE SCALE - if not see CMIP5 above for DBEM 
lons_to_use = seq(1,719,2)
lats_to_use = seq(1,359,2)

data_ipsl_CMIP6$DBEM$diff_8p5 = data_ipsl_CMIP6$DBEM$diff_8p5[lons_to_use, lats_to_use] 
data_gfdl_CMIP6$DBEM$diff_8p5 = data_gfdl_CMIP6$DBEM$diff_8p5[lons_to_use, lats_to_use] 

res_ipsl<-model_stat(data_ipsl_CMIP6, esm = 'diff_8p5')
model_average_ipsl_CMIP6<-res_ipsl$model_average
model_sd_ipsl_CMIP6<-res_ipsl$model_sd
model_agreement_ipsl_CMIP6<- res_ipsl$model_agreement

res_gfdl<-model_stat(data_gfdl_CMIP6, esm = 'diff_8p5')
model_average_gfdl_CMIP6<-res_gfdl$model_average
model_sd_gfdl_CMIP6<-res_gfdl$model_sd
model_agreement_gfdl_CMIP6<- res_gfdl$model_agreement

res_all<-model_stat(c(data_ipsl_CMIP6, data_gfdl_CMIP6), esm = 'diff_8p5')
model_average_all_CMIP6<-res_all$model_average
model_sd_all_CMIP6<-res_all$model_sd
model_agreement_all_CMIP6<- res_all$model_agreement

# define title All
maptitle_average = paste("Mean % change RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 8.5, 1990s to 2090s CMIP6", sep=" ")
maptitle_agreement = paste("Agreement RCP 8.5, 1990s to 2090s CMIP6", sep=" ")

# Plot the model average and standard deviation

# NEED CONTOURS X 3 plots below bt average only

avarage_CMIP6_all<-plot_FISH_MIP(model_average_all_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP6_all<-plot_FISH_MIP(model_sd_all_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP6_all<-plot_FISH_MIP(model_agreement_all_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)") 

# plot averadge by esm 
avarage_CMIP6_ipsl<-plot_FISH_MIP(model_average_ipsl_CMIP6, "Mean % change RCP 8.5, 1990s to 2090s CMIP6 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP6_gfdl<-plot_FISH_MIP(model_average_gfdl_CMIP6, "Mean % change RCP 8.5, 1990s to 2090s CMIP6 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

# RCP 2.6 

data_ipsl_CMIP6$DBEM$diff_2p6 = data_ipsl_CMIP6$DBEM$diff_2p6[lons_to_use, lats_to_use] 
data_gfdl_CMIP6$DBEM$diff_2p6 = data_gfdl_CMIP6$DBEM$diff_2p6[lons_to_use, lats_to_use] 

# model average - see model_stat() in HelperScripts.R

res_ipsl_126<-model_stat(data_ipsl_CMIP6, esm = 'diff_2p6')
model_average_ipsl_CMIP6_126<-res_ipsl_126$model_average
model_sd_ipsl_CMIP6_126<-res_ipsl_126$model_sd
model_agreement_ipsl_CMIP6_126<- res_ipsl_126$model_agreement

res_gfdl_126<-model_stat(data_gfdl_CMIP6, esm = 'diff_2p6')
model_average_gfdl_CMIP6_126<-res_gfdl_126$model_average
model_sd_gfdl_CMIP6_126<-res_gfdl_126$model_sd
model_agreement_gfdl_CMIP6_126<- res_gfdl_126$model_agreement

# if you want the plot to be exactly as per Lotze (DBEM gfdl in agreemetn was not considered)
# data_gfdl_CMIP52$DBEM$diff_8p5<-NULL

res_all_126<-model_stat(c(data_ipsl_CMIP6, data_gfdl_CMIP6), esm = 'diff_2p6')
model_average_all_CMIP6_126<-res_all_126$model_average
model_sd_all_CMIP6_126<-res_all_126$model_sd
model_agreement_all_CMIP6_126<- res_all_126$model_agreement 

# define title All
maptitle_average = paste("Mean % change RCP 2.6, 1990s to 2090s CMIP6", sep=" ")
maptitle_sd = paste("Standard Deviation RCP 2.6, 1990s to 2090s CMIP6", sep=" ")
maptitle_agreement = paste("Agreement RCP 2.6, 1990s to 2090s CMIP6", sep=" ")

# Plot the model average and standard deviation

# NEED CONTOURS X 3 plots below bt average only - added an argument to below function contours = TRUE but this is not working yet... 

avarage_CMIP6_all_126<-plot_FISH_MIP(model_average_all_CMIP6, maptitle_average, mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
sd_CMIP6_all_126<-plot_FISH_MIP(model_sd_all_CMIP6, maptitle_sd, sd_plot_colour_values,colour_scheme = colour_scheme1, coltitle = "Variability  \n (SD)")
agreement_CMIP6_all_126<-plot_FISH_MIP(model_agreement_all_CMIP6, maptitle_agreement, model_agreement_plot_colour_values ,colour_scheme = colour_scheme1, coltitle = "Model \n agreement \n (%)")

# plot averadge by esm 
avarage_CMIP6_ipsl_126<-plot_FISH_MIP(model_average_ipsl_CMIP6, "Mean % change RCP 2.6, 1990s to 2090s CMIP6 IPSL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")
avarage_CMIP6_gfdl_126<-plot_FISH_MIP(model_average_gfdl_CMIP6, "Mean % change RCP 2.6, 1990s to 2090s CMIP6 GFDL", mean_plot_colour_values, colour_scheme = colour_scheme2, coltitle = "Biomass \n change \n (%)")

```

# save outputs ISIMIP3b temp 

```{r}

data_summaries_CMIP6<-list(res_all= res_all, res_ipsl = res_ipsl, res_gfdl = res_gfdl, res_all_126= res_all_126, res_ipsl_126 = res_ipsl_126, res_gfdl_126 = res_gfdl_126)

map_summaries_CMIP6<-list(avarage_CMIP6_all = avarage_CMIP6_all, sd_CMIP6_all = sd_CMIP6_all, agreement_CMIP6_all = agreement_CMIP6_all, avarage_CMIP6_ipsl = avarage_CMIP6_ipsl, avarage_CMIP6_gfdl = avarage_CMIP6_gfdl, avarage_CMIP6_all_126 = avarage_CMIP6_all_126, sd_CMIP6_all_126 = sd_CMIP6_all_126, agreement_CMIP6_all_126 = agreement_CMIP6_all_126, avarage_CMIP6_ipsl_126 = avarage_CMIP6_ipsl_126, avarage_CMIP6_gfdl_126 = avarage_CMIP6_gfdl_126)

# 2 datasets: 1 complete (ALL MODELS), and 1 reduced (LOTZE set + ZOOM) 
# save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, map_ipsl126_CMIP6, map_gfdl126_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6.RData")

save(data_ipsl_CMIP6, data_gfdl_CMIP6, map_ipsl585_CMIP6, map_gfdl585_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_reducedModelSet.RData")

```




# load data *can change folder for the 2 sets of models instead of all fig names* 

```{r}

rm(list=ls())
# 2 datasets: 1 complete (ALL MODELS), and 1 reduced (LOTZE set + ZOOM)  
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5.RData")
# load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6.RData")
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_reducedModelSet.RData")

# no apecosm option... 
# load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP5_noApecosm.RData")
# load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_noApecosm.RData")
# load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIP6_noApecosm_reducedModelSet.RData")

```

# Load libraries for netcdf and define variables

```{r load CMIP5}

library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/20210510/"

# variables 
cmip<-c("CMIP5", "CMIP6")
mod_ipsl <- c("APECOSM", "BOATS", "DBEM", "DBPM","EcoOcean", "MACROECOLOGICAL")
mod_gfdl <- c("BOATS", "DBEM", "EcoOcean", "MACROECOLOGICAL")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")
variable_to_extract <-c("tcb","tpb", "bp30cm", "bp30to90cm", "bp90cm")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values = c(0,10000) # these need to change for each model? 
delta_plot_colour_values = c(-50,50)
model_agreement_plot_colour_values = c(50,100)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c(low = "#fdb863", mid = "#f7f7f7", high = "#b2abd2") # for delta plots (between cmips change) # purple to green shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# Delta plot 

```{r}

# # SCTTER PLOT but better ones done below
# 
# # get lat and long from random file 
# # how do I know the latitude is the one I use above and not the reverse? 
# # image(data_summaries_CMIP5$res_ipsl$model_average)
# # image(data_ipsl_CMIP6$APECOSM$diff_8p5)
# # image(data_ipsl_CMIP6$APECOSM$diff_8p5[1:30, 1:30])  
# 
# # must be this: 
# longitude<-data_ipsl_CMIP6$APECOSM$hist$lon
# latitude<-data_ipsl_CMIP6$APECOSM$hist$lat
# 
# delta_average_limits = c(-100, 100)
# delta_sd_limits = c(0,100)
# 
# # calculate delta as scatter plot of CMIP5 vs CMIP6
# 
# delta_fun<-function(data5, data6, plot_limits = delta_limits, labels){
#   
#   # data5 = model_average_all_CMIP5
#   # data6 = model_average_all_CMIP6
#   
#   # transform in df with lat and long 
#   delta_CMIP5<-as.data.frame(data5) %>% 
#     `colnames<-`(latitude) %>% 
#     mutate(lon = longitude) %>% 
#     gather(lat, value_cmip5, -lon) 
# 
#   delta_CMIP6<-as.data.frame(data6) %>% 
#     `colnames<-`(latitude) %>% 
#     mutate(lon = longitude) %>% 
#     gather(lat, value_cmip6, -lon) 
# 
#   # combine 
#   delta<-delta_CMIP5 %>% 
#     full_join(delta_CMIP6) # %>% 
#     # mutate(color = ifelse(lat> 66.5 | lat < -66.5, "polar", ifelse(lat <23.5 & lat> -23.5, "tropic", "temperate"))) # but need to fix code to appropriately consider ranges - also could color by temperature? See Ryan?
#   
#   st<-summary(lm(delta$value_cmip6~delta$value_cmip5))
#   int = st$coefficients[1,1]
#   sl = st$coefficients[2,1]
#   rsqr = st$r.squared
#   
#   # plot 
#   delta_plot<-ggplot(delta, aes(x = value_cmip5, y = value_cmip6))+
#     geom_point(color = "grey70", alpha=0.5, shape = 16)+ # alpha=0.1
#     geom_abline()+
#     geom_vline(xintercept = 0, linetype = "dashed")+
#     geom_hline(yintercept = 0, linetype = "dashed")+
#     xlim(plot_limits)+
#     ylim(plot_limits)+
#     xlab(labels[1]) + 
#     ylab(labels[2]) + 
#     # geom_abline(intercept = int, slope = sl, color = "red")+ # this does not give exactly the same line... 
#     geom_smooth(method='lm', se = FALSE, formula= y~x)+
#     annotate("text", label = paste("r = ", rsqr), x = -75, y = 75)+
#     theme_bw()+
#     theme(text = element_text(size=18),
#           axis.title.y = element_text(vjust=0.4, size = 12),
#           axis.title.x = element_text(vjust=0.3, size = 12),
#           # axis.text.x = element_text(angle=90, hjust=0.5),
#           panel.grid.major = element_blank(), 
#           strip.background =element_rect(fill="white"),
#           legend.position = "none")
#   delta_plot
#   
#   return(delta_plot = delta_plot)
# }
# 
# ## RCP 8.5
# 
# delta_average_ipsl<-delta_fun(data_summaries_CMIP5$res_ipsl$model_average, data_summaries_CMIP6$res_ipsl$model_average, delta_average_limits, labels = c("Biomass mean % change IPSL RCP 8.5 CMIP5","Biomass mean % change IPSL RCP 8.5 CMIP6"))
# delta_sd_ipsl<-delta_fun(data_summaries_CMIP5$res_ipsl$model_sd, data_summaries_CMIP6$res_ipsl$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 8.5 CMIP5","Biomass SD IPSL RCP 8.5 CMIP6"))
# 
# delta_average_gfdl<-delta_fun(data_summaries_CMIP5$res_gfdl$model_average, data_summaries_CMIP6$res_gfdl$model_average, delta_average_limits, labels = c("Biomass mean % change GFDL RCP 8.5 CMIP5","Biomass mean % change GFDL RCP 8.5 CMIP6"))
# delta_sd_gfdl<-delta_fun(data_summaries_CMIP5$res_gfdl$model_sd, data_summaries_CMIP6$res_gfdl$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 8.5 CMIP5","Biomass SD IPSL RCP 8.5 CMIP6"))
# 
# delta_average_all<-delta_fun(data_summaries_CMIP5$res_all$model_average, data_summaries_CMIP6$res_all$model_average, delta_average_limits,labels = c("Biomass mean % change RCP 8.5 CMIP5","Biomass mean % change RCP 8.5 CMIP6"))
# delta_sd_all<-delta_fun(data_summaries_CMIP5$res_all$model_sd, data_summaries_CMIP6$res_all$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 8.5 CMIP5","Biomass SD IPSL RCP 8.5 CMIP6"))

# DELTA MAP 
# option 1 - subtract (julia) - OK
delta_map_data_all<-data_summaries_CMIP6$res_all$model_average - data_summaries_CMIP5$res_all$model_average
maptitle_detla<-"Delta (CMIP6 change - CMIP5 change)"

# NEED CONTOURS X 3 plots below 

delta_map_all_difference<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 
# if (+1) - (+5) = -4 # CMIP6 decreased 4 times
# if (+1) - (-5) = 6 # CMIP6 increased 6 times 
# if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
# if (-1) - (-5) = 4 # CMIP6 increased 4 times 
# e.g. 
# model_average_all_CMIP5 = -5 (tcb 5% decrease between 1990 and 2090) # where model_average_all_CMIP5 is the mean of diff_8p5 (diff in tcb between the 2 decades) across all models
# model_average_all_CMIP6 = -3 (tcb 3% decrease between 1990 and 2090)
# -3 - -5 = 2 CMIP6 decreased less than CMIP5 by 2 - i.e. positive values indicate that tcb in CMIP6 increased more or decreased less between 1990 and 2090 than tcb in CMIP5 for the same period.  

delta_map_data_ipsl<-data_summaries_CMIP6$res_ipsl$model_average - data_summaries_CMIP5$res_ipsl$model_average
maptitle_detla<-"Delta IPSL (CMIP6 change - CMIP5 change)"
delta_map_ipsl_difference<-plot_FISH_MIP(delta_map_data_ipsl, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_gfdl<-data_summaries_CMIP6$res_gfdl$model_average - data_summaries_CMIP5$res_gfdl$model_average
maptitle_detla<-"Delta GFDL (CMIP6 change - CMIP5 change)"
delta_map_gfdl_difference<-plot_FISH_MIP(delta_map_data_gfdl, maptitle_detla, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

# # option 2 divide (Derek but in another contest as here we have negative values so we use the below)
# delta_map_data_all<-(model_average_all_CMIP6 / model_average_all_CMIP5) * 100 - 100
# maptitle_detla<-"Delta ((CMIP6 change / CMIP5 change)*100)"
# delta_map_all_divide<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-100, 100), colour_scheme = c("#fdb863", "#f7f7f7","#b2abd2"), coltitle = "Difference \nin \nchange \n", legend_ticks = 3)
# # if 1/5*100 - 100 = -80% # CMIP6 decreased
# # if 1/-5*100 - 100 = -120% # CMIP6 decreased - WRONG

# option 3 percentage - same as Julia above if you do abs() but less meaningful as inputs are already % 
# TO DO - DELETE
# delta_map_data_all<-((model_average_all_CMIP6 - model_average_all_CMIP5)/abs(model_average_all_CMIP5)) * 100
# maptitle_detla<-"Delta (((CMIP6 change - CMIP5 change)/|CMIP5 change|) * 100)"
# delta_map_all_percentage<-plot_FISH_MIP(delta_map_data_all, maptitle_detla, c(-100, 100), colour_scheme = c("#fdb863", "#f7f7f7","#b2abd2"), coltitle = "(%) Difference \nin \nchange \n", legend_ticks = 5)
# if ((1 - 5)/5)*100 = -80 # CMIP6 decreased 4 times
# if ((1 - -5)/5)*100 = 120 # CMIP6 increased 6 times 
# if ((-1 - 5)/-5)*100 = 120 # WRONG
# if ((-1 - -5)/-5)*100 = -80 # WRONG
# if ((-1 - 5)/5)*100 = -120 # CMIP6 decrease 6 times - ok if denominator is absolute
# if ((-1 - -5)/5)*100 = 80 # CMIP increase 4 times - ok if denominator is absolute

# # agreement on the direction of change between CMIPs see model_stat. this gives 100%  agreement if biomass in both cmips is decreasing/increasing and 50% is they disagree... (agreement on the direction of change....but  does not tell you which direction.)
# # create array with both matrices 
# # TO DO - weight according to degree of change or used delta as an alpha factor - not particularly usefull... I decided not to do
# trial<-array(NA, dim=c(dim(data_summaries_CMIP5$res_all$model_average)[1],dim(data_summaries_CMIP5$res_all$model_average)[2],2))
# trial[,,1]<-data_summaries_CMIP5$res_all$model_average
# trial[,,2]<-data_summaries_CMIP6$res_all$model_average
# # apply model_stat code to calculate agreement in biomass changes between cmips
# temp<-apply(trial, c(1,2), function(x) length(x[which(x>0)])) 
# temp2<-apply(trial, c(1,2), function(x) length(x[which(!is.na(x))])) #
# temp4<-temp/temp2
# trial_data<-ifelse(is.na(temp4), NA, ifelse(temp4>0.5, temp4*100, (1-temp4)*100))
# trial_data[which(trial_data ==100)]<-1
# trial_data[which(trial_data ==50)]<-0
# delta_map_all_agreement<-plot_FISH_MIP(trial_data, "CMIPs agreement on the direction of change", c(0,1) ,colour_scheme = colour_scheme3, coltitle = "CMIPs \nagreement", legend_ticks = 2) 

# # model's discrepancy from average (withing the CMIP6) 
# # can do with either IPSL or GFDL but not with ALL as you don't have a mean of the 2 for each model 
# delta_average_boats<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$BOATS$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_dbmp<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$DBPM$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_macroecological<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$MACROECOLOGICAL$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_feisty<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$FEISTY$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_zoomss<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$ZooMSS$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_ecotroph<-delta_fun(model_average_ipsl_CMIP6, data_ipsl_CMIP6$EcoTroph$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# 
# # model's discrepancy from average (withing the CMIP5) 
# delta_average_boats_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$BOATS$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_dbmp_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$DBPM$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_macroecological_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$MACROECOLOGICAL$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_apecosm_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$APECOSM$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))
# delta_average_ecoocean_cmip5<-delta_fun(model_average_ipsl_CMIP5, data_ipsl_CMIP5$EcoOcean$diff_8p5, delta_average_limits, labels = c("Biomass mean % change","Biomass model % change"))

## RCP 2.6

# # SCTTER PLOTS 
# 
# delta_average_ipsl_126<-delta_fun(data_summaries_CMIP5$res_ipsl_126$model_average, data_summaries_CMIP6$res_ipsl_126$model_average, delta_average_limits, labels = c("Biomass mean % change IPSL RCP 2.6 CMIP5","Biomass mean % change IPSL RCP 2.6 CMIP6"))
# delta_sd_ipsl_126<-delta_fun(data_summaries_CMIP5$res_ipsl_126$model_sd, data_summaries_CMIP6$res_ipsl_126$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 2.6 CMIP5","Biomass SD IPSL RCP 2.6 CMIP6"))
# 
# delta_average_gfdl_126<-delta_fun(data_summaries_CMIP5$res_gfdl_126$model_average, data_summaries_CMIP6$res_gfdl_126$model_average, delta_average_limits, labels = c("Biomass mean % change GFDL RCP 2.6 CMIP5","Biomass mean % change GFDL RCP 2.6 CMIP6"))
# delta_sd_gfdl_126<-delta_fun(data_summaries_CMIP5$res_gfdl_126$model_sd, data_summaries_CMIP6$res_gfdl_126$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 2.6 CMIP5","Biomass SD IPSL RCP 2.6 CMIP6"))
# 
# delta_average_all_126<-delta_fun(data_summaries_CMIP5$res_all_126$model_average, data_summaries_CMIP6$res_all_126$model_average, delta_average_limits,labels = c("Biomass mean % change RCP 2.6 CMIP5","Biomass mean % change RCP 2.6 CMIP6"))
# delta_sd_all_126<-delta_fun(data_summaries_CMIP5$res_all_126$model_sd, data_summaries_CMIP6$res_all_126$model_sd, delta_sd_limits, labels = c("Biomass SD IPSL RCP 2.6 CMIP5","Biomass SD IPSL RCP 2.6 CMIP6"))

# DELTA MAPS 
# option 1 - subtract (julia) - OK
delta_map_data_all_126<-data_summaries_CMIP6$res_all_126$model_average - data_summaries_CMIP5$res_all_126$model_average
maptitle_detla_126<-"Delta (CMIP6 change - CMIP5 change) RCP 2.6"

# NEED CONTOURS X 3 plots below 

delta_map_all_difference_126<-plot_FISH_MIP(delta_map_data_all_126, maptitle_detla_126, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_ipsl_126<-data_summaries_CMIP6$res_ipsl_126$model_average - data_summaries_CMIP5$res_ipsl_126$model_average
maptitle_detla<-"Delta IPSL (CMIP6 change - CMIP5 change) RCP 2.6"
delta_map_ipsl_difference_126<-plot_FISH_MIP(delta_map_data_ipsl_126, maptitle_detla_126, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

delta_map_data_gfdl_126<-data_summaries_CMIP6$res_gfdl_126$model_average - data_summaries_CMIP5$res_gfdl_126$model_average
maptitle_detla<-"Delta GFDL (CMIP6 change - CMIP5 change) RCP 2.6"
delta_map_gfdl_difference_126<-plot_FISH_MIP(delta_map_data_gfdl_126, maptitle_detla_126, c(-50, 50), colour_scheme = colour_scheme3, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 5) 

```

# flip sign plot 

Similar but more sophisticated than agreement

```{r}

# highlights cells that have switched sign from CMIP5 to CMIP6

flip_sign<-function(temp, temp1){
  
  # find cells where the sign is opposite
  temp2<-temp*temp1 
  temp2<-ifelse(temp2<0, 1, 0) # if negative, sign flipped

  # consider only flipped sign in CMIP5 and CMIP6 matrices
  temp<-temp*temp2
  temp<-ifelse(temp==0, NA, temp)
  temp1<-temp1*temp2
  temp1<-ifelse(temp1==0, NA, temp1)
  # check
  # temp[1:10,1:10]
  # temp1[1:10,1:10]

  # from + to -
  # consider only cells that flipped from + (in cmip5) to - (in cmip6)
  temp_neg<-temp
  temp1_neg<-temp1
  temp_neg<-ifelse(temp_neg<0, NA, temp_neg) # SHOULD THESE BE >= 0 ??? 0 to positive or 0 to negative does not qualify as changing sign I think
  temp1_neg<-ifelse(temp1_neg>0, NA, temp1_neg)

  # by how much? # calcualte delta as above 
  data_negative<-temp1_neg - temp_neg # CMIP6 -CMIP5
  # if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
  # if (-5) - (+1) = -6 # CMIP6 decreased 6 times 
  # check 
  # temp[1,153] # positive 
  # temp1[1,153] # negative
  # trial[1,153]
  
  # from - to +
  # consider only cells that flipped from + (in cmip5) to - (in cmip6)
  temp_pos<-temp
  temp1_pos<-temp1
  temp_pos<-ifelse(temp_pos>0, NA, temp_pos)
  temp1_pos<-ifelse(temp1_pos<0, NA, temp1_pos)

  # by how much? # calcualte delta as above 
  data_positive<-temp1_pos - temp_pos # CMIP6 -CMIP5
  # if (-1) - (+5) = -6 # CMIP6 decreased 6 times 
  # if (-5) - (+1) = -6 # CMIP6 decreased 6 times 
  # check 
  # temp[1,153] # positive 
  # temp1[1,153] # negative
  # trial[1,153]

  return(list(data_negative = data_negative, data_positive = data_positive))
}

flip_sign_data<-flip_sign(data_summaries_CMIP5$res_all$model_average, data_summaries_CMIP6$res_all$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data$data_negative))
c<-sum(!is.na(flip_sign_data$data_positive))
(b/a)*100 # turned negative 
(c/a)*100 # turned positive

# plot
colour_scheme4 <- c(low = "#fc9617", mid = "#fecf95",  high = "#fef4e7")
maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in CMIP6"
map_sign_negative<-plot_FISH_MIP(flip_sign_data$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

colour_scheme5 <- c(low = "#f4f3f9", mid = "#bab4d7",  high = "#8479b7") 
maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in CMIP6"
map_sign_positive<-plot_FISH_MIP(flip_sign_data$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

# by esm now 
flip_sign_data_ipsl<-flip_sign(data_summaries_CMIP5$res_ipsl$model_average, data_summaries_CMIP6$res_ipsl$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data_ipsl$data_negative))
c<-sum(!is.na(flip_sign_data_ipsl$data_positive))
(b/a)*100
(c/a)*100

maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in IPSL CMIP6"
map_sign_negative_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in IPSL CMIP6"
map_sign_positive_ipsl<-plot_FISH_MIP(flip_sign_data_ipsl$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

flip_sign_data_gfdl<-flip_sign(data_summaries_CMIP5$res_gfdl$model_average, data_summaries_CMIP6$res_gfdl$model_average)

# % of cell that change
a<-sum(!is.na(data_summaries_CMIP5$res_all$model_average))
b<-sum(!is.na(flip_sign_data_gfdl$data_negative))
c<-sum(!is.na(flip_sign_data_gfdl$data_positive))
(b/a)*100
(c/a)*100

maptitle_sign_negative<-"Delta for cells that changed from an increase in CMIP5 to a decrease in GFDL CMIP6"
map_sign_negative_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

maptitle_sign_positive<-"Delta for cells that changed from a decrease in CMIP5 to an increase in GFDL CMIP6"
map_sign_positive_gfdl<-plot_FISH_MIP(flip_sign_data_gfdl$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

## RCP 2.6

flip_sign_data_126<-flip_sign(data_summaries_CMIP5$res_all_126$model_average, data_summaries_CMIP6$res_all_126$model_average)

# plot
colour_scheme4 <- c(low = "#fc9617", mid = "#fecf95",  high = "#fef4e7")
map_sign_negative_126<-plot_FISH_MIP(flip_sign_data_126$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

colour_scheme5 <- c(low = "#f4f3f9", mid = "#bab4d7",  high = "#8479b7") 
map_sign_positive_126<-plot_FISH_MIP(flip_sign_data_126$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

# by esm now 
flip_sign_data_ipsl_126<-flip_sign(data_summaries_CMIP5$res_ipsl_126$model_average, data_summaries_CMIP6$res_ipsl_126$model_average)

map_sign_negative_ipsl_126<-plot_FISH_MIP(flip_sign_data_ipsl_126$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

map_sign_positive_ipsl_126<-plot_FISH_MIP(flip_sign_data_ipsl_126$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

flip_sign_data_gfdl_126<-flip_sign(data_summaries_CMIP5$res_gfdl_126$model_average, data_summaries_CMIP6$res_gfdl_126$model_average)

map_sign_negative_gfdl_126<-plot_FISH_MIP(flip_sign_data_gfdl_126$data_negative, maptitle_sign_negative, c(-50, 0), colour_scheme = colour_scheme4, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3) 

map_sign_positive_gfdl_126<-plot_FISH_MIP(flip_sign_data_gfdl_126$data_positive, maptitle_sign_positive, c(0, 50), colour_scheme = colour_scheme5, coltitle = "Difference \nin (%) \nchange \n", legend_ticks = 3)

```

# save plot data that you have not saved yet 

```{r}

# delta plots and flipped signed figures data 
# save(flip_sign_data,flip_sign_data_ipsl,flip_sign_data_gfdl, flip_sign_data_126,flip_sign_data_ipsl_126,flip_sign_data_gfdl_126, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIPs_deltaFigures.RData")

save(flip_sign_data,flip_sign_data_ipsl,flip_sign_data_gfdl,flip_sign_data_126,flip_sign_data_ipsl_126,flip_sign_data_gfdl_126, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIPs_deltaFigures_reducedModelSet.RData")

# # load these data 
# load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIPs_deltaFigures.RData")
# load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_CMIPs_deltaFigures_reducedModelSet.RData")

```

# Put all maps together

```{r multipanel plot}

library(patchwork)

# CMIP5 esm: IPSL-CM5A-LR and GFDL-ESM2M 
# CMIP6 esm: IPSL-CM6A-LR and GFDL-ESM4
# 
# CMIP5 scenario: RCP2.6 AND RCP8.5 
# CMIP6 scenario: SSP1-2.6 and SSP5-8.5

# model average CMIP5, model average CMIP6, delta CMIP5 vs CMIP6
layout <- "
AB
C#
DE
"

a <- map_summaries_CMIP5$avarage_CMIP5_all + ggtitle("a) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b <- map_summaries_CMIP6$avarage_CMIP6_all + ggtitle("b) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c <- delta_map_all_difference + ggtitle("c) Change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d <- map_sign_positive + ggtitle("d) Shift to positive change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- map_sign_negative + ggtitle("e) Shift to negative change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a + b + c + d + e + plot_layout(design = layout)

# # pdf(paste0(save_loc,"Fig2_new_noApecosm.pdf"), height=10, width=15) # old name
# pdf(paste0(save_loc,"FigS5.pdf"), height=10, width=15) # CONSIDER ALL MODELS
# pt
# dev.off()

pdf(paste0(save_loc,"Fig5.pdf"), height=10, width=15) # CONSIDER LOTZE SET + ZOOM
pt
dev.off()

#### 2.6 scenario

a126 <- map_summaries_CMIP5$avarage_CMIP5_all_126 + ggtitle("a) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b126 <- map_summaries_CMIP6$avarage_CMIP6_all_126 + ggtitle("b) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c126 <- delta_map_all_difference_126 + ggtitle("c) Change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d126 <- map_sign_positive_126 + ggtitle("d) Shift to positive change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e126 <- map_sign_negative_126 + ggtitle("e) Shift to negative change") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a126 + b126 + c126 + d126 + e126 + plot_layout(design = layout)

# # pdf(paste0(save_loc,"Fig2_new_noApecosm.pdf"), height=10, width=15) # old name
# pdf(paste0(save_loc,"FigS5_126.pdf"), height=10, width=15) # CONSIDER ALL MODELS
# pt
# dev.off()

pdf(paste0(save_loc,"Fig5_126.pdf"), height=10, width=15) # CONSIDER LOTZE SET + ZOOM
pt
dev.off()

## ALL MODELS? this is fig S6 and S10 but there are 2 options for each here 

# model average CMIP5, model average CMIP6, delta CMIP5 vs CMIP6 by ESM 
layout <- "
AB
CD
EF
GH
IJ
"

a2 <- map_summaries_CMIP5$avarage_CMIP5_ipsl + ggtitle("a) CMIP5 IPSL-CM5A-LR RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b2 <- map_summaries_CMIP6$avarage_CMIP6_ipsl + ggtitle("b) CMIP6 IPSL-CM6A-LR SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c <- map_summaries_CMIP5$avarage_CMIP5_gfdl + ggtitle("c) CMIP5 GFDL-ESM2M RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d <- map_summaries_CMIP6$avarage_CMIP6_gfdl + ggtitle("d) CMIP6 GFDL-ESM4 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- delta_map_ipsl_difference + ggtitle("e) Change between CMIPs IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- delta_map_gfdl_difference + ggtitle("f) Change between CMIPs GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_sign_positive_ipsl + ggtitle("g) Shift to positive change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_sign_negative_ipsl + ggtitle("h) Shift to negative change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_sign_positive_gfdl + ggtitle("i) Shift to positive change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_sign_negative_gfdl + ggtitle("j) Shift to negative change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a2 + b2 + 
  c + d +
  e + f +
  g + h + 
  i + l + 
  plot_layout(design = layout)

# # pdf(paste0(save_loc,"Fig2_noApecosm_ipsl_gfdl.pdf"), height=20, width=15) # old name
# pdf(paste0(save_loc,"FigS6.pdf"), height=20, width=15)
# pt
# dev.off()

pdf(paste0(save_loc,"FigS6_subset.pdf"), height=20, width=15)
pt
dev.off()

#### 2.6 scenario

a2126 <- map_summaries_CMIP5$avarage_CMIP5_ipsl_126 + ggtitle("a) CMIP5 IPSL-CM5A-LR RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b2126 <- map_summaries_CMIP6$avarage_CMIP6_ipsl_126 + ggtitle("b) CMIP6 IPSL-CM6A-LR SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c126 <- map_summaries_CMIP5$avarage_CMIP5_gfdl_126 + ggtitle("c) CMIP5 GFDL-ESM2M RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d126 <- map_summaries_CMIP6$avarage_CMIP6_gfdl_126 + ggtitle("d) CMIP6 GFDL-ESM4 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e126 <- delta_map_ipsl_difference_126 + ggtitle("e) Change between CMIPs IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f126 <- delta_map_gfdl_difference_126 + ggtitle("f) Change between CMIPs GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g126 <- map_sign_positive_ipsl_126 + ggtitle("g) Shift to positive change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h126 <- map_sign_negative_ipsl_126 + ggtitle("h) Shift to negative change IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i126 <- map_sign_positive_gfdl_126 + ggtitle("i) Shift to positive change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l126 <- map_sign_negative_gfdl_126 + ggtitle("j) Shift to negative change GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a2126 + b2126 + 
  c126 + d126 +
  e126 + f126 +
  g126 + h126 + 
  i126 + l126 + 
  plot_layout(design = layout)

# # pdf(paste0(save_loc,"Fig2_noApecosm_ipsl_gfdl.pdf"), height=20, width=15) # old name
# pdf(paste0(save_loc,"FigS6_126.pdf"), height=20, width=15)
# pt
# dev.off()

pdf(paste0(save_loc,"FigS6_subset_126.pdf"), height=20, width=15)
pt
dev.off()

# All protocols models summaries (average, sd and agreement) 
# can  be done with GFDL or IPSL too 
# can be done with spp126 if 'diff_8p5' line 318 is changed too  

layout <- "
AB
CD
EF
"

c<-map_summaries_CMIP5$sd_CMIP5_all +  ggtitle("c) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_summaries_CMIP6$sd_CMIP6_all +  ggtitle("d) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e<-map_summaries_CMIP5$agreement_CMIP5_all + ggtitle("e) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_summaries_CMIP6$agreement_CMIP6_all + ggtitle("f) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a + b + # this is same as Fig2 first raw
    c + d +  
    e + f +  
    plot_layout(design = layout)

# pt<-pt + plot_annotation(
#   title = 'Spatial patterns of projected biomass changes RCP8.5 CMIP5 vs CMIP6, 1990s to 2090s
#   ',
#   theme = theme(plot.title = element_text(size = 20)))

# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# # pdf(paste0(save_loc,"FigS2_noApecosm.pdf"), height=10, width=15) # old name 
# pdf(paste0(save_loc,"FigS10.pdf"), height=10, width=15)
# pt
# dev.off()

pdf(paste0(save_loc,"FigS10_subset.pdf"), height=10, width=15)
pt
dev.off()

#### 2.6 scenario

c126<-map_summaries_CMIP5$sd_CMIP5_all_126 +  ggtitle("c) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d126<-map_summaries_CMIP6$sd_CMIP6_all_126 +  ggtitle("d) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e126<-map_summaries_CMIP5$agreement_CMIP5_all_126 + ggtitle("e) CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f126<-map_summaries_CMIP6$agreement_CMIP6_all_126 + ggtitle("f) CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a126 + b126 + # this is same as Fig2 first raw
    c126 + d126 +  
    e126 + f126 +  
    plot_layout(design = layout)

# pdf(paste0(save_loc,"FigS10_126.pdf"), height=10, width=15)
# pt
# dev.off()

pdf(paste0(save_loc,"FigS10_subset_126.pdf"), height=10, width=15)
pt
dev.off()

```

# all models outputs *when ALL MODELS*

```{r}
# all models map of change IPSL spp585 CMIP5 vs CMIP6
# rearranged in alphabetical order as per trends ... 

layout <- "
AB 
CD
EF
GH
IJ
#K
LM
#N
OP
"

a<-map_ipsl585_CMIP5$APECOSM +  ggtitle("a) APECOSM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_ipsl585_CMIP6$APECOSM +  ggtitle("b) APECOSM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_ipsl585_CMIP5$BOATS +  ggtitle("c) BOATS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_ipsl585_CMIP6$BOATS +  ggtitle("d) BOATS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e<-map_ipsl585_CMIP5$DBEM + ggtitle("e) DBEM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_ipsl585_CMIP6$DBEM + ggtitle("f) DBEM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_ipsl585_CMIP5$DBPM + ggtitle("g) DBPM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_ipsl585_CMIP6$DBPM + ggtitle("h) DBPM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_ipsl585_CMIP5$EcoOcean + ggtitle("i) EcoOcean CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_ipsl585_CMIP6$EcoOcean + ggtitle("j) EcoOcean CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k <- map_ipsl585_CMIP6$EcoTroph + ggtitle("k) EcoTroph CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_ipsl585_CMIP5$MACROECOLOGICAL + ggtitle("l) MACROECOLOGICAL CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
m <- map_ipsl585_CMIP6$MACROECOLOGICAL + ggtitle("m) MACROECOLOGICAL CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
n <- map_ipsl585_CMIP6$FEISTY  + ggtitle("n) FEISTY CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
o<- map_ipsl585_CMIP5$ZooMSS +ggtitle("o) ZooMSS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
p <- map_ipsl585_CMIP6$ZooMSS  +ggtitle("p) ZooMSS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a + b + 
  c + d + 
  e + f + 
  g + h + 
  i + j + 
  k + 
  l + m + 
  n + 
  o + p + 
  plot_layout(design = layout)
    
# try the smallest option possible.... 
jpeg(paste0(save_loc,"FigS8.jpeg"), height=40, width=30, units ='in', res=300)
pt 
dev.off()

#### 2.6 scenario 

a<-map_ipsl126_CMIP5$APECOSM +  ggtitle("a) APECOSM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_ipsl126_CMIP6$APECOSM +  ggtitle("b) APECOSM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_ipsl126_CMIP5$BOATS +  ggtitle("c) BOATS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_ipsl126_CMIP6$BOATS +  ggtitle("d) BOATS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e<-map_ipsl126_CMIP5$DBEM + ggtitle("e) DBEM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_ipsl126_CMIP6$DBEM + ggtitle("f) DBEM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_ipsl126_CMIP5$DBPM + ggtitle("g) DBPM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_ipsl126_CMIP6$DBPM + ggtitle("h) DBPM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_ipsl126_CMIP5$EcoOcean + ggtitle("i) EcoOcean CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_ipsl126_CMIP6$EcoOcean + ggtitle("j) EcoOcean CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k <- map_ipsl126_CMIP6$EcoTroph + ggtitle("k) EcoTroph CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_ipsl126_CMIP5$MACROECOLOGICAL + ggtitle("l) MACROECOLOGICAL CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
m <- map_ipsl126_CMIP6$MACROECOLOGICAL + ggtitle("m) MACROECOLOGICAL CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
n <- map_ipsl126_CMIP6$FEISTY  + ggtitle("n) FEISTY CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
o<- map_ipsl126_CMIP5$ZooMSS +ggtitle("o) ZooMSS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
p <- map_ipsl126_CMIP6$ZooMSS  +ggtitle("p) ZooMSS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a + b + 
  c + d + 
  e + f + 
  g + h + 
  i + j + 
  k + 
  l + m + 
  n + 
  o + p + 
  plot_layout(design = layout)
    
# try the smallest option possible.... 
jpeg(paste0(save_loc,"FigS8_126.jpeg"), height=40, width=30, units ='in', res=300)
pt 
dev.off()

# all models map of change GFDL spp585 CMIP5 vs CMIP6
layout <- "
AB 
CD
EF
#G
HI
#J
KL
"

a<-map_gfdl585_CMIP5$BOATS +  ggtitle("a) BOATS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_gfdl585_CMIP6$BOATS +  ggtitle("b) BOATS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_gfdl585_CMIP5$DBEM + ggtitle("c) DBEM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_gfdl585_CMIP6$DBEM + ggtitle("d) DBEM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
# g <- map_gfdl585_CMIP5$DBPM + ggtitle("E) DBPM CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
# h <- map_gfdl585_CMIP6$DBPM + ggtitle("F) DBPM CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- map_gfdl585_CMIP5$EcoOcean + ggtitle("e) EcoOcean CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- map_gfdl585_CMIP6$EcoOcean + ggtitle("f) EcoOcean CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_gfdl585_CMIP6$EcoTroph + ggtitle("g) EcoTroph CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_gfdl585_CMIP5$MACROECOLOGICAL + ggtitle("h) MACROECOLOGICAL CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_gfdl585_CMIP6$MACROECOLOGICAL + ggtitle("i) MACROECOLOGICAL CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_gfdl585_CMIP6$FEISTY  + ggtitle("j) FEISTY CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k<- map_gfdl585_CMIP5$ZooMSS +ggtitle("k) ZooMSS CMIP5 RCP8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_gfdl585_CMIP6$ZooMSS  +ggtitle("l) ZooMSS CMIP6 SSP5-8.5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a+ b + # IJ
  c + d + # EF
  # g + h + # AB
  e + f + # GH
  g + # #N
  h + i +# CD
  j+ # #M
  k+ l + # KL
  plot_layout(design = layout)

jpeg(paste0(save_loc,"FigS7.jpeg"), height=35, width=30, units ='in', res=300)
pt
dev.off()

####  2.6 scenario

a<-map_gfdl126_CMIP5$BOATS +  ggtitle("a) BOATS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_gfdl126_CMIP6$BOATS +  ggtitle("b) BOATS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_gfdl126_CMIP5$DBEM + ggtitle("c) DBEM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_gfdl126_CMIP6$DBEM + ggtitle("d) DBEM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
# g <- map_gfdl126_CMIP5$DBPM + ggtitle("E) DBPM CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
# h <- map_gfdl126_CMIP6$DBPM + ggtitle("F) DBPM CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
e <- map_gfdl126_CMIP5$EcoOcean + ggtitle("e) EcoOcean CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f <- map_gfdl126_CMIP6$EcoOcean + ggtitle("f) EcoOcean CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g <- map_gfdl126_CMIP6$EcoTroph + ggtitle("g) EcoTroph CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
h <- map_gfdl126_CMIP5$MACROECOLOGICAL + ggtitle("h) MACROECOLOGICAL CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i <- map_gfdl126_CMIP6$MACROECOLOGICAL + ggtitle("i) MACROECOLOGICAL CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
j <- map_gfdl126_CMIP6$FEISTY  + ggtitle("j) FEISTY CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
k<- map_gfdl126_CMIP5$ZooMSS +ggtitle("k) ZooMSS CMIP5 RCP2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l <- map_gfdl126_CMIP6$ZooMSS  +ggtitle("l) ZooMSS CMIP6 SSP5-2.6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-
  a+ b + # IJ
  c + d + # EF
  # g + h + # AB
  e + f + # GH
  g + # #N
  h + i +# CD
  j+ # #M
  k+ l + # KL
  plot_layout(design = layout)

jpeg(paste0(save_loc,"FigS7_126.jpeg"), height=35, width=30, units ='in', res=300)
pt
dev.off()

# # Delta mean over all models and all earth inputs  
# layout <- "
# A
# B
# C
# "
# 
# # delta_average_ipsl<-delta_average_ipsl + ggtitle("IPSL") + theme(plot.title = element_text(size = 12, face = "bold"))
# # delta_average_gfdl<-delta_average_gfdl + ggtitle("GFDL") + theme(plot.title = element_text(size = 12, face = "bold"))
# # delta_average_all<-delta_average_all + ggtitle("ALL") + theme(plot.title = element_text(size = 12, face = "bold"))
# 
# pt<-delta_average_ipsl + delta_average_gfdl + delta_average_all +
#     plot_layout(design = layout)
# 
# pt<-pt + plot_annotation(
#   title = 'Delta average RCP 8.5',
#   theme = theme(plot.title = element_text(size = 20)))

# pdf(paste0(save_loc,"delta_scatterplot.pdf"), height=12, width=8)
# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# pt 
# dev.off()

# # only all instead - can also be colored by lat?
# pdf(paste0(save_loc,"delta_scatterplot.pdf"), height=12, width=8)
# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# delta_average_all 
# dev.off()

```

# scatter plot *when ALL MODELS*

```{r}

# pick lat and log - see scatter plot above, here done slightly differently
latitude<-data_ipsl_CMIP5$APECOSM$hist$lat 
longitude<-data_ipsl_CMIP5$APECOSM$hist$lon

data<-list(data_ipsl_CMIP5= data_ipsl_CMIP5, data_ipsl_CMIP6 = data_ipsl_CMIP6, data_gfdl_CMIP5 = data_gfdl_CMIP5, data_gfdl_CMIP6 = data_gfdl_CMIP6)

new_data<-list()

for(i in 1:length(data)){
  
  # i =1
  x<- lapply(data[[i]], `[[`, "diff_8p5")
  x<- lapply(x, "colnames<-", latitude)
  x<- lapply(x, "rownames<-", longitude)
  
  # from trens code
  x<-do.call(rbind, lapply(x, as.data.frame)) 
  
  x<-x %>% 
    mutate(model = gsub("[^a-zA-Z]", "", rownames(x)), 
           long = rep(longitude, length(data[[i]])), 
           # long2 = sub(".*\\.", "", rownames(x)),
           cmip = 5, 
           earth = "ipsl") %>% 
    gather("lat", "tcb", -c(model, long, cmip, earth))
  
  if(names(data)[i] == "data_ipsl_CMIP5"){
    x$cmip = 5
    x$earth = "ipsl"
  }else if(names(data)[i] == "data_ipsl_CMIP6"){
    x$cmip = 6
    x$earth = "ipsl"
  }else if(names(data)[i] == "data_gfdl_CMIP5"){
    x$cmip = 5
    x$earth = "gfdl"
  }else{
    x$cmip = 6
    x$earth = "gfdl"
  }
  
  new_data[[i]]<-x
  names(new_data)[i]<-names(data)[i]
  
}

# you don't need to fix ecocean as in tcb trends because here you already considered 2 decades 1990s and 2090s 

# add all together 
all_ipsl<-new_data$data_ipsl_CMIP5 %>% 
  full_join(new_data$data_ipsl_CMIP6) %>% 
  spread(cmip, tcb) %>% 
  `colnames<-`(c("model", "long", "earth","lat", "cmip5", "cmip6")) 

# max and min values of change for each cmip 
# LOTS OF PROBLEMS WITH DBEM... 

# 1. inf values (from where?)
trial<-filter(all_ipsl, model == "DBEM")
trial<-trial %>% mutate(cmip5 = ifelse(is.infinite(cmip5), NA, cmip5),
                        cmip6 = ifelse(is.infinite(cmip6), NA, cmip6))

nrow(trial) # 61616

# 2. even without inf values, huge range of changes 
max(trial$cmip5, na.rm = TRUE)
min(trial$cmip5, na.rm = TRUE)
max(trial$cmip6, na.rm = TRUE)
min(trial$cmip6, na.rm = TRUE)

# 3. some cells did not run in cmip5 but they did in cmip6 and vice versa, this is true for other models too 
trial<-trial %>% 
  mutate(id = ifelse(is.na(cmip5) & !is.na(cmip6), "remove", 
                    ifelse(is.na(cmip6) & !is.na(cmip5), "remove", "keep")),
         lat = as.numeric(lat)) %>% 
  filter(id == "keep")

nrow(trial) #60421
# plots remove 23462 s0 on plots are 36959 grid cells 

# 4. there seems to be a cut at -100% of change. 
# problem with inf values .... 
ggplot(trial, aes(color = lat, x=cmip5, y = cmip6))+
  geom_point(alpha = 0.2)+
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  scale_y_continuous(name = "Change in biomass (%) CMIP6", limits = c(-200, 200))+
  scale_x_continuous(name = "Change in biomass (%) CMIP5", limits = c(-200, 200))

# other models .... 

mod = "ZooMSS"

trial<-filter(all_ipsl, model == mod)
max(trial$cmip5, na.rm = TRUE)
min(trial$cmip5, na.rm = TRUE)
max(trial$cmip6, na.rm = TRUE)
min(trial$cmip6, na.rm = TRUE)

# OTHER PROBLEMS - some cells have NA values for CMIP5 and not for CMIP6 adn vice versa... 
# trial[which(trial$cmip6 > 100),] 

a<-filter(trial, is.na(cmip6), !is.na(cmip5))
nrow(a)
a<-filter(trial, is.na(cmip5), !is.na(cmip6))
nrow(a)

all_ipsl<-all_ipsl %>% 
  mutate(id = ifelse(is.na(cmip5) & !is.na(cmip6), "remove", 
                    ifelse(is.na(cmip6) & !is.na(cmip5), "remove", "keep")),
         lat = as.numeric(lat)) %>% 
  filter(id == "keep")

all_ipsl2<-all_ipsl%>% 
  filter(!model %in% c("FEISTY", "EcoTroph")) # they don't have a CMIP5 counterpart... 

# scatter plot
a<-ggplot(all_ipsl2, aes(color = lat, x=cmip5, y = cmip6))+
  geom_point(alpha = 0.2)+
  geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  scale_y_continuous(name = "Change in biomass (%) CMIP6", limits = c(-200, 1200)) + # the very BROAD LIMITS are to cover BOATS changes in CMIP6....  
  scale_x_continuous(name = "Change in biomass (%) CMIP5", limits = c(-200, 200))+ 
  # scale_color_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  # scale_fill_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.title.y = element_text(vjust=0.4, size = 22),
        axis.title.x = element_text(vjust=0.3, size = 22),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.minor = element_blank(),
        # legend.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text.x = element_text(face = "bold"))+
        # legend.position = c(0.13, 0.3))+
  facet_wrap(~model, scale = "free")

# CMIP6 vs latitude 
b<-ggplot(all_ipsl, aes(x=lat, y = cmip6))+
  geom_point(alpha = 0.2)+
  # geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
  scale_y_continuous(name = "Latitude") + # the very BROAD LIMITS are to cover BOATS changes in CMIP6....  
  scale_x_continuous(name = "Change in biomass (%) CMIP5")+ 
  # scale_color_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  # scale_fill_manual(values = c("black","blue" ,"red"), name = "Scenarios", labels = c("Historical", "RCP2.6", "RCP8.6"))+
  theme_bw()+
  theme(text = element_text(size=20),
        axis.title.y = element_text(vjust=0.4, size = 22),
        axis.title.x = element_text(vjust=0.3, size = 22),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.minor = element_blank(),
        # legend.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.border = element_rect(colour = "black"),
        strip.text.x = element_text(face = "bold"))+
        # legend.position = c(0.13, 0.3))+
  facet_wrap(~model, scale = "free")

# layout <- "
# AB
# CD
# "
# 
# a1<-a1 + ggtitle("a) CMIP5 IPSL-CM5A-LR") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0), axis.title.x = element_blank())
# b1<-b1 + ggtitle("b) CMIP6 IPSL-CM6A-LR") + theme(plot.title = element_text(size = 16, face = "bold",hjust = 0), axis.title.x = element_blank(), axis.title.y = element_blank())
# a2<-a2 + ggtitle("c) CMIP5 GFDL-ESM2M") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
# b2<-b2 + ggtitle("d) CMIP6 GFDL-ESM4") + theme(plot.title = element_text(size = 16, face = "bold",hjust = 0), axis.title.y = element_blank()) # legend.position = "none"
# 
# plot<-a1 + b1 + a2 + b2 + 
#   plot_layout(design = layout)

pdf(paste0(save_loc,"Scatterplot_ipsl.pdf"), height=12, width=15) # no matters the set of models as the plot can be done only for 
a
dev.off()

pdf(paste0(save_loc,"Scatterplot_ipsl_latitude.pdf"), height=12, width=15) # CONSIDER ALL MODELS
b
dev.off()

```


# random and model-specific plots *can skyp*

```{r}
# # Delta models ipsl vs mean over all model ipsl CMIP6 
# # can do CMIP5 too
# 
# layout <- "
# AB
# CD
# EF
# "
# # plot titles - should add to code creating plots above 
# delta_average_boats<-delta_average_boats + ggtitle("BOATS") + theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_dbmp<-delta_average_dbmp + ggtitle("DBPM")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_ecotroph<-delta_average_ecotroph + ggtitle("EcoTroph")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_feisty<-delta_average_feisty + ggtitle("FEISTY")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_macroecological<- delta_average_macroecological + ggtitle("MACROECOLOGICAL")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_zoomss<- delta_average_zoomss + ggtitle("ZooMSS")+  theme(plot.title = element_text(size = 12, face = "bold"))
# 
# pt<-delta_average_boats + delta_average_dbmp + 
#   delta_average_ecotroph + delta_average_feisty +
#   delta_average_macroecological + delta_average_zoomss +
#   plot_layout(design = layout)
# 
# pt<-pt + plot_annotation(
#   title = 'Delta average models IPSL RCP 8.5 CMIP6',
#   theme = theme(plot.title = element_text(size = 20)))
# 
# pdf(paste0(save_loc,"20201104_delta_models_cmip6_noApecosm.pdf"), height=10, width=15)
# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# pt 
# dev.off()
# 
# # for CMIP5 
# 
# layout <- "
# AB
# CD
# "
# # plot titles - should add to code creating plots above 
# delta_average_boats_cmip5<-delta_average_boats_cmip5 + ggtitle("BOATS") + theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_dbmp_cmip5<-delta_average_dbmp_cmip5 + ggtitle("DBPM")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_macroecological_cmip5<- delta_average_macroecological_cmip5 + ggtitle("MACROECOLOGICAL")+  theme(plot.title = element_text(size = 12, face = "bold"))
# delta_average_ecoocean_cmip5<- delta_average_ecoocean_cmip5 + ggtitle("EcoOcean")+  theme(plot.title = element_text(size = 12, face = "bold"))
# # delta_average_apecosm_cmip5<- delta_average_apecosm_cmip5 + ggtitle("Apecosm")+  theme(plot.title = element_text(size = 12, face = "bold"))
# # delta_avarave_dbem_cmip5<- delta_average_dbem_cmip5 + ggtitle("DBEM")+  theme(plot.title = element_text(size = 12, face = "bold"))
# 
# pt<-delta_average_boats_cmip5 + delta_average_dbmp_cmip5 + 
#   delta_average_macroecological_cmip5 + delta_average_ecoocean_cmip5 +
#   # delta_average_apecosm_cmip5 + # delta_avarave_dbem_cmip5 +
#   plot_layout(design = layout)
# 
# pt<-pt + plot_annotation(
#   title = 'Delta average models IPSL RCP 8.5 CMIP5',
#   theme = theme(plot.title = element_text(size = 20)))
# 
# pdf(paste0(save_loc,"20201104_delta_models_cmip5_noApecosm.pdf"), height=10, width=15)
# # tiff(paste0(save_loc,"20201104_IPSL_CMIP5vsCMIP5_mean.tiff"), height=10, width=20, units ='in', res=300)
# pt 
# dev.off()

```