---
title: "Plotting global models' inputs"
author: "Camilla Novaglio"
date: "02/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# TO DO 

ref paper: https://doi.org/10.5194/bg-17-3439-2020

# Load libraries for netcdf and define variables

```{r load CMIP5}

rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)
library(patchwork)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/20210525/"

# variables - TO CHANGE 
cmip<-c("CMIP5", "CMIP6")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values_tos = c(0,30) # C and following Ryan paper  

# for CMIP6.... units checked by checking max and min in 2030 for each variable # MAX are too high for all 
# main_plot_colour_values_pp = c(1e-09,5e-07) # mol m-2 s-1 # ryan paper is in mg C m-2 d-1
# main_plot_colour_values_phyto = c(0, 0.3) # mol m-2 # ryan paper is in mg C m-2
# main_plot_colour_values_zoo = c(0,0.5) # mol m-2 # ryan paper is in mg C m-2
main_plot_colour_values_pp = c(0,1) # g C m-2 d-1 
main_plot_colour_values_phyto = c(0, 4) # g C m-2 
main_plot_colour_values_zoo = c(0, 4) # g C m-2 
delta_plot_colour_values = c(-50,50)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots (% change between cmips) # purple to yellow shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 
colour_scheme4 <- c(low = 'white', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# load ISIMIP2b inputs 

```{r}

# extract data IPSL ---- 

directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP2b/IPSL_CM5A_LR/"

variable_to_extract <-c("to", "pp", "phy", "zoo")

yearmonth1<- as.yearmon("1990-01")
yearmonth2<- as.yearmon("1999-01") # yearly values

yearmonth1_fut<- as.yearmon("2090-01")
yearmonth2_fut<- as.yearmon("2099-01")

data_ipsl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # i = 2
  # the variable is temperature,extract and convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], ".nc4.zs.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 # can be done later on if this is going to be merged with the loop below
    hist$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp261_20060101_21001231_1Y.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],".nc4.zs.rgrd.v3.rcp851_20060101_21001231_1Y.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"

    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  
  }else{ # the variable is other than temperature, extract both small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
      
      filename<-paste0("l",variable_to_extract[i], ".nc4.zint.rgrd.v3.historical1_19500101_20051231_1Y.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp26.1_20060101_21001231_1Y.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("s", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      
      filename<-paste0("l",variable_to_extract[i],".nc4.zint.rgrd.v3.rcp85.1_20060101_21001231_1Y.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("l", variable_to_extract[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = TRUE, hist = FALSE)
      
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 
      
      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      if(variable_to_extract[i] == "pp"){
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }
      
      # (mean(hist$fishvar, na.rm = TRUE)/0.0000115741)*1000 # mg * day as per Ryan 
      # (mean(hist$fishvar, na.rm = TRUE)/3.1709791983765e-8) # g per year as per cmip6 input paper 
      # (mean(hist$fishvar, na.rm = TRUE)/0.0000115741) # g per days as here 
      
      diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
      diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
    
  }
  
  data_ipsl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
  
}

# extract data GFDL ---- 

directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP2b/GFDL_ESM2M/"

variable_to_extract <-c("to", "pp", "phy", "zoo")
# the variable inside the netcdf is called differently than the variable in the file name.  
variable_to_extract2 <-c("TO_ZS", "PP_ZINT", "PHY_ZINT", "ZOO_ZINT")

data_gfdl_CMIP5<-list()

for (i in 1:length(variable_to_extract)){

  # the variable is temperature,extract adn convert from K to C
  if(variable_to_extract[[i]] == "to"){
    
    filename<-paste0(variable_to_extract[i], "_gfdl-esm2m_historical_zs_annual_195001-200512.nc4")
    hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
    # from k to C
    hist$fishvar<-hist$fishvar - 273.15 # can be done later on if this is going to be merged with the loop below
    hist$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp26_zs_annual_200601-210012.nc4")
    fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
    fut126$fishvar<-fut126$fishvar - 273.15
    fut126$data_units<-"C"
  
    filename<-paste0(variable_to_extract[i],"_gfdl-esm2m_rcp85_zs_annual_200601-210012.nc4")
    fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract2[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
    fut585$fishvar<-fut585$fishvar - 273.15
    fut126$data_units<-"C"
    
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  
  }else{ # # the variable is other than temperature, extract both small and large PP, phy or zoo and sum the size classes
    
      filename<-paste0("s",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histS<- averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
      filename<-paste0("l",variable_to_extract[i], "_gfdl-esm2m_historical_zint_annual_195001-200512.nc4")
      histL<- averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = TRUE)
      hist<-histS
      hist$fishvar<-hist$fishvar+histL$fishvar 
      
      hist$fishvar<-hist$fishvar * 12 
      hist$data_units<-paste0(hist$data_units, " CN converted in g C")
 
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp26_zint_annual_200601-210012.nc4")
      fut126L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      fut126<-fut126S
      fut126$fishvar<-fut126$fishvar+fut126L$fishvar 
      
      fut126$fishvar<-fut126$fishvar * 12 
      fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
      
      filename<-paste0("s",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585S<-averageEnvironmentalCDF(directory, filename , paste0("S", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
      filename<-paste0("l",variable_to_extract[i],"_gfdl-esm2m_rcp85_zint_annual_200601-210012.nc4")
      fut585L<-averageEnvironmentalCDF(directory, filename , paste0("L", variable_to_extract2[i]), yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, ipsl = FALSE, hist = FALSE)
  
      fut585<-fut585S
      fut585$fishvar<-fut585$fishvar+fut585L$fishvar 
      fut585$fishvar<-fut585$fishvar * 12 
      fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
      if(variable_to_extract[i] == "pp"){
        hist$fishvar<-hist$fishvar / 0.0000115741
        hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
        fut126$fishvar<-fut126$fishvar / 0.0000115741
        fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
        fut585$fishvar<-fut585$fishvar / 0.0000115741
        fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
      }
      
      diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
      diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
    
  }
  
  data_gfdl_CMIP5[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
  
}

names(data_gfdl_CMIP5)

```

# Plot ISIMIP2b inputs

```{r map CMIP6}

# flip matrix

fliplr_matrix<- function(data_to_flip){
  temp= data_to_flip
  for (ii in 1:dim(data_to_flip)[2])
    data_to_flip[,ii] = temp[,dim(data_to_flip)[2] - ii + 1]
  
  data_to_flip
}

move_hemispheres<- function(data_to_flip){
  temp= data_to_flip
  data_to_flip[1:180,] = temp[181:360,]
  data_to_flip[181:360,] = temp[1:180,]
  data_to_flip
}
  

## plot IPSL ----

data_ipsl_CMIP5$to$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$to$diff_8p5)
data_ipsl_CMIP5$to$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$to$diff_8p5)

data_ipsl_CMIP5$to$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$to$fut585$fishvar)
data_ipsl_CMIP5$to$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$to$fut585$fishvar)
data_ipsl_CMIP5$to$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$to$hist$fishvar)
data_ipsl_CMIP5$to$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$to$hist$fishvar)

data_ipsl_CMIP5$pp$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$pp$diff_8p5)
data_ipsl_CMIP5$pp$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$pp$diff_8p5)
data_ipsl_CMIP5$pp$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$pp$fut585$fishvar)
data_ipsl_CMIP5$pp$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$pp$fut585$fishvar)
data_ipsl_CMIP5$pp$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$pp$hist$fishvar)
data_ipsl_CMIP5$pp$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$pp$hist$fishvar)

data_ipsl_CMIP5$phy$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$phy$diff_8p5)
data_ipsl_CMIP5$phy$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$phy$diff_8p5)
data_ipsl_CMIP5$phy$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$phy$fut585$fishvar)
data_ipsl_CMIP5$phy$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$phy$fut585$fishvar)
data_ipsl_CMIP5$phy$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$phy$hist$fishvar)
data_ipsl_CMIP5$phy$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$phy$hist$fishvar)

data_ipsl_CMIP5$zoo$diff_8p5<- fliplr_matrix(data_ipsl_CMIP5$zoo$diff_8p5)
data_ipsl_CMIP5$zoo$diff_8p5<- move_hemispheres(data_ipsl_CMIP5$zoo$diff_8p5)
data_ipsl_CMIP5$zoo$fut585$fishvar<- fliplr_matrix(data_ipsl_CMIP5$zoo$fut585$fishvar)
data_ipsl_CMIP5$zoo$fut585$fishvar<- move_hemispheres(data_ipsl_CMIP5$zoo$fut585$fishvar)
data_ipsl_CMIP5$zoo$hist$fishvar<- fliplr_matrix(data_ipsl_CMIP5$zoo$hist$fishvar)
data_ipsl_CMIP5$zoo$hist$fishvar<- move_hemispheres(data_ipsl_CMIP5$zoo$hist$fishvar)

titles<-c("Sea surface temperature", "Net primary production","Phytoplankton carbon","Zooplankton carbon")
coltitles<-c("C", "g C m-2 d-1","g C m-2","g C m-2") # check that all units are the same across CMIPs and earth models - transform to more meaningful - e.g. milligrams?
data_ipsl_CMIP5$to$hist$data_units
data_ipsl_CMIP5$pp$hist$data_units
data_ipsl_CMIP5$phy$hist$data_units
data_ipsl_CMIP5$zoo$hist$data_units

color<-list(main_plot_colour_values_tos, main_plot_colour_values_pp, main_plot_colour_values_phyto, main_plot_colour_values_zoo) 
num_dp_variables<-c(0,1,0,0)

## plot GFDL ----

names(data_gfdl_CMIP5)

data_gfdl_CMIP5$to$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$to$diff_8p5)
data_gfdl_CMIP5$to$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$to$diff_8p5)

data_gfdl_CMIP5$to$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$to$fut585$fishvar)
data_gfdl_CMIP5$to$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$to$fut585$fishvar)
data_gfdl_CMIP5$to$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$to$hist$fishvar)
data_gfdl_CMIP5$to$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$to$hist$fishvar)

data_gfdl_CMIP5$pp$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$pp$diff_8p5)
data_gfdl_CMIP5$pp$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$pp$diff_8p5)
data_gfdl_CMIP5$pp$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$pp$fut585$fishvar)
data_gfdl_CMIP5$pp$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$pp$fut585$fishvar)
data_gfdl_CMIP5$pp$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$pp$hist$fishvar)
data_gfdl_CMIP5$pp$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$pp$hist$fishvar)

data_gfdl_CMIP5$phy$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$phy$diff_8p5)
data_gfdl_CMIP5$phy$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$phy$diff_8p5)
data_gfdl_CMIP5$phy$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$phy$fut585$fishvar)
data_gfdl_CMIP5$phy$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$phy$fut585$fishvar)
data_gfdl_CMIP5$phy$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$phy$hist$fishvar)
data_gfdl_CMIP5$phy$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$phy$hist$fishvar)

data_gfdl_CMIP5$zoo$diff_8p5<- fliplr_matrix(data_gfdl_CMIP5$zoo$diff_8p5)
data_gfdl_CMIP5$zoo$diff_8p5<- move_hemispheres(data_gfdl_CMIP5$zoo$diff_8p5)
data_gfdl_CMIP5$zoo$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP5$zoo$fut585$fishvar)
data_gfdl_CMIP5$zoo$fut585$fishvar<- move_hemispheres(data_gfdl_CMIP5$zoo$fut585$fishvar)
data_gfdl_CMIP5$zoo$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP5$zoo$hist$fishvar)
data_gfdl_CMIP5$zoo$hist$fishvar<- move_hemispheres(data_gfdl_CMIP5$zoo$hist$fishvar)

# coltitles<-c("C", "mol m-2 s-1","mol m-2","mol m-2") 
# check units 
data_gfdl_CMIP5$to$hist$data_units
data_gfdl_CMIP5$pp$hist$data_units
data_gfdl_CMIP5$phy$hist$data_units
data_gfdl_CMIP5$zoo$hist$data_units

```

# Model average for CMIP5

```{r}

# you can calculate SD and agreement as in batch_run_maps.R

model_stat<-function(data, variable){

  # i = 1
  # data=list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]])
  # variable = 'hist'
  
  X <- lapply(data, `[[`, variable)
  
  if (variable != "diff_8p5"){
    X <- lapply(X, `[[`, 'fishvar')
  }
  
  X <- lapply(X, function(x) replace(x, !is.finite(x), NA))
  Y <- do.call(cbind, X)
  Y <- array(Y, dim=c(dim(X[[1]]), length(X)))
  model_average_new<-apply(Y, c(1, 2), mean, na.rm = TRUE)

  return(list(model_average = model_average_new))
}

data_average_change_CMIP5<-list()
data_average_value_2000_CMIP5<-list()
data_average_value_2100_CMIP5<-list()

names(data_ipsl_CMIP5)

for(i in 1:length(data_ipsl_CMIP5)){
  
  # i = 1
  data_average_change_CMIP5[[i]]<-model_stat(list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]]), variable = 'diff_8p5')$model_average
  names(data_average_change_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  data_average_value_2000_CMIP5[[i]]<-model_stat(list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]]), variable = 'hist')$model_average
  names(data_average_value_2000_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  data_average_value_2100_CMIP5[[i]]<-model_stat(list(data_ipsl_CMIP5[[i]], data_gfdl_CMIP5[[i]]), variable = 'fut585')$model_average
  names(data_average_value_2100_CMIP5)[[i]]<-variable_to_extract[[i]]
  
}

# plot earth models average for all input variables

delta_plot_colour_values_new<-list(c(0,4), delta_plot_colour_values, delta_plot_colour_values, delta_plot_colour_values)
coltitles1<-list("Change \n(째C)", "Change \n(%)", "Change \n(%)", "Change \n(%)")
colour_scheme_vary<-list(c(low = "white", mid = '#fee5d9', high = "#de2d26"),colour_scheme2,colour_scheme2,colour_scheme2) # or mid = #fcbba1 for darker 

map_average_change_CMIP5<-list()
map_average_value_2000_CMIP5<-list()
map_average_value_2100_CMIP5<-list()

for (i in 1:length(data_average_change_CMIP5)){ 
  
  # i = 1
  tit <- paste("Mean change in", titles[[i]], "RCP 8.5, 1990s to 2090s",cmip[1], sep =" ")
  map_average_change_CMIP5[[i]]<-plot_FISH_MIP(data_average_change_CMIP5[[i]], tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_average_change_CMIP5)[[i]]<-variable_to_extract[[i]]

  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 1990s", cmip[1], sep =" ")
  map_average_value_2000_CMIP5[[i]]<-plot_FISH_MIP(data_average_value_2000_CMIP5[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2000_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 2090s", cmip[1], sep =" ")
  map_average_value_2100_CMIP5[[i]]<-plot_FISH_MIP(data_average_value_2100_CMIP5[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2100_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

# map_average_change_CMIP5$to
# map_average_value_2000_CMIP5$phy
# map_average_value_2000_CMIP5$zoo
# map_average_value_2100_CMIP5$pp
# 
# max(data_average_value_2000_CMIP5$pp, na.rm = TRUE) # 2 ### CHANGE to 1
# min(data_average_value_2000_CMIP5$pp, na.rm = TRUE) # 0.05 # change to 0
# mean(data_average_value_2000_CMIP5$pp, na.rm = TRUE)
# max(data_average_value_2000_CMIP5$phy, na.rm = TRUE) # 6 ### CHANGE to  4
# min(data_average_value_2000_CMIP5$phy, na.rm = TRUE) # 0
# mean(data_average_value_2000_CMIP5$phy, na.rm = TRUE)
# max(data_average_value_2000_CMIP5$zoo, na.rm = TRUE) # 6 ### CHANGE to 4
# min(data_average_value_2000_CMIP5$zoo, na.rm = TRUE) # 0
# mean(data_average_value_2000_CMIP5$zoo, na.rm = TRUE)

# do same maps for single ESMs - DONE BELOW... 

# map_average_change_CMIP5_ipsl<-list()
# 
# for (i in 1:length(data_ipsl_CMIP5)){ 
#   
#   # i = 1
#   tit <- paste("Mean change in", titles[[i]], "IPSL RCP 8.5, 1990s to 2090s",cmip[1], sep =" ")
#   map_average_change_CMIP5_ipsl[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
#   names(map_average_change_CMIP5_ipsl)[[i]]<-variable_to_extract[[i]]
#   
#   rm(tit)
#   
# }
# 
# map_average_change_CMIP5_gfdl<-list()
# 
# for (i in 1:length(data_gfdl_CMIP5)){ 
#   
#   # i = 1
#   tit <- paste("Mean change in", titles[[i]], "GFDL RCP 8.5, 1990s to 2090s",cmip[1], sep =" ")
#   map_average_change_CMIP5_gfdl[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
#   names(map_average_change_CMIP5_gfdl)[[i]]<-variable_to_extract[[i]]
#   
#   rm(tit)
#   
# }
# 
# # map_average_change_CMIP5_ipsl$to
# # map_average_change_CMIP5_gfdl$to
# # map_average_change_CMIP5$to

```

# save inputs ISIMIP2b temp 

```{r}

data_summaries_CMIP5<-list(data_average_change_CMIP5 = data_average_change_CMIP5, data_average_value_2000_CMIP5 = data_average_value_2000_CMIP5, data_average_value_2100_CMIP5 = data_average_value_2100_CMIP5)
map_summaries_CMIP5<-list(map_average_change_CMIP5 = map_average_change_CMIP5, map_average_value_2000_CMIP5 = map_average_value_2000_CMIP5, map_average_value_2000_CMIP5 = map_average_value_2000_CMIP5) #, map_average_change_CMIP5_ipsl = map_average_change_CMIP5_ipsl, map_average_change_CMIP5_gfdl = map_average_change_CMIP5_gfdl)
save(data_ipsl_CMIP5, data_gfdl_CMIP5, data_summaries_CMIP5, map_summaries_CMIP5, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_inputs_CMIP5.RData")

```

# Load ISIMIP3b inputs 

```{r}

# CMIP6 data location
directory = "/Users/camillan/fishmip_inputs/marine-fishery_global_ISIMIP3b/"

# extract data IPSL ---- 

variable_to_extract <-c("to", "pp", "phy", "zoo") # just to be consistent with names across cmips and earth models 
variable_to_extract3 <-c("tos", "intpp", "phyc-vint", "zooc-vint")

yearmonth1<- as.yearmon("1990-01")
yearmonth2<- as.yearmon("1999-12") # montly values 

yearmonth1_fut<- as.yearmon("2090-01")
yearmonth2_fut<- as.yearmon("2099-12")

data_ipsl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut126<-averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("ipsl-cm6a-lr_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  if (variable_to_extract3[[i]] == "tos"){
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  }else {
    
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }

    diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
    diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  }
  
  data_ipsl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126, fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_ipsl_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_ipsl_CMIP6)

# extract data GFDL ---- 

data_gfdl_CMIP6<-list()

for (i in 1:length(variable_to_extract3)){

  filename<-paste0("gfdl-esm4_r1i1p1f1_historical_", variable_to_extract3[i],"_onedeg_global_monthly_1850_2014.nc")
  
  hist<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1, yearmonth2, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = TRUE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp126_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut126<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  filename<-paste0("gfdl-esm4_r1i1p1f1_ssp585_", variable_to_extract3[i],"_onedeg_global_monthly_2015_2100.nc")
  
  fut585<- averageEnvironmentalCDF(directory, filename , variable_to_extract3[i], yearmonth1_fut, yearmonth2_fut, average_whole_period = TRUE, convert_to_kg_km = FALSE, hist = FALSE, cmip = 6)
  
  if (variable_to_extract3[[i]] == "tos"){
    # do celsius change 
    diff_2p6 = fut126$fishvar - hist$fishvar # 20C - 15C = 5C (celsius increase)
    diff_8p5 = fut585$fishvar - hist$fishvar
  }else {
    
    hist$fishvar<-hist$fishvar * 12 
    hist$data_units<-paste0(hist$data_units, " CN converted in g C")
    fut126$fishvar<-fut126$fishvar * 12 
    fut126$data_units<-paste0(fut126$data_units, " CN converted in g C")
    fut585$fishvar<-fut585$fishvar * 12 
    fut585$data_units<-paste0(fut585$data_units, " CN converted in g C")
      
    if(variable_to_extract3[[i]] == "intpp"){
      hist$fishvar<-hist$fishvar / 0.0000115741
      hist$data_units<-paste0(hist$data_units, " CN converted in d-1") 
      fut126$fishvar<-fut126$fishvar / 0.0000115741
      fut126$data_units<-paste0(fut126$data_units, " CN converted in d-1") 
      fut585$fishvar<-fut585$fishvar / 0.0000115741
      fut585$data_units<-paste0(fut585$data_units, " CN converted in d-1") 
    }

    diff_2p6 = fut126$fishvar / hist$fishvar * 100 - 100
    diff_8p5 = fut585$fishvar / hist$fishvar * 100 - 100
  }
  
  data_gfdl_CMIP6[[i]]<-list(hist = hist, fut126 = fut126,  fut585 = fut585, diff_2p6 = diff_2p6, diff_8p5 = diff_8p5)
  names(data_gfdl_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(hist, fut126, fut585, diff_2p6, diff_8p5)
 
}

names(data_gfdl_CMIP6)

```

# Plot ISIMIP3b inputs

```{r map CMIP6}

## plot IPSL ----

# same as above - need to run if only considering CMIP6
# titles<-c("Sea surface temperature", "Net primary production","Phytoplankton carbon","Zooplankton carbon")
# coltitles<-c("C", "mol m-2 s-1","mol m-2","mol m-2")
# color<-list(main_plot_colour_values_tos, main_plot_colour_values_pp, main_plot_colour_values_phyto, main_plot_colour_values_zoo) 
# check units
data_ipsl_CMIP6$to$hist$data_units
data_ipsl_CMIP6$pp$hist$data_units
data_ipsl_CMIP6$phy$hist$data_units
data_ipsl_CMIP6$zoo$hist$data_units

## plot GFDL ----

# need to model hemisphere
# checked: different data layout do not effect the calculation of model mean, SD and agreements because these are done after you flipped the matrix and/or change hemisphere. it does not effect the calculation of trends because you are first weighting biomass by grid cell according to explicit lat values and then you are averaging by lat and long anyway.

data_gfdl_CMIP6$to$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$to$diff_8p5)
data_gfdl_CMIP6$to$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$to$fut585$fishvar)
data_gfdl_CMIP6$to$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$to$hist$fishvar)

data_gfdl_CMIP6$pp$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$pp$diff_8p5)
data_gfdl_CMIP6$pp$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$pp$fut585$fishvar)
data_gfdl_CMIP6$pp$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$pp$hist$fishvar)

data_gfdl_CMIP6$phy$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$phy$diff_8p5)
data_gfdl_CMIP6$phy$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$phy$fut585$fishvar)
data_gfdl_CMIP6$phy$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$phy$hist$fishvar)

data_gfdl_CMIP6$zoo$diff_8p5<- fliplr_matrix(data_gfdl_CMIP6$zoo$diff_8p5)
data_gfdl_CMIP6$zoo$fut585$fishvar<- fliplr_matrix(data_gfdl_CMIP6$zoo$fut585$fishvar)
data_gfdl_CMIP6$zoo$hist$fishvar<- fliplr_matrix(data_gfdl_CMIP6$zoo$hist$fishvar)

```

# Model average for CMIP6

```{r}

data_average_change_CMIP6<-list()
data_average_value_2000_CMIP6<-list()
data_average_value_2100_CMIP6<-list()

for(i in 1:length(data_ipsl_CMIP6)){
  
  # i = 1
  data_average_change_CMIP6[[i]]<-model_stat(list(data_ipsl_CMIP6[[i]], data_gfdl_CMIP6[[i]]), variable = 'diff_8p5')$model_average
  names(data_average_change_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  data_average_value_2000_CMIP6[[i]]<-model_stat(list(data_ipsl_CMIP6[[i]], data_gfdl_CMIP6[[i]]), variable = 'hist')$model_average
  names(data_average_value_2000_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  data_average_value_2100_CMIP6[[i]]<-model_stat(list(data_ipsl_CMIP6[[i]], data_gfdl_CMIP6[[i]]), variable = 'fut585')$model_average
  names(data_average_value_2100_CMIP6)[[i]]<-variable_to_extract[[i]]
  
}

# plot earth models average for all input variables

map_average_change_CMIP6<-list()
map_average_value_2000_CMIP6<-list()
map_average_value_2100_CMIP6<-list()

for (i in 1:length(data_average_change_CMIP6)){ 
  
  # i = 1
  tit <- paste("Mean change in", titles[[i]], "RCP 8.5, 1990s to 2090s",cmip[2], sep =" ")
  map_average_change_CMIP6[[i]]<-plot_FISH_MIP(data_average_change_CMIP6[[i]], tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_average_change_CMIP6)[[i]]<-variable_to_extract[[i]]

  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 1990s", cmip[2], sep =" ")
  map_average_value_2000_CMIP6[[i]]<-plot_FISH_MIP(data_average_value_2000_CMIP6[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2000_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste("Mean", titles[[i]], "across IPSL and GFDL RCP 8.5, 2090s", cmip[2], sep =" ")
  map_average_value_2100_CMIP6[[i]]<-plot_FISH_MIP(data_average_value_2100_CMIP6[[i]], tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_average_value_2100_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

```


# save inputs ISIMIP3b temp 

```{r}

data_summaries_CMIP6<-list(data_average_change_CMIP6 = data_average_change_CMIP6, data_average_value_2000_CMIP6 = data_average_value_2000_CMIP6, data_average_value_2100_CMIP6 = data_average_value_2100_CMIP6)
map_summaries_CMIP6<-list(map_average_change_CMIP6 = map_average_change_CMIP6, map_average_value_2000_CMIP6 = map_average_value_2000_CMIP6, map_average_value_2000_CMIP6 = map_average_value_2000_CMIP6)
save(data_ipsl_CMIP6, data_gfdl_CMIP6, data_summaries_CMIP6, map_summaries_CMIP6, file = "/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_inputs_CMIP6.RData")

```



# load outputs 

```{r}

rm(list=ls())
variable_to_extract <-c("to", "pp", "phy", "zoo")
titles<-c("Sea surface temperature", "Net primary production","Phytoplankton carbon","Zooplankton carbon")
coltitles<-c("째C", "g C m-2 d-1","g C m-2","g C m-2") #

# run first 2 sections above 
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_inputs_CMIP6.RData")
load("/Users/camillan/fishmip_outputs/CMIP6vsCMIP5_fig_temp/data_inputs_CMIP5.RData")

```

# Load libraries for netcdf and define variables

```{r load CMIP5}

#rm(list=ls())
library(grid)
library(zoo)
library(viridis)
library(tidyr)
library(dplyr)
library(patchwork)

source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/HelperScripts.r")
source("/Users/camillan/R-projects/CMIP5vsCMIP6/R/Funcs_maps.r")

# saving outputs location  
save_loc <- "/Users/camillan/Dropbox/CMIP5vsCMIP6/CMIP5vsCMIP6_figs/20210525/"

# variables - TO CHANGE 
cmip<-c("CMIP5", "CMIP6")
protocol <- c("picontrol","historical", "future")
future<-c("SSP126", "SSP585")

```

# load libraries for plotting and define criteria 

```{r}

# Define color/legend limits 
main_plot_colour_values_tos = c(0,30) # C and following Ryan paper  

# for CMIP6.... units checked by checking max and min in 2030 for each variable # MAX are too high for all 
# main_plot_colour_values_pp = c(1e-09,5e-07) # mol m-2 s-1 # ryan paper is in mg C m-2 d-1
# main_plot_colour_values_phyto = c(0, 0.3) # mol m-2 # ryan paper is in mg C m-2
# main_plot_colour_values_zoo = c(0,0.5) # mol m-2 # ryan paper is in mg C m-2
main_plot_colour_values_pp = c(0,1) # g C m-2 d-1 
main_plot_colour_values_phyto = c(0, 4) # g C m-2 
main_plot_colour_values_zoo = c(0, 4) # g C m-2 
delta_plot_colour_values = c(-50,50)

# define a color scheme 
colour_scheme1 <- c(low = 'white', mid = "skyblue1",  high = 'royalblue1') # for statistics - e.g model mean, SD and agreement
colour_scheme2 <- c(low = 'red', mid = "white",  high = 'royalBlue1') # for % changes - either increasing or decreasing 
colour_scheme3 <- c("#fdb863", "#f7f7f7","#b2abd2") # for delta plots (% change between cmips) # purple to yellow shades
colour_scheme4 <- c(low = '#e0ecf4', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 
colour_scheme4 <- c(low = 'white', mid = "#9ebcda",  high = '#8856a7') # for inputs values # shades of blue to purple?? 

# Download and process world outline
library(sf)
library(rnaturalearth)
library("rgeos")
world <- ne_countries(scale = "medium", returnclass = "sf")
robCRS <- CRS("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
world_sf <- st_transform(world, crs = st_crs(robCRS)) # Convert to different CRS

```

# Delta plot 

```{r}

# option 1 - subtract (julia) - OK
delta_plot_colour_values_new2<-list(c(-2, 2), c(-30, 30), c(-30, 30), c(-30, 30)) # highlight delta changes more ..... 

delta_data<-list()
delta_map<-list()

coltitleDelta<-c("Difference \nin \nchange \n(째C)","Difference \nin \nchange \n(%)","Difference \nin \nchange \n(%)","Difference \nin \nchange \n(%)")

for(i in 1:length(data_summaries_CMIP6$data_average_change_CMIP6)){
 
  # NOTE it should be OK with temp too even if temp is in C change and the other are in % change
  # if positive -> t, pp, phy or zoo have increased between 1990s and 2090s more in CMIP6 than in CMIP5
  # if negative, inputs have increased more in CMIP5 than CMIP6
  
  delta_data[[i]]<-data_summaries_CMIP6$data_average_change_CMIP6[[i]] - data_summaries_CMIP5$data_average_change_CMIP5[[i]]
  names(delta_data)[[i]]<-variable_to_extract[[i]]
  
  tit<-paste("Delta (CMIP6 change - CMIP5 change)", titles[[i]], sep =" ")
  delta_map[[i]]<-plot_FISH_MIP(delta_data[[i]], tit, delta_plot_colour_values_new2[[i]], colour_scheme = colour_scheme3, coltitle = coltitleDelta[[i]])  
  names(delta_map)[[i]]<-variable_to_extract[[i]]
  
}

```

# Put all maps together 

```{r multipanel plot}

library(patchwork)

# change between 1990 and 2090s for CMIP5 and form CMIP6 and delta between CMIPs 

layout <- "
AB
CD
"

a<-map_summaries_CMIP6$map_average_change_CMIP6$to +  ggtitle("a) SST CMIP6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-delta_map$to +  ggtitle("b) SST change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_summaries_CMIP6$map_average_change_CMIP6$pp + ggtitle("c) NPP CMIP6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-delta_map$pp + ggtitle("d) NPP change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<- a + b +
  c + d +
  plot_layout(design = layout)

# pdf(paste0(save_loc,"Fig2.pdf"), height=10, width=15)
# pt 
# dev.off()

# as above but with info on all variables 

layout <- "
ABC
DEF
GHK
LMN
"

a1<-map_summaries_CMIP5$map_average_change_CMIP5$to +  ggtitle("a) SST CMIP5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
a<-map_summaries_CMIP6$map_average_change_CMIP6$to +  ggtitle("b) SST CMIP6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-delta_map$to +  ggtitle("c) SST change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

c1<-map_summaries_CMIP5$map_average_change_CMIP5$pp + ggtitle("d) NPP CMIP5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_summaries_CMIP6$map_average_change_CMIP6$pp + ggtitle("e) NPP CMIP6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-delta_map$pp + ggtitle("f) NPP change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

e<-map_summaries_CMIP5$map_average_change_CMIP5$phy +  ggtitle("g) Phytoplankton carbon CMIP5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_summaries_CMIP6$map_average_change_CMIP6$phy + ggtitle("h) Phytoplankton carbon CMIP6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g<-delta_map$phy + ggtitle("i) Phytoplankton carbon change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

h<-map_summaries_CMIP5$map_average_change_CMIP5$zoo +  ggtitle("j) Zooplankton carbon CMIP5") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i<-map_summaries_CMIP6$map_average_change_CMIP6$zoo + ggtitle("k) Zooplankton carbon CMIP6") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l<-delta_map$zoo+ ggtitle("l) Zooplankton carbon change between CMIPs") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a1 + a + b +
  c1 + c + d +
  e + f + g +
  h+ i + l +
  plot_layout(design = layout)

pdf(paste0(save_loc,"Fig2.pdf"), height=15, width=20)
pt 
dev.off()



# can do RCP2.6 too?? 







# plot of values can skyp 
# layout <- "
# AB
# CD
# EF
# GH
# "
# 
# pt<-map_summaries_CMIP5$map_average_value_2000_CMIP5$to + map_summaries_CMIP6$map_average_value_2000_CMIP6$to +
#   map_summaries_CMIP5$map_average_value_2000_CMIP5$pp + map_summaries_CMIP6$map_average_value_2000_CMIP6$pp + 
#   map_summaries_CMIP5$map_average_value_2000_CMIP5$phy + map_summaries_CMIP6$map_average_value_2000_CMIP6$phy + 
#   map_summaries_CMIP5$map_average_value_2000_CMIP5$zoo + map_summaries_CMIP6$map_average_value_2000_CMIP6$zoo + 
#   plot_layout(design = layout)
# 
# pdf(paste0(save_loc,"Fig1B_1990.pdf"), height=15, width=15)
# pt 
# dev.off()
# 
# # FIG 1B or S1?? 
# layout <- "
# AB
# CD
# EF
# GH
# "
# 
# pt<-map_summaries_CMIP5$map_average_value_2100_CMIP5$to + map_summaries_CMIP6$map_average_value_2100_CMIP6$to +
#   map_summaries_CMIP5$map_average_value_2100_CMIP5$pp + map_summaries_CMIP6$map_average_value_2100_CMIP6$pp + 
#   map_summaries_CMIP5$map_average_value_2100_CMIP5$phy + map_summaries_CMIP6$map_average_value_2100_CMIP6$phy + 
#   map_summaries_CMIP5$map_average_value_2100_CMIP5$zoo + map_summaries_CMIP6$map_average_value_2100_CMIP6$zoo + 
#   plot_layout(design = layout)
# 
# pdf(paste0(save_loc,"Fig1B_2090.pdf"), height=15, width=15)
# pt 
# dev.off()

```

# maps of inputs by ESM 

```{r}

delta_plot_colour_values_new<-list(c(0,4), delta_plot_colour_values, delta_plot_colour_values, delta_plot_colour_values)
coltitles1<-list("Change \n(째C)", "Change \n(%)", "Change \n(%)", "Change \n(%)")
colour_scheme_vary<-list(c(low = "white", mid = '#fee5d9', high = "#de2d26"),colour_scheme2,colour_scheme2,colour_scheme2) # or mid = #fcbba1 for darker 
color<-list(main_plot_colour_values_tos, main_plot_colour_values_pp, main_plot_colour_values_phyto, main_plot_colour_values_zoo) 
num_dp_variables<-c(0,1,0,0)

map_ipsl_change_CMIP5<-list()
map_ipsl_value_2000_CMIP5<-list()
map_ipsl_value_2100_CMIP5<-list()

map_ipsl_change_CMIP5$to

for (i in 1:length(data_ipsl_CMIP5)){
    
  # i = 1
  tit <- paste("Change in", titles[[i]], "IPSL RCP 8.5, 1990s to 2090s",cmip[1], sep =" ")
  map_ipsl_change_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_ipsl_change_CMIP5)[[i]]<-variable_to_extract[[i]]

  tit <- paste(titles[[i]], "IPSL RCP 8.5, 1990s", cmip[1], sep =" ")
  map_ipsl_value_2000_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$hist$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_ipsl_value_2000_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste(titles[[i]], "IPSL RCP 8.5, 2090s", cmip[1], sep =" ")
  map_ipsl_value_2100_CMIP5[[i]]<-plot_FISH_MIP(data_ipsl_CMIP5[[i]]$fut585$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_ipsl_value_2100_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

map_gfdl_change_CMIP5<-list()
map_gfdl_value_2000_CMIP5<-list()
map_gfdl_value_2100_CMIP5<-list()

for (i in 1:length(data_gfdl_CMIP5)){
    
  # i = 1
  tit <- paste("Change in", titles[[i]], "GFDL RCP 8.5, 1990s to 2090s",cmip[1], sep =" ")
  map_gfdl_change_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$diff_8p5, tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_gfdl_change_CMIP5)[[i]]<-variable_to_extract[[i]]

  tit <- paste(titles[[i]], "GFDL RCP 8.5, 1990s", cmip[1], sep =" ")
  map_gfdl_value_2000_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$hist$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_gfdl_value_2000_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste(titles[[i]], "GFDL RCP 8.5, 2090s", cmip[1], sep =" ")
  map_gfdl_value_2100_CMIP5[[i]]<-plot_FISH_MIP(data_gfdl_CMIP5[[i]]$fut585$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_gfdl_value_2100_CMIP5)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

map_ipsl_change_CMIP6<-list()
map_ipsl_value_2000_CMIP6<-list()
map_ipsl_value_2100_CMIP6<-list()

for (i in 1:length(data_ipsl_CMIP6)){
    
  # i = 1
  tit <- paste("Change in", titles[[i]], "IPSL RCP 8.5, 1990s to 2090s",cmip[2], sep =" ")
  map_ipsl_change_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_ipsl_change_CMIP6)[[i]]<-variable_to_extract[[i]]

  tit <- paste(titles[[i]], "IPSL RCP 8.5, 1990s", cmip[2], sep =" ")
  map_ipsl_value_2000_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$hist$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_ipsl_value_2000_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste(titles[[i]], "IPSL RCP 8.5, 2090s", cmip[2], sep =" ")
  map_ipsl_value_2100_CMIP6[[i]]<-plot_FISH_MIP(data_ipsl_CMIP6[[i]]$fut585$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_ipsl_value_2100_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}

map_gfdl_change_CMIP6<-list()
map_gfdl_value_2000_CMIP6<-list()
map_gfdl_value_2100_CMIP6<-list()

for (i in 1:length(data_gfdl_CMIP6)){
    
  # i = 1
  tit <- paste("Change in", titles[[i]], "GFDL RCP 8.5, 1990s to 2090s",cmip[2], sep =" ")
  map_gfdl_change_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$diff_8p5, tit, delta_plot_colour_values_new[[i]], colour_scheme = colour_scheme_vary[[i]], coltitle = coltitles1[[i]], model_type = NA)
  names(map_gfdl_change_CMIP6)[[i]]<-variable_to_extract[[i]]

  tit <- paste(titles[[i]], "GFDL RCP 8.5, 1990s", cmip[2], sep =" ")
  map_gfdl_value_2000_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$hist$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_gfdl_value_2000_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  tit <- paste(titles[[i]], "GFDL RCP 8.5, 2090s", cmip[2], sep =" ")
  map_gfdl_value_2100_CMIP6[[i]]<-plot_FISH_MIP(data_gfdl_CMIP6[[i]]$fut585$fishvar, tit, color[[i]], colour_scheme = colour_scheme4, coltitle = coltitles[[i]], model_type = NA, num_dp = num_dp_variables[[i]])
  names(map_gfdl_value_2100_CMIP6)[[i]]<-variable_to_extract[[i]]
  
  rm(tit)
  
}


# changes between 90s and 2090s for CMIP5 by ESM

layout <- "
ABC
DEF
GHK
LMN
"

a1<-map_summaries_CMIP5$map_average_change_CMIP5$to +  ggtitle("c) SST CMIP5 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
a<-map_ipsl_change_CMIP5$to +  ggtitle("a) SST CMIP5 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_gfdl_change_CMIP5$to +  ggtitle("b) SST CMIP5 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

c1<-map_summaries_CMIP5$map_average_change_CMIP5$pp + ggtitle("f) NPP CMIP5 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_ipsl_change_CMIP5$pp + ggtitle("d) NPP CMIP5 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_gfdl_change_CMIP5$pp + ggtitle("e) NPP CMIP5 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

e<-map_summaries_CMIP5$map_average_change_CMIP5$phy +  ggtitle("i) Phytoplankton carbon CMIP5 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_ipsl_change_CMIP5$phy + ggtitle("g) Phytoplankton carbon CMIP5 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g<-map_gfdl_change_CMIP5$phy + ggtitle("h) Phytoplankton carbon CMIP5 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

h<-map_summaries_CMIP5$map_average_change_CMIP5$zoo +  ggtitle("l) Zooplankton carbon CMIP5 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i<- map_ipsl_change_CMIP5$zoo + ggtitle("j) Zooplankton carbon CMIP5 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l<-map_gfdl_change_CMIP5$zoo+ ggtitle("k) Zooplankton carbon CMIP5 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a + b + a1 +
  c + d + c1 +
  f + g + e +
  i + l + h +
  plot_layout(design = layout)

pdf(paste0(save_loc,"FigS1.pdf"), height=15, width=20)
pt
dev.off()

# CMIP6

a1<-map_summaries_CMIP6$map_average_change_CMIP6$to +  ggtitle("c) SST CMIP6 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
a<-map_ipsl_change_CMIP6$to +  ggtitle("a) SST CMIP6 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
b<-map_gfdl_change_CMIP6$to +  ggtitle("b) SST CMIP6 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

c1<-map_summaries_CMIP6$map_average_change_CMIP6$pp + ggtitle("f) NPP CMIP6 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
c<-map_ipsl_change_CMIP6$pp + ggtitle("d) NPP CMIP6 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
d<-map_gfdl_change_CMIP6$pp + ggtitle("e) NPP CMIP6 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

e<-map_summaries_CMIP6$map_average_change_CMIP6$phy +  ggtitle("i) Phytoplankton carbon CMIP6 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
f<-map_ipsl_change_CMIP6$phy + ggtitle("g) Phytoplankton carbon CMIP6 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
g<-map_gfdl_change_CMIP6$phy + ggtitle("h) Phytoplankton carbon CMIP6 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

h<-map_summaries_CMIP6$map_average_change_CMIP6$zoo +  ggtitle("l) Zooplankton carbon CMIP6 ESMs average") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
i<- map_ipsl_change_CMIP6$zoo + ggtitle("j) Zooplankton carbon CMIP6 IPSL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))
l<-map_gfdl_change_CMIP6$zoo+ ggtitle("k) Zooplankton carbon CMIP6 GFDL") + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0))

pt<-a + b + a1 +
  c + d + c1 +
  f + g + e +
  i + l + h +
  plot_layout(design = layout)

pdf(paste0(save_loc,"FigS2.pdf"), height=15, width=20)
pt 
dev.off()

# # values by IPSL and GFDL 
# layout <- "
# AB
# CD
# EF
# GH
# "
# 
# pt<-map_ipsl_value_2000_CMIP5$to + map_ipsl_value_2000_CMIP6$to +
#   map_ipsl_value_2000_CMIP5$pp + map_ipsl_value_2000_CMIP6$pp + 
#   map_ipsl_value_2000_CMIP5$phy + map_ipsl_value_2000_CMIP6$phy + 
#   map_ipsl_value_2000_CMIP5$zoo + map_ipsl_value_2000_CMIP6$zoo + 
#   plot_layout(design = layout)
# 
# pdf(paste0(save_loc,"Fig1B_1990_IPSL.pdf"), height=15, width=15)
# pt 
# dev.off()
# 
# pt<-map_gfdl_value_2000_CMIP5$to + map_gfdl_value_2000_CMIP6$to +
#   map_gfdl_value_2000_CMIP5$pp + map_gfdl_value_2000_CMIP6$pp + 
#   map_gfdl_value_2000_CMIP5$phy + map_gfdl_value_2000_CMIP6$phy + 
#   map_gfdl_value_2000_CMIP5$zoo + map_gfdl_value_2000_CMIP6$zoo + 
#   plot_layout(design = layout)
# 
# pdf(paste0(save_loc,"Fig1B_1990_GFDL.pdf"), height=15, width=15)
# pt 
# dev.off()


```






